### 2019-05-20 reproducing_registered_reports.Rmd
initial commit

---
title             : "Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology"
shorttitle        : "Reproducing Registered Reports"

author: 
  - name          : "Pepijn Obels"
    affiliation   : "1"
  - name          : "Daniel Lakens"
    affiliation   : "1"
    corresponding : yes
    address       : "ATLAS 9.402, 5600 MB, Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
  - name          : "Nicholas A. Coles"
    affiliation   : "2"
  - name          : "Jaroslav Gottfried"
    affiliation   : "3"

affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology, The Netherlands"
  - id            : "2"
    institution   : "University of Tennessee, Knoxville, USA"
  - id            : "3"
    institution   : "Masaryk University, Brno, Czech Republic"

author_note: |
  This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013. All code used to create this manuscript is provided in an OSF repository at https://osf.io/suqz3/.

abstract: |
  Ongoing technological developments have made it easier than ever before for scientists to share their data, materials, and analysis code. Sharing data and analysis code makes it easier for other researchers to re-use or check published research. These benefits will only emerge if researchers can reproduce the analysis reported in published articles, and if data is annotated well enough so that it is clear what all variables mean. Because most researchers have not been trained in computational reproducibility, it is important to evaluate current practices to identify practices that can be improved. We examined data and code sharing, as well as computational reproducibility of the main results without contacting the original authors, for Registered Reports published in the in psychological literature between 2014 and 2018. Of the 62 articles that met our inclusion criteria data was available for 40 articles, and analysis scripts for 43 articles. For the 35 articles that shared both data and code and performed analyses in SPSS, R, or JASP, we could run the scripts for 30 articles, and reproduce the main results for 19 articles. Although the percentage of articles that shared both data and code (61%) and articles that could be computationally reproduced (54%) was relatively high compared to other studies, there is clear room for improvement. We provide practices recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.

keywords          : "reproducibility, Registered Reports, data sharing, open science"
wordcount         : 4926

bibliography      : ["reproducing_registered_reports.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "jou, a4paper"
output            : papaja::apa6_pdf
---
```{r load_packages, include=FALSE}

# > sessionInfo()
# R version 3.5.3 (2019-03-11)
# Platform: x86_64-w64-mingw32/x64 (64-bit)
# Running under: Windows 10 x64 (build 17134)
# 
# Matrix products: default
# 
# locale:
# [1] LC_COLLATE=Dutch_Netherlands.1252  LC_CTYPE=Dutch_Netherlands.1252   
# [3] LC_MONETARY=Dutch_Netherlands.1252 LC_NUMERIC=C                      
# [5] LC_TIME=Dutch_Netherlands.1252    
# 
# attached base packages:
# [1] stats     graphics  grDevices utils     datasets  methods   base     
# 
# other attached packages:
# [1] here_0.1       irr_0.84.1     lpSolve_5.6.13 readxl_1.3.1  
# 
# loaded via a namespace (and not attached):
#  [1] Rcpp_1.0.1       crayon_1.3.4     rprojroot_1.3-2  cellranger_1.1.0 backports_1.1.4 
#  [6] pillar_1.4.0     rlang_0.3.4      rstudioapi_0.10  tools_3.5.3      xfun_0.6        
#  [11] compiler_3.5.3   pkgconfig_2.0.2  knitr_1.22       tibble_2.1.1

library(readxl)
library(here)
library(irr)

all_data <- read_excel("Data_for_Analysis_of_Open_Data_and_Computational_Reproducibility_in_Registered_Reports_in_Psychology.xlsx", n_max = 62)

#Count how many papers have data available
availability <- sum(all_data$availability)

#Calculate number of studies using spss, r, or both.
spss_or_r_or_jasp <- sum(all_data$programming_language == "spss", na.rm = TRUE) + sum(all_data$programming_language == "R", na.rm = TRUE) + 
sum(all_data$programming_language == "R, spss", na.rm = TRUE) + sum(all_data$programming_language == "JASP", na.rm = TRUE)

#Calculate time for subsets of spss and r for po who reproduced both.
time_spss_po <- subset(all_data$time_reproducing_po, all_data$programming_language == "spss")
time_r_po <- subset(all_data$time_reproducing_po, all_data$programming_language == "R")
time_jasp_po <- subset(all_data$time_reproducing_po, all_data$programming_language == "JASP")

#Create subgroups to report reproducibility per language
run_script_spss <- subset(all_data$run_script_final, all_data$programming_language == "spss")
run_script_r <- subset(all_data$run_script_final, all_data$programming_language == "R")
run_script_r_spss <- subset(all_data$run_script_final, all_data$programming_language == "R, spss")
run_script_jasp <- subset(all_data$run_script_final, all_data$programming_language == "JASP")

# Compute average time for all coders for all studies
average_time <- mean(c(all_data$time_reproducing_po, all_data$time_reproducing_nc, all_data$time_reproducing_jg, all_data$time_reproducing_dl), na.rm = TRUE)

```

Researchers are currently exploring ways to make science more open and transparent. Among novel developments such as pre-registration, pre-prints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., [@morey_peer_2016]. Sharing data and analysis code with scientific publications allows others to more easily reproduce, check, and build on existing work. However, since most researchers have received relatively little training in how to share data and code to facilitate reproducible science, it is important to evaluate how data and code is currently being shared to learn what needs to be improved. With this goal in mind we aimed to computationally reproduce the results of Registered Reports published in the psychological literature.

It is desirable that research is reproducible. Data availability has the potential to save time in the long run by facilitating other researchers to re-use data, allows findings to be more easily included in meta-analyses, and makes it possible for peers to check and correct published findings. According to @kitzes_practice_2017 computational reproducibility means that ”a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.” For scientific research to be computationally reproducible, the data and code needs to be shared. However, the availability of data and code in itself is not enough. Data and code also need to be linked in the article so that readers know where to find it. Preferably, the data should be available in a format that can be read by open source software. In addition to being able to access the data and code underlying the results in an article, researchers should be able to understand the data and code (which means variables are described, and code is annotated). Finally, the results reported in the scientific manuscript should be reproducible, which means the data and code can be used to compute the results that are reported in the article.

Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and if so, whether it was possible to reproduce the data analysis reported in the published article. @hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal Cognition. They could reproduce 11 articles without assistance, 11 with assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance. Hardwicke et al. (2018) estimated that it took between 2-4 hours to reproduce a paper, but they did not record the exact time. @stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals. They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one could not be reproduced due to a lack of a software license, and 16 articles could not be reproduced with access to the required software. For the remaining articles, 32 could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results. @stodden_empirical_2018 analyzed data availability in the journal science in 2011-2012 and found that 26 of 204 (or 13%) of articles provided information to retrieve data and/or code without contacting the authors. For all datasets they acquired after e-mailing authors for data and code, 26% was estimated to be computationally reproducible.

Our main interest is to examine whether data and code authors shared with their paper were reusable without contacting the original authors. The benefit of sharing data and code over making them available upon request is that even if the original author can no longer be reached, the data is still reusable. We set out to examine the data availability and reproducibility in Registered Reports published in psychological science. Registered Reports are a relatively novel development in psychology. The theoretical introduction and a detailed description of the method is submitted for publication, peer reviewed, and revised, after which it can receive an 'in principle acceptance'. This means the article will be published as long as the authors follow their preregistered data collection and analysis plan [@chambers_instead_2014; @nosek_registered_2014]. The population of Registered Reports in psychology is still relatively small (91 Registered Reports had been published as of February 22, 2018), which makes it possible to examine it in full. The novelty of Registered Reports may attract early adopters who are also exploring other novel developments in psychology, such as sharing data and code. We assumed that researchers who publish Registered Reports would also be likely to share data and code in public repositories. In line with our assumptions, `r sum(all_data$availability, na.rm = TRUE)` out of `r length(all_data$doi)` articles in our final dataset shared data and code (`r round(100*sum(all_data$availability, na.rm = TRUE)/length(all_data$doi),1)`%). In comparison, after Cognition introduced a mandatory data sharing policy, 136 out of 174 articles (78.2%) had a data availability statement, and 49% of 174 articles had reusable data (Hardwicke et al., 2018). Sharing analysis code was not required, and only 18 out of 174 articles provided the analysis code (10.3%). To evaluate the reproducibility of findings published in Registered Reports, we examine if data can be located, is available at the indicated location, can be opened in open-source software, is understandable, and can be used to reproduce the reported results.

### The Current Research

Our main objective is to examine how reusable data and code underlying Registered Reports in Psychology are, based purely on the information provided in the published literature. We examine the extent to which we can reproduce reported analyses without contacting the original authors. While reproducing the results reported in Registered Reports, we kept track of factors that facilitated reproducibility or that made reproducing the result more difficult. We report these qualitative findings with an aim to highlight how current practices can be improved.

### Method

To find Registered Reports published in psychology, we drew from a database of registered reports maintained by by Center for Open Science. At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such papers are most representative of the psychological literature, and excluded 7 large scale collaborations where dedicated team members worked on making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018]. Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally registered reports. This left `r length(all_data$doi)` studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, Matlab), which led to the exclusion of `r sum(all_data$included_language == FALSE, na.rm = TRUE)` additional studies.

### Results

We set out to reproduce the `r length(all_data$doi)` papers that met our inclusion criteria. For each article we coded whether the data and code were (a) linked, (b) available, (c) not software-specific, (d) understandable, and (e) reproducible. These five categories were inspired by FAIR data principles [@wilkinson_fair_2016] that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles. Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of meta-data (which is missing for practically all datasets). We considered data and code to be linked when the manuscript included a unique link to the data and scripts. Ideally, such a link consists of a stable digital object identifier (DOI). A hyperlink to a website that contains the data and script also suffices, although such regular links are known to often break over time [@gertler_reference_2017].

Of the `r length(all_data$doi)` papers, `r sum(all_data$linked)` had data and/or code that was linked to the article. Linking to data does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable. For one article the link no longer worked (highlighting the need to use a stable DOI when linking to data). For three articles the link still worked, but there was no data at the linked destination. For three articles where there was no link to the data in the article, we were nevertheless able to find data on the Open Science Framework when searching for the title of the paper. For one paper the data was linked but not available, as the data was embargoed until a future date. Altogether, data was available for `r sum(all_data$availability)` out of `r length(all_data$doi)` papers.

We also coded the extent to which data and code was specific to software that was not freely available. When open source software is used, the analyses can be reproduced by anyone with a computer and internet, regardless of whether they have bought the same software package. When proprietary software is used, results might still be reproducible by anyone, but it could require more effort to do so. For example, SPSS produces proprietary .sav and .sps files. However, .sav files can be opened in R, and .sps files can be opened by a text editor and the code can be rewritten, as long the code is annotated well enough to be recoded into R. Note that we had access to SPSS and therefore reproduced the analyses using the original .sps scripts where available. The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files that were analyzed in matlab, which we could not reproduce using open source software. This left `r sum(all_data$not_software_specific, na.rm = TRUE)` papers (see Figure 1).

\begin{figure*}
\begin{center}
\includegraphics{fig1.png}

\caption{Of all articles in the Registered Report database 79 were psychology related, and `r length(all_data$doi)` were registered reports not part of a multi-lab Registered Replication Report. Of these `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to the data. After searching the OSF, data was available for `r sum(all_data$availability)` studies. Of these datasets, `r sum(all_data$understandable, na.rm = TRUE)` were labelled well enough so that it was clear what variables meant. Of the `r length(all_data$doi)` papers `r sum(all_data$analysis_script_included, na.rm = TRUE)` shared the analysis script and data, for which `r spss_or_r_or_jasp` were in SPSS, R or JASP. Of these, the analysis script could be run for `r sum(all_data$run_script_final, na.rm = TRUE)`, of which `r sum(all_data$reproducible_final, na.rm = TRUE)` reproduced all main results. 
}

\label{fig:fig1}
\end{center}
\end{figure*}

One of the reasons to share data is allow other researchers to reproduce the reported results. Another important reason to share data is to enable other researchers to reuse the data. If the data can be understood by others, they can be used to answer novel research questions. This is one of the reasons why it is recommended to describe the dataset variables in a codebook. If the variables are not clearly described (e.g., the dataset consists of variables identified by abbreviations that only make sense to the original researcher), other researchers will not be able to reuse the data to answer novel questions. In our analyses, data were scored as 'understandable' when all variables were clearly named (e.g., 'Condition') and the values for variables were labeled (e.g., 0 = control, 1 = experimental). Out of the `r sum(all_data$not_software_specific, na.rm = TRUE)` papers with available data in a format that was not software specific, only `r sum(all_data$understandable, na.rm = TRUE)` datasets were described in enough detail to be understandable. This highlights the importance of adding a codebook with a datafile.

Finally, we examined how many of the `r sum(all_data$not_software_specific, na.rm = TRUE)` non-software-specific papers could be reproduced. It is possible that running the code on the data reproduces all analyses, even when the data file itself is not understandable (i.e., the data columns are not labeled). Two authors coded SPSS, R, and JASP analyses regarding (a) the executability of the script, and (b) the reproducibility of the results. After the initial coding, inter-rater reliability was low (`r agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_jg == FALSE))$value`% agreement on executability, and `r agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_jg == FALSE))$value`% agreement on reproducibility for SPSS scripts, `r agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_nc == FALSE))$value`% agreement on executability, and `r agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_nc == FALSE))$value`% agreement on reproducibility for R scripts). This initial low agreement provided two important insights about the definition of reproducibility and executability on the one hand, and the role of expertise on the other hand.

We used a dichotomous coding scheme to when coding whether the script could be executed whether the results could be reproduced ('yes' or 'no'). Code often needed minor adjustments to run on the data, such as changing file locations, or loading packages in R, and coders sometimes took different approaches to how much they would adjust the code to make it run on the data. Furthermore, coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article. After evaluating our initial coding round, we considered an article reproducible if we could get the same main results as represented in the paper with at best minor changes to make the scripts run on the data. This means we considered the analysis reproducible, even if variables could only be found with reasonable effort or by making assumptions about how variable names mapped onto variables reported in the data analysis. Furthermore, we changed folder locations when needed and loaded libraries that were required.

There were differences between coders in how much expertise they had with R, SPSS, and JASP (PO had less experience, while JG and NC had more experience). The more expertise coders had, the easier it was to reproduce findings (which lead to lower inter-rater reliability). This raises the question regarding which level of skill is expected to be able to reproduce results reported in a scientific article. The required experience might be difficult to quantify. Our results concerning the reproducibility of results is based on which results a PhD student with experience in the statistical software and educated in the same scientific discipline could reproduce, which we feel is a reasonable standard. For the current analysis, we considered a study reproducible as long as the more experienced coder could reproduce the main results.

All authors have collectively discussed the discording ratings, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g. overlooked script files). The final ratings presented here have been discussed and approved by all authors, but will likely not be completely flawless, as different teams of coders will likely reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve). It should be noted that the main goal of our analysis is to evaluate whether there is room for improvement, and how the reproducibility of results can be improved in practice. We expect any estimate of the reproducibility of results to improve over time as the field develops better standards and researchers are trained in reproducibility.

For each article two coders examined whether the code could be run on the data. Of the original `r length(all_data$doi)` articles, `r sum(all_data$included_language == FALSE, na.rm = TRUE, na.rm = TRUE)` used Matlab and Python and were excluded from the analysis due to a lack of expertise in our team with these languages. In total code and data were available for `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)` articles, of which `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` used R, SPSS, or JASP. We were able to run the code for `r sum(all_data$run_script_final == TRUE, na.rm = TRUE)` out of the `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` articles that used SPSS, R, and JASP. R was used as a coding language in `r length(run_script_r)`, of which `r sum(run_script_r)` scripts could be run on the data, `r length(run_script_spss)` papers used SPSS, for `r sum(run_script_spss)` of which the script could be run, and `r length(run_script_r_spss)` papers used both SPSS and R, for which the scripts could be run for all `r sum(run_script_r_spss)` papers. JASP does not seperate the data and code, but instead stores both in a single JASP file. This means that the analyses are always directly linked to the code for every output, you can see which settings were used to generate it, as well as the data that were used. Because of this useful feature, because the JASP files were available for the `r sum(run_script_jasp)` articles that relied on JASP for the analyses, we could always see how the output was generated.

Being able to run the code on the data does not imply that all the main analyses reported in the manuscript are correctly reproduced. Some analyses in a paper might not be part of the code or the output. We found that `r sum(all_data$reproducible_final, na.rm = TRUE)` out of `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` papers (`r round(100*sum(all_data$reproducible_final, na.rm = TRUE)/sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE),1)`%) that included their data and code could be used to reproduce the main results in the article. The average time to reproduce analyses reported in R was `r round(mean(time_r_po, na.rm = TRUE),2)` minutes for the first coder (SD = `r round(sd(time_r_po, na.rm = TRUE),2)`) and `r round(mean(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)` minutes (SD =  `r round(sd(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)`) for the second coder. Reproducing the SPSS analysis took on average `r round(mean(time_spss_po, na.rm = TRUE),2)` minutes (SD = `r round(sd(time_spss_po, na.rm = TRUE),2)`) for the first coder and  `r round(mean(as.numeric(all_data$time_reproducing_jg), na.rm = TRUE),2)` minutes (SD = `r round(sd(as.numeric(all_data$time_reproducing_jg), na.rm = TRUE),2)`) for the second coder. Most of the time was spent on matching output from the statistical analyses to the analyses reported in the manuscript. This suggests that even if results are reproducible, the organization of the output, and the relation of the output to the published manuscript, can often be improved.

### Discussion

We analyzed data and scripts of `r length(all_data$doi)` Registered Reports to examine how many authors shared their data and code, and how often main results reported in the manuscript could be reproduced. In total, `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)` out of `r length(all_data$doi)` (or `r round(100*sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)/length(all_data$doi),1)`%) of the articles shared the underlying data and the code that was used to generate the results. Of the papers that shared both the data and the analysis code and used software we had experience with, we could reproduce the main results for approximately half the papers. Authors of Registered Reports in psychology seem to voluntarily choose to share data and code relatively often compared to authors of articles in political science [@stockemer_data_2018]. Compared to authors of non-registered reports in psychology, voluntary data and code sharing is relatively high, as is the reproducibility rate (taking into account that we reproduced articles without contacting the original authors). The reproducibility rate was higher than the 31% rate observed by Hardwicke et al. (2018), and both voluntary data sharing as reproducibility were higher than in the sample of papers from the journal Science in 2011-2012 analyzing in @stodden_empirical_2018.

Nevertheless, the reproducibility rate for articles where data and code were available show there is clear room for improvement in how reproducible published Registered Reports are, when we attempted to reproduce main analyses without contacting the authors. One of the main goals of our project was to identify ways to improve the reproducibility of published articles. We encountered several common issues that made results reported in Registered Reports difficult to reproduce (cf. Hardwicke et al., 2018). This leads to X points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output anaysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process. We will discuss each of these points below, and link to examples of good practices that we encountered.

First, data is easier to understand and more reusable if variables and their values are clearly described, for example in a codebook. Researchers should ensure that the codebook and variable names are in the same language as the article. Furthermore, when there are multiple datafiles, researchers should provide a clear description of what each datafile contains, for example in a README file in the root directory of the data folder. @le_open_2018 provides useful guidelines to create codebooks in his Open Science Manual. A good example of a codebook can be found as part of the materials of @wesselmann_revisiting_2014. Creating a codebook should be considered a best practice when sharing data.

Second, code should be well-annotated, so that it is understandable for researchers who did not write the code. Well-annotated code makes clear what the analysis code does, in which order it should be run, and which output each section of analysis code generates. A good example of well-annotated code can be found in the materials of @weston_role_2018. It helps to make clear how the analysis code relates to the analyses reported in the paper, to make it easier for others to identify which code generates which results in the paper. For one manuscript which was coded as not reproducible, there was too much unstructured code, and each analyses took too long to run, that it was decided that the manuscript was not reproducible with a reasonable amount of effort mainly due to the lack of a clear indication which code needed to be run to reproduce specific results. Explicitly linking code in the analysis script to the final manuscript also helps researchers to check whether all results in the article are reproduced by the shared code. An example of a data analysis file that clearly links the code to the final articles can be found in the materials of @voorspoels_can_2014. If analyses are performed that are not included in the manuscript, this should be stated explicitly (e.g., assumption checks, exploratory analyses, etc.). The structure of analysis scripts can often be improved by creating different sections in the code, or creating different files for different parts of the data analysis (e.g., data cleaning, data preparation, exploratory data analysis, and confirmatory data analysis scripts). It is also highly recommended to perform a final check after the peer-review process has been completed to make sure any changes in the code introduced during the peer-review process are reflected in the shared data and code.

Based on our experiences, we have several specific recommendations for data analyzed in R. First of all, most code in R relies on specific libraries (or packages). List all the packages that the code needs to run at the top of the script. Because packages update, it is necessary to report the version numbers of packages that were used (for example using packrat of copying the output of the the sessionInfo() function as a comment in the script). Remember that folder names and folder structures differ between computers, and therefore you should use relative locations (and not “c:/user/myfolder/code”). RStudio projects and the 'here' package provide an easy way to use relative paths. When multiple scripts are used in the analysis, include the order in which scripts should be performed on the data in a README file. RMarkdown files provide a useful way to share clearly annotated code and structure the difference steps in the data analysis, for example as done by @campbell_self-esteem_2018.

While trying to reproduce the results of SPSS scripts, the biggest issue was the often confusing and unclear structure of the scripts. Large portion of the scripts were not annotated, and it was unclear which results they should produce. Often, the descriptive, confirmatory and exploratory analyses were not easily distinguishable because of an overall lack of structure. The absence of understandable variable and value labels in more than half of all SPSS scripts hindered our attempts to reproduce these results. Often the only time-efficient way to check if an article was reproducible so was to run the whole script, and search try to identify specific p-values or effect sizes from the article in the SPSS output. SPSS users should take greater care to clearly organize their analysis scripts by adding comments or a README file that links results generated by the SPSS script to the analyses reported in the manuscript. Another frequent problem consisted of missing or incorrectly labeled variables in the dataset, so the script could not run properly. We expect this is the result of authors updating or modifying either their datasets or their scripts during the publication process. This issue could be easily detected if a second author of the manuscript attempted to reproduce the analyses reported in the final manuscript before the data and scripts are shared publicly.

### Limitations and Future Research

We limited our analysis to Registered Reports based on the idea that these article formats might be used by people who are early adopters of innovations in science, and would therefore be more likely to also share data and code. The default rate with which data and code was shared was relatively high, compared to other studies on the reproducibility of analyses (e.g, Hardwicke et al., 2018, Stockemer et al., 2018), but we do not have data that gives insights into the motivations of these authors. Registered Reports are written by a diverse set of researchers, working in different subfields in psychology, and it would be interesting for future research to qualitatively examine the motivations of researchers who published Registered Reports for sharing or not sharing data and code. There are several good reasons why data can not be shared, and researchers should be able to explain why data is not available when they publish a scientific article [@morey_peer_2016].

The main aim of this article was not to accurately estimate mean reproducibility rates, but to see what current standards are, and how the reproducibility of research articles using the Registered Report format could be improved. The sample size is small, and it is doubtful whether an accurate estimate of the reproducibility of Registered Reports is of much value, beyond examining where most room for improvement is. Data and code sharing are relatively new, researchers typically lack training in reproducible data analysis, and therefore the main contribution of this article is the identification of common issues that can be improved. We provided some suggestions and examples of better practices that should make the results in published articles more reproducible.

In addition to the recommendations we have provided above, we believe novel technological solutions might improve the reproducibility of research articles. For example, CodeOcean is a new cloud based computational reproducibility platform that could solve some of the problems we observed. CodeOcean is an online, cloud based, computational reproducibility platform [@clyburne-sherin_computational_2018]. It provides a code environment that runs online, which means that researchers using CodeOcean do not have to download data, code, or software, but can analyze the data in their browser. It is not yet possible to use SPSS within CodeOcean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations. Another example is RMarkdown which enable researchers to write fully reproducible manuscripts. RMarkdown files load the raw data and allow researchers to compute each number reported in the manuscript, instead of copy-pasting values. This means that, as long as the data and require packages can be loaded, all reported numbers can be transparently and reproducibly reported. This saves a lot of time matching the analysis code to the reported results, and thus speeds up the process of checking whether all results reported in the manuscripts are reproduced by the code. This manuscript is an example of a reproducible RMarkdown file. Alternative solutions that help researchers to share reproducible analyses might become available in the future.

Finally, journals who value reproducibility might find it worthwhile to check whether the data and analysis code shared with a submission can be used to reproduce the results. The average time it took our team to check that the analysis code could reproduce the results the results reported in the paper was `r round(average_time,0)` minutes. This is slightly shorter than the time it took Hardwicke and colleagues (2018), who estimated (without keeping track of the time explicitly) that reproducibility reports took between 2 and 25 person-hours, depending on whether the paper eventually fell in the reproducible or not-reproducible category, and whether author assistance was needed. The main difference might be that we did not write 'reproducibility reports' for each article. Documenting the process of reproducing a paper adds transparency and allows others to check the the decisions about every value in an article. Whether such a level of detailed is worth the additional costs of documenting each reported value individually is a cost-benefit analysis that each journal should make. The required time might be reduced by explicitly asking authors to submit files in a format or structure that facilitates such checks, or automating part of the work that is needed to check the reproducibility of results. Overall, we feel that the time required for a basic check of the reproducibility of manuscripts (i.e., where one checks whether the *main* results in the paper are reproduced by the analysis scripts, but without documenting this step at the level of each individual number) is not an insurmountable problem for scientific journals that aim to add value and improve the computational reproducibility of the published literature.

In addition to novel technologies, most progress can probably be made by developing standards within a research community, and educating researchers about best practices to guarantee reproducibility. Most researchers are currently not trained in reproducible data analysis, and they can not be expected to invent best-practices from scratch. As good examples appear in the published literature over time, and best practices within subdisciplines crystalize, standards should emerge that improve reproducibility, and that allow researchers to share data and code in such a way that others with basic scientific training can reproduce their results and reuse their data.

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

### 2019-05-22 codebook.Rmd
add codebook

---
title: "Codebook"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: true
  pdf_document:
    toc: yes
    toc_depth: 4
    latex_engine: xelatex
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = TRUE, # show warnings during codebook generation
  message = TRUE, # show messages during codebook generation
  error = TRUE, # do not interrupt codebook generation in case of errors,
                # usually better for debugging
  echo = TRUE  # show R code
)
ggplot2::theme_set(ggplot2::theme_bw())
pander::panderOptions("table.split.table", Inf)
```

```{r prepare_codebook}
library(codebook)
library(readxl)
library(here)
library(rio)

codebook_data <- read_excel("Data_for_Analysis_of_Open_Data_and_Computational_Reproducibility_in_Registered_Reports_in_Psychology.xlsx", n_max = 62)
#Read codebook from second sheet in excel file.
dict <- read_excel("Data_for_Analysis_of_Open_Data_and_Computational_Reproducibility_in_Registered_Reports_in_Psychology.xlsx", sheet = "Codebook")

#Add variable labels to data
var_label(codebook_data) <- dict_to_list(dict)

#Add meta data
metadata(codebook_data)$name <- "Reproducibility of Registered Reports in psychology"
metadata(codebook_data)$description <- "Coded variables to examine data and code sharing and the computational reproducibility for Registered Reports in psychology"
metadata(codebook_data)$creator <- "Pepijn Obels, Daniel Lakens, Nicholas A. Coles, Jaroslav Gottfried"
metadata(codebook_data)$temporalCoverage <- "Spring 2018"

#Export codebook
rio::export(codebook_data, "reproducing_registered_reports_codebook.rds") # to R data structure file
```

```{r codebook}
codebook(codebook_data)
```

### 2019-05-22 reproducing_registered_reports.Rmd
add codebook

@@
 Although the percentage of articles that shared both data and code (61%) and articles that could be computationally reproduced (54%) was relatively high compared to other studies, there is clear room for improvement.
-We provide practices recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.
+We provide practical recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.
 
@@
 
-# > sessionInfo()
-# R version 3.5.3 (2019-03-11)
-# Platform: x86_64-w64-mingw32/x64 (64-bit)
-# Running under: Windows 10 x64 (build 17134)
-# 
-# Matrix products: default
-# 
-# locale:
-# [1] LC_COLLATE=Dutch_Netherlands.1252  LC_CTYPE=Dutch_Netherlands.1252   
-# [3] LC_MONETARY=Dutch_Netherlands.1252 LC_NUMERIC=C                      
-# [5] LC_TIME=Dutch_Netherlands.1252    
-# 
-# attached base packages:
-# [1] stats     graphics  grDevices utils     datasets  methods   base     
-# 
-# other attached packages:
-# [1] here_0.1       irr_0.84.1     lpSolve_5.6.13 readxl_1.3.1  
-# 
-# loaded via a namespace (and not attached):
-#  [1] Rcpp_1.0.1       crayon_1.3.4     rprojroot_1.3-2  cellranger_1.1.0 backports_1.1.4 
-#  [6] pillar_1.4.0     rlang_0.3.4      rstudioapi_0.10  tools_3.5.3      xfun_0.6        
-#  [11] compiler_3.5.3   pkgconfig_2.0.2  knitr_1.22       tibble_2.1.1
-
 library(readxl)
@@
 library(irr)
+library(codebook)
 
 all_data <- read_excel("Data_for_Analysis_of_Open_Data_and_Computational_Reproducibility_in_Registered_Reports_in_Psychology.xlsx", n_max = 62)
+codebook_data <- read_excel("Data_for_Analysis_of_Open_Data_and_Computational_Reproducibility_in_Registered_Reports_in_Psychology.xlsx", sheet = "Codebook")
+
+#Use the codebook package to add labels to variables
+var_label(all_data) <- dict_to_list(codebook_data)
 
@@
 Sharing data and analysis code with scientific publications allows others to more easily reproduce, check, and build on existing work.
-However, since most researchers have received relatively little training in how to share data and code to facilitate reproducible science, it is important to evaluate how data and code is currently being shared to learn what needs to be improved.
-With this goal in mind we aimed to computationally reproduce the results of Registered Reports published in the psychological literature.
+However, since most researchers have received limited training in how to share data and code to facilitate reproducible science, it is important to evaluate how data and code are currently being shared to learn what needs to be improved.
+With this goal in mind, we aimed to computationally reproduce the results of Registered Reports published in the psychological literature.
 
 It is desirable that research is reproducible.
-Data availability has the potential to save time in the long run by facilitating other researchers to re-use data, allows findings to be more easily included in meta-analyses, and makes it possible for peers to check and correct published findings.
-According to @kitzes_practice_2017 computational reproducibility means that ”a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.” For scientific research to be computationally reproducible, the data and code needs to be shared.
+Data availability has the potential to save time in the long run by facilitating the re-use of data, allows findings to be more easily included in meta-analyses, and makes it possible for peers to check and correct published findings.
+According to @kitzes_practice_2017, computational reproducibility means that ”a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.” For scientific research to be computationally reproducible, the data and code needs to be shared.
 However, the availability of data and code in itself is not enough.
-Data and code also need to be linked in the article so that readers know where to find it.
+These materials also need to be linked in the article so that readers know where to find them.
 Preferably, the data should be available in a format that can be read by open source software.
-In addition to being able to access the data and code underlying the results in an article, researchers should be able to understand the data and code (which means variables are described, and code is annotated).
-Finally, the results reported in the scientific manuscript should be reproducible, which means the data and code can be used to compute the results that are reported in the article.
+Having access to rdata and analysis files is not worth much of these files can not be understood.
+Variables must be described and labeled (e.g., in a codebook), and code should be annotated.
+Finally, the results reported in the scientific manuscript should be reproducible, which means the data and code can be used to compute the results that are reported in the published article.
 
-Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and if so, whether it was possible to reproduce the data analysis reported in the published article.
+Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the published article.
 @hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal Cognition.
-They could reproduce 11 articles without assistance, 11 with assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance.
+Eleven  articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance.
 Hardwicke et al.
@@
 For all datasets they acquired after e-mailing authors for data and code, 26% was estimated to be computationally reproducible.
+It seems there is clear room for improvement in how reproducible published articles are.
 
+We set out to examine the data availability and reproducibility in Registered Reports published in psychological science.
 Our main interest is to examine whether data and code authors shared with their paper were reusable without contacting the original authors.
 The benefit of sharing data and code over making them available upon request is that even if the original author can no longer be reached, the data is still reusable.
-We set out to examine the data availability and reproducibility in Registered Reports published in psychological science.
 Registered Reports are a relatively novel development in psychology.
-The theoretical introduction and a detailed description of the method is submitted for publication, peer reviewed, and revised, after which it can receive an 'in principle acceptance'.
+Before data collection commences, the introduction and methods are peer-reviewed, after whichauthors can receive an 'in principle acceptance'.
 This means the article will be published as long as the authors follow their preregistered data collection and analysis plan [@chambers_instead_2014; @nosek_registered_2014].
@@
 In line with our assumptions, `r sum(all_data$availability, na.rm = TRUE)` out of `r length(all_data$doi)` articles in our final dataset shared data and code (`r round(100*sum(all_data$availability, na.rm = TRUE)/length(all_data$doi),1)`%).
-In comparison, after Cognition introduced a mandatory data sharing policy, 136 out of 174 articles (78.2%) had a data availability statement, and 49% of 174 articles had reusable data (Hardwicke et al., 2018).
+In comparison, after *Cognition* introduced a mandatory data sharing policy, 136 out of 174 articles (78.2%) had a data availability statement, and 49% of 174 articles had reusable data (Hardwicke et al., 2018).
 Sharing analysis code was not required, and only 18 out of 174 articles provided the analysis code (10.3%).
-To evaluate the reproducibility of findings published in Registered Reports, we examine if data can be located, is available at the indicated location, can be opened in open-source software, is understandable, and can be used to reproduce the reported results.
+To evaluate the reproducibility of findings published in Registered Reports, we examine if data can be located, are available at the indicated location, can be opened in open-source software, are understandable, and can be used to reproduce the reported results.
 
@@
 
-Our main objective is to examine how reusable data and code underlying Registered Reports in Psychology are, based purely on the information provided in the published literature.
-We examine the extent to which we can reproduce reported analyses without contacting the original authors.
+Our main objective was to examine how reusable data and code underlying Registered Reports are, based purely on the information provided in the published literature.
+We examined the extent to which we could reproduce reported analyses without contacting the original authors.
 While reproducing the results reported in Registered Reports, we kept track of factors that facilitated reproducibility or that made reproducing the result more difficult.
@@
 We limited our analysis to studies performed by single groups, since such papers are most representative of the psychological literature, and excluded 7 large scale collaborations where dedicated team members worked on making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018].
-Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally registered reports.
+Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports.
 This left `r length(all_data$doi)` studies in our sample.
@@
 Furthermore, we changed folder locations when needed and loaded libraries that were required.
+Finally, even though sometimes Figures contained relevant information (e.g., the pattern of means) we did not require all figures to be reproducible.
 

### 2019-05-22 reproducing_registered_reports.Rmd
updated manuscript

@@
 library(irr)
-library(codebook)
 
 all_data <- read_excel("Data_for_Analysis_of_Open_Data_and_Computational_Reproducibility_in_Registered_Reports_in_Psychology.xlsx", n_max = 62)
-codebook_data <- read_excel("Data_for_Analysis_of_Open_Data_and_Computational_Reproducibility_in_Registered_Reports_in_Psychology.xlsx", sheet = "Codebook")
-
-#Use the codebook package to add labels to variables
-var_label(all_data) <- dict_to_list(codebook_data)
 
@@
 Sharing data and analysis code with scientific publications allows others to more easily reproduce, check, and build on existing work.
-However, since most researchers have received limited training in how to share data and code to facilitate reproducible science, it is important to evaluate how data and code are currently being shared to learn what needs to be improved.
-With this goal in mind, we aimed to computationally reproduce the results of Registered Reports published in the psychological literature.
+This requires the development of new skills and best practices, since most scientists have not received training in how to make their work reproducible.
+It is important to evaluate how data and code are currently being shared, and how easy it is to reproduce analyses reported in the published literature, to learn what can be improved.
+With this goal in mind, we computationally reproduced the main results of Registered Reports published in the psychological literature.
 
 It is desirable that research is reproducible.
-Data availability has the potential to save time in the long run by facilitating the re-use of data, allows findings to be more easily included in meta-analyses, and makes it possible for peers to check and correct published findings.
+Data availability has the potential to make science more efficient by facilitating the re-use of data.
+The availability of analysis code makes it possible for peers to check and correct published findings.
 According to @kitzes_practice_2017, computational reproducibility means that ”a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.” For scientific research to be computationally reproducible, the data and code needs to be shared.
+
 However, the availability of data and code in itself is not enough.
-These materials also need to be linked in the article so that readers know where to find them.
+Articles need to link to these materials so that readers know where to find them.
 Preferably, the data should be available in a format that can be read by open source software.
-Having access to rdata and analysis files is not worth much of these files can not be understood.
 Variables must be described and labeled (e.g., in a codebook), and code should be annotated.
@@
 Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the published article.
-@hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal Cognition.
+@hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal *Cognition*.
 Eleven  articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance.
 Hardwicke et al.
-(2018) estimated that it took between 2-4 hours to reproduce a paper, but they did not record the exact time.
+(2018) estimated that it took between 2-4 hours to reproduce the reported results, but they did not record the exact time.
 @stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals.
@@
 For the remaining articles, 32 could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results.
-@stodden_empirical_2018 analyzed data availability in the journal science in 2011-2012 and found that 26 of 204 (or 13%) of articles provided information to retrieve data and/or code without contacting the authors.
+@stodden_empirical_2018 analyzed data availability in the journal *Science* in 2011-2012 and found that 26 of 204 (or 13%) of articles provided information to retrieve data and/or code without contacting the authors.
 For all datasets they acquired after e-mailing authors for data and code, 26% was estimated to be computationally reproducible.
-It seems there is clear room for improvement in how reproducible published articles are.
+These studies reveal that there is clear room for improvement in how reproducible published articles are.
 
 We set out to examine the data availability and reproducibility in Registered Reports published in psychological science.
-Our main interest is to examine whether data and code authors shared with their paper were reusable without contacting the original authors.
-The benefit of sharing data and code over making them available upon request is that even if the original author can no longer be reached, the data is still reusable.
-Registered Reports are a relatively novel development in psychology.
-Before data collection commences, the introduction and methods are peer-reviewed, after whichauthors can receive an 'in principle acceptance'.
+Our main interest was to examine the computational reproducibility of the main analyses reported in published articles, without contacting the original authors.
+One of the main benefits of sharing data and code with the article (compared to making these files available upon request) is that results can be reproduced, and data reused even if the original author can no longer be reached.
+Registered Reports are a novel development in psychology.
+Before data collection commences, the introduction and methods are peer-reviewed, after which authors can receive an 'in principle acceptance'.
 This means the article will be published as long as the authors follow their preregistered data collection and analysis plan [@chambers_instead_2014; @nosek_registered_2014].
 The population of Registered Reports in psychology is still relatively small (91 Registered Reports had been published as of February 22, 2018), which makes it possible to examine it in full.
-The novelty of Registered Reports may attract early adopters who are also exploring other novel developments in psychology, such as sharing data and code.
-We assumed that researchers who publish Registered Reports would also be likely to share data and code in public repositories.
+
+The novelty of Registered Reports may attract early adopters who are also exploring other novel developments aimed at improving research practices in psychology, such as data and code sharing.
+We assumed that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
 In line with our assumptions, `r sum(all_data$availability, na.rm = TRUE)` out of `r length(all_data$doi)` articles in our final dataset shared data and code (`r round(100*sum(all_data$availability, na.rm = TRUE)/length(all_data$doi),1)`%).
-In comparison, after *Cognition* introduced a mandatory data sharing policy, 136 out of 174 articles (78.2%) had a data availability statement, and 49% of 174 articles had reusable data (Hardwicke et al., 2018).
-Sharing analysis code was not required, and only 18 out of 174 articles provided the analysis code (10.3%).
-To evaluate the reproducibility of findings published in Registered Reports, we examine if data can be located, are available at the indicated location, can be opened in open-source software, are understandable, and can be used to reproduce the reported results.
+In comparison, after the journal *Cognition* introduced a mandatory data sharing policy, 136 out of 174 articles (78.2%) had a data availability statement, 85 of 174 articles (49%) had reusable data, and only 18 out of 174 articles (10.3%) provided the analysis code (Hardwicke et al., 2018).
+To evaluate the reproducibility of findings published in Registered Reports, we examined if data could be located, were available at the indicated location, could be opened in open-source software, were documented well enough to be understandable, and could be used to reproduce the main analyses reported in the published manuscript.
 
@@
 Our main objective was to examine how reusable data and code underlying Registered Reports are, based purely on the information provided in the published literature.
-We examined the extent to which we could reproduce reported analyses without contacting the original authors.
+We examined how many authors voluntarily shared data and code, and the extent to which we could reproduce reported analyses without contacting the original authors.
 While reproducing the results reported in Registered Reports, we kept track of factors that facilitated reproducibility or that made reproducing the result more difficult.
@@
 
-To find Registered Reports published in psychology, we drew from a database of registered reports maintained by by Center for Open Science.
-At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
+To find Registered Reports published in psychology we drew from a database of registered reports maintained by by Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
 Eighty-one articles in this database were published in the psychological literature.
-We limited our analysis to studies performed by single groups, since such papers are most representative of the psychological literature, and excluded 7 large scale collaborations where dedicated team members worked on making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018].
+We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018].
 Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports.
@@
 Ideally, such a link consists of a stable digital object identifier (DOI).
-A hyperlink to a website that contains the data and script also suffices, although such regular links are known to often break over time [@gertler_reference_2017].
+A hyperlink to a website that contains the data and script also suffices, although normal hyperlinks are known to break over time [@gertler_reference_2017].
 
-Of the `r length(all_data$doi)` papers, `r sum(all_data$linked)` had data and/or code that was linked to the article.
+Of the `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to data and/or code in the article.
 Linking to data does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable.
@@
 The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files that were analyzed in matlab, which we could not reproduce using open source software.
-This left `r sum(all_data$not_software_specific, na.rm = TRUE)` papers (see Figure 1).
+This left `r sum(all_data$not_software_specific, na.rm = TRUE)` papers where data was available in a non-software-specific format.
 
@@
 After searching the OSF, data was available for `r sum(all_data$availability)` studies.
-Of these datasets, `r sum(all_data$understandable, na.rm = TRUE)` were labelled well enough so that it was clear what variables meant.
+Of these datasets, `r sum(all_data$understandable, na.rm = TRUE)` were documented well enough, for example through a codebook, so that variables were understandable.
 Of the `r length(all_data$doi)` papers `r sum(all_data$analysis_script_included, na.rm = TRUE)` shared the analysis script and data, for which `r spss_or_r_or_jasp` were in SPSS, R or JASP.
@@
 This highlights the importance of adding a codebook with a datafile.
+For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript) see @arslan_how_2019.
 
@@
 Two authors coded SPSS, R, and JASP analyses regarding (a) the executability of the script, and (b) the reproducibility of the results.
-After the initial coding, inter-rater reliability was low (`r agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_jg == FALSE))$value`% agreement on executability, and `r agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_jg == FALSE))$value`% agreement on reproducibility for SPSS scripts, `r agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_nc == FALSE))$value`% agreement on executability, and `r agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_nc == FALSE))$value`% agreement on reproducibility for R scripts).
+After the initial coding, inter-rater reliability was low (`r round(agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_jg == FALSE))$value,0)`% agreement on executability, and `r round(agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_jg == FALSE))$value,0)`% agreement on reproducibility for SPSS scripts, `r round(agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_nc == FALSE))$value,0)`% agreement on executability, and `r round(agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_nc == FALSE))$value,0)`% agreement on reproducibility for R scripts).
 This initial low agreement provided two important insights about the definition of reproducibility and executability on the one hand, and the role of expertise on the other hand.
 
-We used a dichotomous coding scheme to when coding whether the script could be executed whether the results could be reproduced ('yes' or 'no').
+We used a dichotomous coding scheme to when coding whether the script could be executed whether the results could be reproduced ('yes' or 'no'), but coders often reported 'partial' reproducibility.
 Code often needed minor adjustments to run on the data, such as changing file locations, or loading packages in R, and coders sometimes took different approaches to how much they would adjust the code to make it run on the data.
 Furthermore, coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article.
-After evaluating our initial coding round, we considered an article reproducible if we could get the same main results as represented in the paper with at best minor changes to make the scripts run on the data.
+After evaluating our initial coding round, we considered an article was reproducible when we could get the same *main results* as represented in the paper with at best *minor changes* to the analysis scripts.
 This means we considered the analysis reproducible, even if variables could only be found with reasonable effort or by making assumptions about how variable names mapped onto variables reported in the data analysis.
 Furthermore, we changed folder locations when needed and loaded libraries that were required.
-Finally, even though sometimes Figures contained relevant information (e.g., the pattern of means) we did not require all figures to be reproducible.
+Finally, even though sometimes figures were generated in R and contained relevant information (e.g., the pattern of means) we did not require all figures to be reproducible.
 
@@
 
-All authors have collectively discussed the discording ratings, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g.
+All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g.
 overlooked script files).
-The final ratings presented here have been discussed and approved by all authors, but will likely not be completely flawless, as different teams of coders will likely reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve).
-It should be noted that the main goal of our analysis is to evaluate whether there is room for improvement, and how the reproducibility of results can be improved in practice.
-We expect any estimate of the reproducibility of results to improve over time as the field develops better standards and researchers are trained in reproducibility.
+The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve).
+It should be noted that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.
 
@@
 JASP does not seperate the data and code, but instead stores both in a single JASP file.
-This means that the analyses are always directly linked to the code for every output, you can see which settings were used to generate it, as well as the data that were used.
-Because of this useful feature, because the JASP files were available for the `r sum(run_script_jasp)` articles that relied on JASP for the analyses, we could always see how the output was generated.
+This means that the analyses are always directly linked to the code for every output.
+It is always clear which settings were used to generate results.
+Because of this useful feature, the `r sum(run_script_jasp)` articles that relied on JASP for the analyses always allowed us to reproduce the analyses.
 
@@
 In total, `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)` out of `r length(all_data$doi)` (or `r round(100*sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)/length(all_data$doi),1)`%) of the articles shared the underlying data and the code that was used to generate the results.
-Of the papers that shared both the data and the analysis code and used software we had experience with, we could reproduce the main results for approximately half the papers.
+Of the papers that shared both the data and the analysis code and used software we had experience with, we could reproduce the main results for `r round(100*sum(all_data$reproducible_final, na.rm = TRUE)/sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE),1)`% of the papers.
 Authors of Registered Reports in psychology seem to voluntarily choose to share data and code relatively often compared to authors of articles in political science [@stockemer_data_2018].
-Compared to authors of non-registered reports in psychology, voluntary data and code sharing is relatively high, as is the reproducibility rate (taking into account that we reproduced articles without contacting the original authors).
+Compared to authors of non-registered reports in psychology, voluntary data and code sharing is also relatively high, as is the reproducibility rate (taking into account that we reproduced articles without contacting the original authors).
 The reproducibility rate was higher than the 31% rate observed by Hardwicke et al.
-(2018), and both voluntary data sharing as reproducibility were higher than in the sample of papers from the journal Science in 2011-2012 analyzing in @stodden_empirical_2018.
+(2018), and both voluntary data sharing as reproducibility were higher than in the sample of papers from the journal *Science* in 2011-2012 analyzed in @stodden_empirical_2018.
 
@@
 Hardwicke et al., 2018).
-This leads to X points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output anaysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process.
+This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output anaysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process.
 We will discuss each of these points below, and link to examples of good practices that we encountered.
@@
 It helps to make clear how the analysis code relates to the analyses reported in the paper, to make it easier for others to identify which code generates which results in the paper.
-For one manuscript which was coded as not reproducible, there was too much unstructured code, and each analyses took too long to run, that it was decided that the manuscript was not reproducible with a reasonable amount of effort mainly due to the lack of a clear indication which code needed to be run to reproduce specific results.
+For one manuscript which was coded as not reproducible, there was too much unstructured code, and each analyses took too long to run, so that it was decided that the manuscript was not reproducible with a reasonable amount of effort mainly due to the lack of a clear indication which code needed to be run to reproduce specific results.
 Explicitly linking code in the analysis script to the final manuscript also helps researchers to check whether all results in the article are reproduced by the shared code.
@@
 The structure of analysis scripts can often be improved by creating different sections in the code, or creating different files for different parts of the data analysis (e.g., data cleaning, data preparation, exploratory data analysis, and confirmatory data analysis scripts).
-It is also highly recommended to perform a final check after the peer-review process has been completed to make sure any changes in the code introduced during the peer-review process are reflected in the shared data and code.
+Third, it is highly recommended to perform a final check after the peer-review process has been completed to make sure any changes in the code introduced during the peer-review process are reflected in the shared data and code.
 
@@
 The absence of understandable variable and value labels in more than half of all SPSS scripts hindered our attempts to reproduce these results.
-Often the only time-efficient way to check if an article was reproducible so was to run the whole script, and search try to identify specific p-values or effect sizes from the article in the SPSS output.
+Often the only time-efficient way to check if an article was reproducible so was to run the whole script, and search try to identify specific *p*-values or effect sizes from the article in the SPSS output.
 SPSS users should take greater care to clearly organize their analysis scripts by adding comments or a README file that links results generated by the SPSS script to the analyses reported in the manuscript.
@@
 In addition to the recommendations we have provided above, we believe novel technological solutions might improve the reproducibility of research articles.
-For example, CodeOcean is a new cloud based computational reproducibility platform that could solve some of the problems we observed.
-CodeOcean is an online, cloud based, computational reproducibility platform [@clyburne-sherin_computational_2018].
-It provides a code environment that runs online, which means that researchers using CodeOcean do not have to download data, code, or software, but can analyze the data in their browser.
+For example, CodeOcean is an online, cloud based, computational reproducibility platform [@clyburne-sherin_computational_2018].
+It provides a code environment (or container) that runs online, which means that researchers using CodeOcean do not have to download data, code, or software, but can analyze the data in their browser.
 It is not yet possible to use SPSS within CodeOcean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.
-Another example is RMarkdown which enable researchers to write fully reproducible manuscripts.
-RMarkdown files load the raw data and allow researchers to compute each number reported in the manuscript, instead of copy-pasting values.
-This means that, as long as the data and require packages can be loaded, all reported numbers can be transparently and reproducibly reported.
+Another solution is RMarkdown which enable researchers to write fully reproducible manuscripts.
+RMarkdown files load the raw data and allow researchers to compute each number reported in the manuscript from the data, instead of copy-pasting values.
+This means that, as long as the data and require packages can be loaded, all reported numbers can be reproduced.
 This saves a lot of time matching the analysis code to the reported results, and thus speeds up the process of checking whether all results reported in the manuscripts are reproduced by the code.
-This manuscript is an example of a reproducible RMarkdown file.
-Alternative solutions that help researchers to share reproducible analyses might become available in the future.
+The current manuscript is an example of a reproducible RMarkdown file.^[see https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd] Additional solutions that help researchers to share reproducible analyses might become available in the future.
 
 Finally, journals who value reproducibility might find it worthwhile to check whether the data and analysis code shared with a submission can be used to reproduce the results.
-The average time it took our team to check that the analysis code could reproduce the results the results reported in the paper was `r round(average_time,0)` minutes.
+The average time it took our team to check that the analysis code could reproduce the results reported in the paper was `r round(average_time,0)` minutes.
 This is slightly shorter than the time it took Hardwicke and colleagues (2018), who estimated (without keeping track of the time explicitly) that reproducibility reports took between 2 and 25 person-hours, depending on whether the paper eventually fell in the reproducible or not-reproducible category, and whether author assistance was needed.
@@
 Documenting the process of reproducing a paper adds transparency and allows others to check the the decisions about every value in an article.
-Whether such a level of detailed is worth the additional costs of documenting each reported value individually is a cost-benefit analysis that each journal should make.
+Whether such a level of detail is worth the additional time investment of documenting each reported value is a cost-benefit analysis that journals should make for themselves.
 The required time might be reduced by explicitly asking authors to submit files in a format or structure that facilitates such checks, or automating part of the work that is needed to check the reproducibility of results.
-Overall, we feel that the time required for a basic check of the reproducibility of manuscripts (i.e., where one checks whether the *main* results in the paper are reproduced by the analysis scripts, but without documenting this step at the level of each individual number) is not an insurmountable problem for scientific journals that aim to add value and improve the computational reproducibility of the published literature.
+Overall, we feel that the time required for a basic check of the reproducibility of manuscripts (i.e., where one checks whether the *main* results in the paper are reproduced by the analysis scripts, but without documenting this step at the level of each individual number) is not an insurmountable problem for scientific journals that aim to add value, and would substantially improve the computational reproducibility of the published literature.
 
-In addition to novel technologies, most progress can probably be made by developing standards within a research community, and educating researchers about best practices to guarantee reproducibility.
-Most researchers are currently not trained in reproducible data analysis, and they can not be expected to invent best-practices from scratch.
+In addition to novel technologies, most progress can probably be made by developing standards within a research community, and educating researchers about best practices that guarantee reproducibility.
+Most researchers are not trained in reproducible data analysis, and can not be expected to invent best practices from scratch.
 As good examples appear in the published literature over time, and best practices within subdisciplines crystalize, standards should emerge that improve reproducibility, and that allow researchers to share data and code in such a way that others with basic scientific training can reproduce their results and reuse their data.

### 2019-05-22 reproducing_registered_reports.tex
updated manuscript

--- 2019-05-22 reproducing_registered_reports.Rmd
@@
----
-title             : "Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology"
-shorttitle        : "Reproducing Registered Reports"
+\documentclass[,jou, a4paper,floatsintext]{apa6}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology},
+            pdfauthor={Pepijn Obels, Daniel Lakens, Nicholas A. Coles, \& Jaroslav Gottfried},
+            pdfkeywords={reproducibility, Registered Reports, data sharing, open science},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-author: 
-  - name          : "Pepijn Obels"
-    affiliation   : "1"
-  - name          : "Daniel Lakens"
-    affiliation   : "1"
-    corresponding : yes
-    address       : "ATLAS 9.402, 5600 MB, Eindhoven, The Netherlands"
-    email         : "D.Lakens@tue.nl"
-  - name          : "Nicholas A. Coles"
-    affiliation   : "2"
-  - name          : "Jaroslav Gottfried"
-    affiliation   : "3"
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
 
-affiliation:
-  - id            : "1"
-    institution   : "Eindhoven University of Technology, The Netherlands"
-  - id            : "2"
-    institution   : "University of Tennessee, Knoxville, USA"
-  - id            : "3"
-    institution   : "Masaryk University, Brno, Czech Republic"
+  \title{Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology}
+    \author{Pepijn Obels\textsuperscript{1}, Daniel Lakens\textsuperscript{1}, Nicholas A. Coles\textsuperscript{2}, \& Jaroslav Gottfried\textsuperscript{3}}
+    \date{}
 
-author_note: |
-  This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
-All code used to create this manuscript is provided in an OSF repository at https://osf.io/suqz3/.
+\shorttitle{Reproducing Registered Reports}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Eindhoven University of Technology, The Netherlands\\\textsuperscript{2} University of Tennessee, Knoxville, USA\\\textsuperscript{3} Masaryk University, Brno, Czech Republic}
+\keywords{reproducibility, Registered Reports, data sharing, open science\newline\indent Word count: 4926}
+\usepackage{csquotes}
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
 
-abstract: |
+\usepackage{longtable}
+\usepackage{lscape}
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
+
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+\authornote{This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
+All code used to create this manuscript is provided in an OSF repository at \url{https://osf.io/suqz3/}.
+
+Correspondence concerning this article should be addressed to Daniel Lakens, ATLAS 9.402, 5600 MB, Eindhoven, The Netherlands. E-mail: \href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}
+
+\abstract{
 Ongoing technological developments have made it easier than ever before for scientists to share their data, materials, and analysis code.
@@
 For the 35 articles that shared both data and code and performed analyses in SPSS, R, or JASP, we could run the scripts for 30 articles, and reproduce the main results for 19 articles.
-Although the percentage of articles that shared both data and code (61%) and articles that could be computationally reproduced (54%) was relatively high compared to other studies, there is clear room for improvement.
+Although the percentage of articles that shared both data and code (61\%) and articles that could be computationally reproduced (54\%) was relatively high compared to other studies, there is clear room for improvement.
 We provide practical recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.
 
-keywords          : "reproducibility, Registered Reports, data sharing, open science"
-wordcount         : 4926
+}
 
-bibliography      : ["reproducing_registered_reports.bib"]
-
-figsintext        : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-lineno            : no
-mask              : no
-
-class             : "jou, a4paper"
-output            : papaja::apa6_pdf
----
-```{r load_packages, include=FALSE}
-
-library(readxl)
-library(here)
-library(irr)
-
-all_data <- read_excel("Data_for_Analysis_of_Open_Data_and_Computational_Reproducibility_in_Registered_Reports_in_Psychology.xlsx", n_max = 62)
-
-#Count how many papers have data available
-availability <- sum(all_data$availability)
-
-#Calculate number of studies using spss, r, or both.
-spss_or_r_or_jasp <- sum(all_data$programming_language == "spss", na.rm = TRUE) + sum(all_data$programming_language == "R", na.rm = TRUE) + 
-sum(all_data$programming_language == "R, spss", na.rm = TRUE) + sum(all_data$programming_language == "JASP", na.rm = TRUE)
-
-#Calculate time for subsets of spss and r for po who reproduced both.
-time_spss_po <- subset(all_data$time_reproducing_po, all_data$programming_language == "spss")
-time_r_po <- subset(all_data$time_reproducing_po, all_data$programming_language == "R")
-time_jasp_po <- subset(all_data$time_reproducing_po, all_data$programming_language == "JASP")
-
-#Create subgroups to report reproducibility per language
-run_script_spss <- subset(all_data$run_script_final, all_data$programming_language == "spss")
-run_script_r <- subset(all_data$run_script_final, all_data$programming_language == "R")
-run_script_r_spss <- subset(all_data$run_script_final, all_data$programming_language == "R, spss")
-run_script_jasp <- subset(all_data$run_script_final, all_data$programming_language == "JASP")
-
-# Compute average time for all coders for all studies
-average_time <- mean(c(all_data$time_reproducing_po, all_data$time_reproducing_nc, all_data$time_reproducing_jg, all_data$time_reproducing_dl), na.rm = TRUE)
-
-```
+\begin{document}
+\maketitle
 
 Researchers are currently exploring ways to make science more open and transparent.
-Among novel developments such as pre-registration, pre-prints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., [@morey_peer_2016].
+Among novel developments such as pre-registration, pre-prints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., (Morey et al., 2016).
 Sharing data and analysis code with scientific publications allows others to more easily reproduce, check, and build on existing work.
@@
 The availability of analysis code makes it possible for peers to check and correct published findings.
-According to @kitzes_practice_2017, computational reproducibility means that ”a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.” For scientific research to be computationally reproducible, the data and code needs to be shared.
+According to Kitzes, Turek, and Deniz (2017), computational reproducibility means that ''a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.'' For scientific research to be computationally reproducible, the data and code needs to be shared.
 
@@
 Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the published article.
-@hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal *Cognition*.
+Hardwicke et al.
+(2018) examined the reproducibility of 35 articles published in the journal \emph{Cognition}.
 Eleven articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance.
-Hardwicke et al.
-(2018) estimated that it took between 2-4 hours to reproduce the reported results, but they did not record the exact time.
-@stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals.
+Hardwicke et al.~(2018) estimated that it took between 2-4 hours to reproduce the reported results, but they did not record the exact time.
+Stockemer, Koehler, and Lentz (2018) analyzed reproducibility in all articles published in 2015 in three political science journals.
 They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one could not be reproduced due to a lack of a software license, and 16 articles could not be reproduced with access to the required software.
 For the remaining articles, 32 could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results.
-@stodden_empirical_2018 analyzed data availability in the journal *Science* in 2011-2012 and found that 26 of 204 (or 13%) of articles provided information to retrieve data and/or code without contacting the authors.
-For all datasets they acquired after e-mailing authors for data and code, 26% was estimated to be computationally reproducible.
+Stodden, Seiler, and Ma (2018) analyzed data availability in the journal \emph{Science} in 2011-2012 and found that 26 of 204 (or 13\%) of articles provided information to retrieve data and/or code without contacting the authors.
+For all datasets they acquired after e-mailing authors for data and code, 26\% was estimated to be computationally reproducible.
 These studies reveal that there is clear room for improvement in how reproducible published articles are.
@@
 Registered Reports are a novel development in psychology.
-Before data collection commences, the introduction and methods are peer-reviewed, after which authors can receive an 'in principle acceptance'.
-This means the article will be published as long as the authors follow their preregistered data collection and analysis plan [@chambers_instead_2014; @nosek_registered_2014].
+Before data collection commences, the introduction and methods are peer-reviewed, after which authors can receive an \enquote{in principle acceptance}.
+This means the article will be published as long as the authors follow their preregistered data collection and analysis plan (Chambers, Feredoes, Muthukumaraswamy, \& Etchells, 2014; Nosek \& Lakens, 2014).
 The population of Registered Reports in psychology is still relatively small (91 Registered Reports had been published as of February 22, 2018), which makes it possible to examine it in full.
@@
 We assumed that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
-In line with our assumptions, `r sum(all_data$availability, na.rm = TRUE)` out of `r length(all_data$doi)` articles in our final dataset shared data and code (`r round(100*sum(all_data$availability, na.rm = TRUE)/length(all_data$doi),1)`%).
-In comparison, after the journal *Cognition* introduced a mandatory data sharing policy, 136 out of 174 articles (78.2%) had a data availability statement, 85 of 174 articles (49%) had reusable data, and only 18 out of 174 articles (10.3%) provided the analysis code (Hardwicke et al., 2018).
+In line with our assumptions, 43 out of 62 articles in our final dataset shared data and code (69.40\%).
+In comparison, after the journal \emph{Cognition} introduced a mandatory data sharing policy, 136 out of 174 articles (78.2\%) had a data availability statement, 85 of 174 articles (49\%) had reusable data, and only 18 out of 174 articles (10.3\%) provided the analysis code (Hardwicke et al., 2018).
 To evaluate the reproducibility of findings published in Registered Reports, we examined if data could be located, were available at the indicated location, could be opened in open-source software, were documented well enough to be understandable, and could be used to reproduce the main analyses reported in the published manuscript.
 
-### The Current Research
+\hypertarget{the-current-research}{%
+\subsubsection{The Current Research}\label{the-current-research}}
 
@@
 
-### Method
+\hypertarget{method}{%
+\subsubsection{Method}\label{method}}
 
-To find Registered Reports published in psychology we drew from a database of registered reports maintained by by Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
+To find Registered Reports published in psychology we drew from a database of registered reports maintained by by Center for Open Science.\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
 Eighty-one articles in this database were published in the psychological literature.
-We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018].
+We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports (Hagger et al., 2016) and Many Labs projects (Klein et al., 2014, 2018).
 Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports.
-This left `r length(all_data$doi)` studies in our sample.
-When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, Matlab), which led to the exclusion of `r sum(all_data$included_language == FALSE, na.rm = TRUE)` additional studies.
+This left 62 studies in our sample.
+When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, Matlab), which led to the exclusion of 5 additional studies.
 
-### Results
+\hypertarget{results}{%
+\subsubsection{Results}\label{results}}
 
-We set out to reproduce the `r length(all_data$doi)` papers that met our inclusion criteria.
+We set out to reproduce the 62 papers that met our inclusion criteria.
 For each article we coded whether the data and code were (a) linked, (b) available, (c) not software-specific, (d) understandable, and (e) reproducible.
-These five categories were inspired by FAIR data principles [@wilkinson_fair_2016] that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles.
+These five categories were inspired by FAIR data principles (Wilkinson et al., 2016) that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles.
 Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of meta-data (which is missing for practically all datasets).
@@
 Ideally, such a link consists of a stable digital object identifier (DOI).
-A hyperlink to a website that contains the data and script also suffices, although normal hyperlinks are known to break over time [@gertler_reference_2017].
+A hyperlink to a website that contains the data and script also suffices, although normal hyperlinks are known to break over time (Gertler \& Bullock, 2017).
 
-Of the `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to data and/or code in the article.
+Of the 62 papers, 45 linked to data and/or code in the article.
 Linking to data does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable.
@@
 For one paper the data was linked but not available, as the data was embargoed until a future date.
-Altogether, data was available for `r sum(all_data$availability)` out of `r length(all_data$doi)` papers.
+Altogether, data was available for 43 out of 62 papers.
 
@@
 The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files that were analyzed in matlab, which we could not reproduce using open source software.
-This left `r sum(all_data$not_software_specific, na.rm = TRUE)` papers where data was available in a non-software-specific format.
+This left 42 papers where data was available in a non-software-specific format.
 
@@
 
-\caption{Of all articles in the Registered Report database 79 were psychology related, and `r length(all_data$doi)` were registered reports not part of a multi-lab Registered Replication Report.
-Of these `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to the data.
-After searching the OSF, data was available for `r sum(all_data$availability)` studies.
-Of these datasets, `r sum(all_data$understandable, na.rm = TRUE)` were documented well enough, for example through a codebook, so that variables were understandable.
-Of the `r length(all_data$doi)` papers `r sum(all_data$analysis_script_included, na.rm = TRUE)` shared the analysis script and data, for which `r spss_or_r_or_jasp` were in SPSS, R or JASP.
-Of these, the analysis script could be run for `r sum(all_data$run_script_final, na.rm = TRUE)`, of which `r sum(all_data$reproducible_final, na.rm = TRUE)` reproduced all main results.
+\caption{Of all articles in the Registered Report database 79 were psychology related, and 62 were registered reports not part of a multi-lab Registered Replication Report.
+Of these 62 papers, 45 linked to the data.
+After searching the OSF, data was available for 43 studies.
+Of these datasets, 21 were documented well enough, for example through a codebook, so that variables were understandable.
+Of the 62 papers 40 shared the analysis script and data, for which 35 were in SPSS, R or JASP.
+Of these, the analysis script could be run for 30, of which 19 reproduced all main results.
 }
@@
 If the variables are not clearly described (e.g., the dataset consists of variables identified by abbreviations that only make sense to the original researcher), other researchers will not be able to reuse the data to answer novel questions.
-In our analyses, data were scored as 'understandable' when all variables were clearly named (e.g., 'Condition') and the values for variables were labeled (e.g., 0 = control, 1 = experimental).
-Out of the `r sum(all_data$not_software_specific, na.rm = TRUE)` papers with available data in a format that was not software specific, only `r sum(all_data$understandable, na.rm = TRUE)` datasets were described in enough detail to be understandable.
+In our analyses, data were scored as \enquote{understandable} when all variables were clearly named (e.g., \enquote{Condition}) and the values for variables were labeled (e.g., 0 = control, 1 = experimental).
+Out of the 42 papers with available data in a format that was not software specific, only 21 datasets were described in enough detail to be understandable.
 This highlights the importance of adding a codebook with a datafile.
-For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript) see @arslan_how_2019.
+For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript) see Arslan (2019).
 
-Finally, we examined how many of the `r sum(all_data$not_software_specific, na.rm = TRUE)` non-software-specific papers could be reproduced.
+Finally, we examined how many of the 42 non-software-specific papers could be reproduced.
 It is possible that running the code on the data reproduces all analyses, even when the data file itself is not understandable (i.e., the data columns are not labeled).
 Two authors coded SPSS, R, and JASP analyses regarding (a) the executability of the script, and (b) the reproducibility of the results.
-After the initial coding, inter-rater reliability was low (`r round(agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_jg == FALSE))$value,0)`% agreement on executability, and `r round(agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_jg == FALSE))$value,0)`% agreement on reproducibility for SPSS scripts, `r round(agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_nc == FALSE))$value,0)`% agreement on executability, and `r round(agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_nc == FALSE))$value,0)`% agreement on reproducibility for R scripts).
+After the initial coding, inter-rater reliability was low (60\% agreement on executability, and 55\% agreement on reproducibility for SPSS scripts, 75\% agreement on executability, and 56\% agreement on reproducibility for R scripts).
 This initial low agreement provided two important insights about the definition of reproducibility and executability on the one hand, and the role of expertise on the other hand.
 
-We used a dichotomous coding scheme to when coding whether the script could be executed whether the results could be reproduced ('yes' or 'no'), but coders often reported 'partial' reproducibility.
+We used a dichotomous coding scheme to when coding whether the script could be executed whether the results could be reproduced (\enquote{yes} or \enquote{no}), but coders often reported \enquote{partial} reproducibility.
 Code often needed minor adjustments to run on the data, such as changing file locations, or loading packages in R, and coders sometimes took different approaches to how much they would adjust the code to make it run on the data.
 Furthermore, coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article.
-After evaluating our initial coding round, we considered an article was reproducible when we could get the same *main results* as represented in the paper with at best *minor changes* to the analysis scripts.
+After evaluating our initial coding round, we considered an article was reproducible when we could get the same \emph{main results} as represented in the paper with at best \emph{minor changes} to the analysis scripts.
 This means we considered the analysis reproducible, even if variables could only be found with reasonable effort or by making assumptions about how variable names mapped onto variables reported in the data analysis.
@@
 
-All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g.
-overlooked script files).
+All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g.~overlooked script files).
 The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve).
@@
 For each article two coders examined whether the code could be run on the data.
-Of the original `r length(all_data$doi)` articles, `r sum(all_data$included_language == FALSE, na.rm = TRUE, na.rm = TRUE)` used Matlab and Python and were excluded from the analysis due to a lack of expertise in our team with these languages.
-In total code and data were available for `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)` articles, of which `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` used R, SPSS, or JASP.
-We were able to run the code for `r sum(all_data$run_script_final == TRUE, na.rm = TRUE)` out of the `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` articles that used SPSS, R, and JASP.
-R was used as a coding language in `r length(run_script_r)`, of which `r sum(run_script_r)` scripts could be run on the data, `r length(run_script_spss)` papers used SPSS, for `r sum(run_script_spss)` of which the script could be run, and `r length(run_script_r_spss)` papers used both SPSS and R, for which the scripts could be run for all `r sum(run_script_r_spss)` papers.
+Of the original 62 articles, 5 used Matlab and Python and were excluded from the analysis due to a lack of expertise in our team with these languages.
+In total code and data were available for 38 articles, of which 35 used R, SPSS, or JASP.
+We were able to run the code for 30 out of the 35 articles that used SPSS, R, and JASP.
+R was used as a coding language in 13, of which 10 scripts could be run on the data, 17 papers used SPSS, for 15 of which the script could be run, and 3 papers used both SPSS and R, for which the scripts could be run for all 3 papers.
 JASP does not seperate the data and code, but instead stores both in a single JASP file.
@@
 It is always clear which settings were used to generate results.
-Because of this useful feature, the `r sum(run_script_jasp)` articles that relied on JASP for the analyses always allowed us to reproduce the analyses.
+Because of this useful feature, the 2 articles that relied on JASP for the analyses always allowed us to reproduce the analyses.
 
@@
 Some analyses in a paper might not be part of the code or the output.
-We found that `r sum(all_data$reproducible_final, na.rm = TRUE)` out of `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` papers (`r round(100*sum(all_data$reproducible_final, na.rm = TRUE)/sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE),1)`%) that included their data and code could be used to reproduce the main results in the article.
-The average time to reproduce analyses reported in R was `r round(mean(time_r_po, na.rm = TRUE),2)` minutes for the first coder (SD = `r round(sd(time_r_po, na.rm = TRUE),2)`) and `r round(mean(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)` minutes (SD =  `r round(sd(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)`) for the second coder.
-Reproducing the SPSS analysis took on average `r round(mean(time_spss_po, na.rm = TRUE),2)` minutes (SD = `r round(sd(time_spss_po, na.rm = TRUE),2)`) for the first coder and  `r round(mean(as.numeric(all_data$time_reproducing_jg), na.rm = TRUE),2)` minutes (SD = `r round(sd(as.numeric(all_data$time_reproducing_jg), na.rm = TRUE),2)`) for the second coder.
+We found that 19 out of 35 papers (54.30\%) that included their data and code could be used to reproduce the main results in the article.
+The average time to reproduce analyses reported in R was 27.08 minutes for the first coder (SD = 28.55) and 32.50 minutes (SD = 20.95) for the second coder.
+Reproducing the SPSS analysis took on average 17.35 minutes (SD = 9.54) for the first coder and 25.50 minutes (SD = 9.72) for the second coder.
 Most of the time was spent on matching output from the statistical analyses to the analyses reported in the manuscript.
@@
 
-### Discussion
+\hypertarget{discussion}{%
+\subsubsection{Discussion}\label{discussion}}
 
-We analyzed data and scripts of `r length(all_data$doi)` Registered Reports to examine how many authors shared their data and code, and how often main results reported in the manuscript could be reproduced.
-In total, `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)` out of `r length(all_data$doi)` (or `r round(100*sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)/length(all_data$doi),1)`%) of the articles shared the underlying data and the code that was used to generate the results.
-Of the papers that shared both the data and the analysis code and used software we had experience with, we could reproduce the main results for `r round(100*sum(all_data$reproducible_final, na.rm = TRUE)/sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE),1)`% of the papers.
-Authors of Registered Reports in psychology seem to voluntarily choose to share data and code relatively often compared to authors of articles in political science [@stockemer_data_2018].
+We analyzed data and scripts of 62 Registered Reports to examine how many authors shared their data and code, and how often main results reported in the manuscript could be reproduced.
+In total, 38 out of 62 (or 61.30\%) of the articles shared the underlying data and the code that was used to generate the results.
+Of the papers that shared both the data and the analysis code and used software we had experience with, we could reproduce the main results for 54.30\% of the papers.
+Authors of Registered Reports in psychology seem to voluntarily choose to share data and code relatively often compared to authors of articles in political science (Stockemer et al., 2018).
 Compared to authors of non-registered reports in psychology, voluntary data and code sharing is also relatively high, as is the reproducibility rate (taking into account that we reproduced articles without contacting the original authors).
-The reproducibility rate was higher than the 31% rate observed by Hardwicke et al.
-(2018), and both voluntary data sharing as reproducibility were higher than in the sample of papers from the journal *Science* in 2011-2012 analyzed in @stodden_empirical_2018.
+The reproducibility rate was higher than the 31\% rate observed by Hardwicke et al.~(2018), and both voluntary data sharing as reproducibility were higher than in the sample of papers from the journal \emph{Science} in 2011-2012 analyzed in Stodden et al.
+(2018).
 
@@
 One of the main goals of our project was to identify ways to improve the reproducibility of published articles.
-We encountered several common issues that made results reported in Registered Reports difficult to reproduce (cf.
-Hardwicke et al., 2018).
+We encountered several common issues that made results reported in Registered Reports difficult to reproduce (cf.~Hardwicke et al., 2018).
 This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output anaysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process.
@@
 Furthermore, when there are multiple datafiles, researchers should provide a clear description of what each datafile contains, for example in a README file in the root directory of the data folder.
-@le_open_2018 provides useful guidelines to create codebooks in his Open Science Manual.
-A good example of a codebook can be found as part of the materials of @wesselmann_revisiting_2014.
+Le (2018) provides useful guidelines to create codebooks in his Open Science Manual.
+A good example of a codebook can be found as part of the materials of Wesselmann et al.
+(2014).
 Creating a codebook should be considered a best practice when sharing data.
@@
 Well-annotated code makes clear what the analysis code does, in which order it should be run, and which output each section of analysis code generates.
-A good example of well-annotated code can be found in the materials of @weston_role_2018.
+A good example of well-annotated code can be found in the materials of Weston and Jackson (2018).
 It helps to make clear how the analysis code relates to the analyses reported in the paper, to make it easier for others to identify which code generates which results in the paper.
@@
 Explicitly linking code in the analysis script to the final manuscript also helps researchers to check whether all results in the article are reproduced by the shared code.
-An example of a data analysis file that clearly links the code to the final articles can be found in the materials of @voorspoels_can_2014.
+An example of a data analysis file that clearly links the code to the final articles can be found in the materials of Voorspoels, Bartlema, and Vanpaemel (2014).
 If analyses are performed that are not included in the manuscript, this should be stated explicitly (e.g., assumption checks, exploratory analyses, etc.).
@@
 Because packages update, it is necessary to report the version numbers of packages that were used (for example using packrat of copying the output of the the sessionInfo() function as a comment in the script).
-Remember that folder names and folder structures differ between computers, and therefore you should use relative locations (and not “c:/user/myfolder/code”).
-RStudio projects and the 'here' package provide an easy way to use relative paths.
+Remember that folder names and folder structures differ between computers, and therefore you should use relative locations (and not \enquote{c:/user/myfolder/code}).
+RStudio projects and the \enquote{here} package provide an easy way to use relative paths.
 When multiple scripts are used in the analysis, include the order in which scripts should be performed on the data in a README file.
-RMarkdown files provide a useful way to share clearly annotated code and structure the difference steps in the data analysis, for example as done by @campbell_self-esteem_2018.
+RMarkdown files provide a useful way to share clearly annotated code and structure the difference steps in the data analysis, for example as done by Campbell et al.
+(2018).
 
@@
 The absence of understandable variable and value labels in more than half of all SPSS scripts hindered our attempts to reproduce these results.
-Often the only time-efficient way to check if an article was reproducible so was to run the whole script, and search try to identify specific *p*-values or effect sizes from the article in the SPSS output.
+Often the only time-efficient way to check if an article was reproducible so was to run the whole script, and search try to identify specific \emph{p}-values or effect sizes from the article in the SPSS output.
 SPSS users should take greater care to clearly organize their analysis scripts by adding comments or a README file that links results generated by the SPSS script to the analyses reported in the manuscript.
@@
 
-### Limitations and Future Research
+\hypertarget{limitations-and-future-research}{%
+\subsubsection{Limitations and Future Research}\label{limitations-and-future-research}}
 
@@
 Registered Reports are written by a diverse set of researchers, working in different subfields in psychology, and it would be interesting for future research to qualitatively examine the motivations of researchers who published Registered Reports for sharing or not sharing data and code.
-There are several good reasons why data can not be shared, and researchers should be able to explain why data is not available when they publish a scientific article [@morey_peer_2016].
+There are several good reasons why data can not be shared, and researchers should be able to explain why data is not available when they publish a scientific article (Morey et al., 2016).
 
@@
 In addition to the recommendations we have provided above, we believe novel technological solutions might improve the reproducibility of research articles.
-For example, CodeOcean is an online, cloud based, computational reproducibility platform [@clyburne-sherin_computational_2018].
+For example, CodeOcean is an online, cloud based, computational reproducibility platform (Clyburne-Sherin, Fei, \& Green, 2018).
 It provides a code environment (or container) that runs online, which means that researchers using CodeOcean do not have to download data, code, or software, but can analyze the data in their browser.
@@
 This saves a lot of time matching the analysis code to the reported results, and thus speeds up the process of checking whether all results reported in the manuscripts are reproduced by the code.
-The current manuscript is an example of a reproducible RMarkdown file.^[see https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd] Additional solutions that help researchers to share reproducible analyses might become available in the future.
+The current manuscript is an example of a reproducible RMarkdown file.\footnote{see \url{https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd}} Additional solutions that help researchers to share reproducible analyses might become available in the future.
 
 Finally, journals who value reproducibility might find it worthwhile to check whether the data and analysis code shared with a submission can be used to reproduce the results.
-The average time it took our team to check that the analysis code could reproduce the results reported in the paper was `r round(average_time,0)` minutes.
+The average time it took our team to check that the analysis code could reproduce the results reported in the paper was 24 minutes.
 This is slightly shorter than the time it took Hardwicke and colleagues (2018), who estimated (without keeping track of the time explicitly) that reproducibility reports took between 2 and 25 person-hours, depending on whether the paper eventually fell in the reproducible or not-reproducible category, and whether author assistance was needed.
-The main difference might be that we did not write 'reproducibility reports' for each article.
+The main difference might be that we did not write \enquote{reproducibility reports} for each article.
 Documenting the process of reproducing a paper adds transparency and allows others to check the the decisions about every value in an article.
@@
 The required time might be reduced by explicitly asking authors to submit files in a format or structure that facilitates such checks, or automating part of the work that is needed to check the reproducibility of results.
-Overall, we feel that the time required for a basic check of the reproducibility of manuscripts (i.e., where one checks whether the *main* results in the paper are reproduced by the analysis scripts, but without documenting this step at the level of each individual number) is not an insurmountable problem for scientific journals that aim to add value, and would substantially improve the computational reproducibility of the published literature.
+Overall, we feel that the time required for a basic check of the reproducibility of manuscripts (i.e., where one checks whether the \emph{main} results in the paper are reproduced by the analysis scripts, but without documenting this step at the level of each individual number) is not an insurmountable problem for scientific journals that aim to add value, and would substantially improve the computational reproducibility of the published literature.
 
@@
 
-# References
+\hypertarget{references}{%
+\section{References}\label{references}}
 
@@
 \setlength{\leftskip}{0.5in}
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-arslan_how_2019}{}%
+Arslan, R.
+C.
+(2019).
+How to Automatically Document Data With the codebook Package to Facilitate Data Reuse.
+\emph{Advances in Methods and Practices in Psychological Science}, 2515245919838783.
+doi:\href{https://doi.org/10.1177/2515245919838783}{10.1177/2515245919838783}
+
+\leavevmode\hypertarget{ref-campbell_self-esteem_2018}{}%
+Campbell, L., Balzarini, R.
+N., Kohut, T., Dobson, K., Hahn, C.
+M., Moroz, S.
+E., \& Stanton, S.
+C.
+E.
+(2018).
+Self-esteem, relationship threat, and dependency regulation: Independent replication of Murray, Rose, Bellavia, Holmes, and Kusche (2002) Study 3.
+\emph{Journal of Research in Personality}, \emph{72}, 5--9.
+doi:\href{https://doi.org/10.1016/j.jrp.2017.04.001}{10.1016/j.jrp.2017.04.001}
+
+\leavevmode\hypertarget{ref-chambers_instead_2014}{}%
+Chambers, C.
+D., Feredoes, E., Muthukumaraswamy, S.
+D., \& Etchells, P.
+(2014).
+Instead of "playing the game" it is time to change the rules: Registered Reports at AIMS Neuroscience and beyond.
+\emph{AIMS Neuroscience}, \emph{1}, 4--17.
+doi:\href{https://doi.org/10.3934/Neuroscience2014.1.4}{10.3934/Neuroscience2014.1.4}
+
+\leavevmode\hypertarget{ref-clyburne-sherin_computational_2018}{}%
+Clyburne-Sherin, A., Fei, X., \& Green, S. A. (2018). Computational Reproducibility via Containers in Social Psychology. doi:\href{https://doi.org/10.31234/osf.io/mf82t}{10.31234/osf.io/mf82t}
+
+\leavevmode\hypertarget{ref-gertler_reference_2017}{}%
+Gertler, A.
+L., \& Bullock, J.
+G.
+(2017).
+Reference Rot: An Emerging Threat to Transparency in Political Science.
+\emph{PS: Political Science \& Politics}, \emph{50}(1), 166--171.
+doi:\href{https://doi.org/10.1017/S1049096516002353}{10.1017/S1049096516002353}
+
+\leavevmode\hypertarget{ref-hagger_multilab_2016}{}%
+Hagger, M.
+S., Chatzisarantis, N.
+L.
+D., Alberts, H., Anggono, C.
+O., Batailler, C., Birt, A.
+R., \ldots{} Zwienenberg, M.
+(2016).
+A Multilab Preregistered Replication of the Ego-Depletion Effect.
+\emph{Perspectives on Psychological Science}, \emph{11}(4), 546--573.
+doi:\href{https://doi.org/10.1177/1745691616652873}{10.1177/1745691616652873}
+
+\leavevmode\hypertarget{ref-hardwicke_data_2018}{}%
+Hardwicke, T.
+E., Mathur, M.
+B., MacDonald, K., Nilsonne, G., Banks, G.
+C., Kidwell, M.
+C., \ldots{} Frank, M.
+C.
+(2018).
+Data availability, reusability, and analytic reproducibility: Evaluating the impact of a mandatory open data policy at the journal Cognition.
+\emph{Open Science}, \emph{5}(8), 180448.
+doi:\href{https://doi.org/10.1098/rsos.180448}{10.1098/rsos.180448}
+
+\leavevmode\hypertarget{ref-kitzes_practice_2017}{}%
+Kitzes, J., Turek, D., \& Deniz, F. (2017). \emph{The Practice of Reproducible Research: Case Studies and Lessons from the Data-Intensive Sciences}. Univ of California Press.
+
+\leavevmode\hypertarget{ref-klein_investigating_2014}{}%
+Klein, R.
+A., Ratliff, K.
+A., Vianello, M., Adams, R.
+B., Bahník, Š., Bernstein, M.
+J., \ldots{} Nosek, B.
+A.
+(2014).
+Investigating Variation in Replicability.
+\emph{Social Psychology}, \emph{45}(3), 142--152.
+doi:\href{https://doi.org/10.1027/1864-9335/a000178}{10.1027/1864-9335/a000178}
+
+\leavevmode\hypertarget{ref-klein_many_2018}{}%
+Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams, R.
+B., Alper, S., \ldots{} Nosek, B.
+A.
+(2018).
+Many Labs 2: Investigating Variation in Replicability Across Samples and Settings.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 443--490.
+doi:\href{https://doi.org/10.1177/2515245918810225}{10.1177/2515245918810225}
+
+\leavevmode\hypertarget{ref-le_open_2018}{}%
+Le, B. (2018, May). Open Science Manual. https://bit.ly/2w2F6Xu.
+
+\leavevmode\hypertarget{ref-morey_peer_2016}{}%
+Morey, R.
+D., Chambers, C.
+D., Etchells, P.
+J., Harris, C.
+R., Hoekstra, R., Lakens, D., \ldots{} others.
+(2016).
+The Peer Reviewers' Openness Initiative: Incentivizing open research practices through peer review.
+\emph{Royal Society Open Science}, \emph{3}(1), 150547.
+
+\leavevmode\hypertarget{ref-nosek_registered_2014}{}%
+Nosek, B. A., \& Lakens, D. (2014). Registered Reports. \emph{Social Psychology}, \emph{45}(3), 137--141. doi:\href{https://doi.org/10.1027/1864-9335/a000192}{10.1027/1864-9335/a000192}
+
+\leavevmode\hypertarget{ref-stockemer_data_2018}{}%
+Stockemer, D., Koehler, S., \& Lentz, T.
+(2018).
+Data Access, Transparency, and Replication: New Insights from the Political Behavior Literature.
+\emph{PS: Political Science \& Politics}, \emph{51}(4), 799--803.
+doi:\href{https://doi.org/10.1017/S1049096518000926}{10.1017/S1049096518000926}
+
+\leavevmode\hypertarget{ref-stodden_empirical_2018}{}%
+Stodden, V., Seiler, J., \& Ma, Z.
+(2018).
+An empirical analysis of journal policy effectiveness for computational reproducibility.
+\emph{Proceedings of the National Academy of Sciences}, \emph{115}(11), 2584--2589.
+doi:\href{https://doi.org/10.1073/pnas.1708290115}{10.1073/pnas.1708290115}
+
+\leavevmode\hypertarget{ref-voorspoels_can_2014}{}%
+Voorspoels, W., Bartlema, A., \& Vanpaemel, W.
+(2014).
+Can race really be erased?
+A pre-registered replication study.
+\emph{Frontiers in Psychology}, \emph{5}.
+doi:\href{https://doi.org/10.3389/fpsyg.2014.01035}{10.3389/fpsyg.2014.01035}
+
+\leavevmode\hypertarget{ref-wesselmann_revisiting_2014}{}%
+Wesselmann, E.
+D., Williams, K.
+D., Pryor, J.
+B., Eichler, F.
+A., Gill, D.
+M., \& Hogue, J.
+D.
+(2014).
+Revisiting Schachter's Research on Rejection, Deviance, and Communication (1951).
+\emph{Social Psychology}, \emph{45}(3), 164--169.
+doi:\href{https://doi.org/10.1027/1864-9335/a000180}{10.1027/1864-9335/a000180}
+
+\leavevmode\hypertarget{ref-weston_role_2018}{}%
+Weston, S.
+J., \& Jackson, J.
+J.
+(2018).
+The role of vigilance in the relationship between neuroticism and health: A registered report.
+\emph{Journal of Research in Personality}, \emph{73}, 27--34.
+doi:\href{https://doi.org/10.1016/j.jrp.2017.10.005}{10.1016/j.jrp.2017.10.005}
+
+\leavevmode\hypertarget{ref-wilkinson_fair_2016}{}%
+Wilkinson, M.
+D., Dumontier, M., Aalbersberg, I.
+J., Appleton, G., Axton, M., Baak, A., \ldots{} Mons, B.
+(2016).
+The FAIR Guiding Principles for scientific data management and stewardship.
+\emph{Scientific Data}, \emph{3}, 160018.
+doi:\href{https://doi.org/10.1038/sdata.2016.18}{10.1038/sdata.2016.18}
+
+\end{document}

### 2019-05-23 reproducing_registered_reports.Rmd
preprint

@@
 Hardwicke et al.
-(2018) estimated that it took between 2-4 hours to reproduce the reported results, but they did not record the exact time.
+(2018) estimated that it took between 2-25 hours to reproduce the reported results, but they did not record the exact time.
 @stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals.
@@
 
-To find Registered Reports published in psychology we drew from a database of registered reports maintained by by Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
+To find Registered Reports published in psychology we drew from a database of registered reports maintained by the Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
 Eighty-one articles in this database were published in the psychological literature.
@@
 \begin{center}
-\includegraphics{fig1.png}
+\includegraphics[width=\textwidth]{fig1.png}
 
@@
 
-One of the reasons to share data is allow other researchers to reproduce the reported results.
+One of the reasons to share data is to allow other researchers to reproduce the reported results.
 Another important reason to share data is to enable other researchers to reuse the data.
@@
 For the current analysis, we considered a study reproducible as long as the more experienced coder could reproduce the main results.
-
 All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g.
@@
 Hardwicke et al., 2018).
-This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output anaysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process.
+This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output analysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process.
 We will discuss each of these points below, and link to examples of good practices that we encountered.
@@
 In addition to the recommendations we have provided above, we believe novel technological solutions might improve the reproducibility of research articles.
-For example, CodeOcean is an online, cloud based, computational reproducibility platform [@clyburne-sherin_computational_2018].
-It provides a code environment (or container) that runs online, which means that researchers using CodeOcean do not have to download data, code, or software, but can analyze the data in their browser.
-It is not yet possible to use SPSS within CodeOcean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.
-Another solution is RMarkdown which enable researchers to write fully reproducible manuscripts.
+For example, Code Ocean is an online, cloud based, computational reproducibility platform [@clyburne-sherin_computational_2018].
+It provides a code environment (or container) that runs online, which means that researchers using Code Ocean do not have to download data, code, or software, but can analyze the data in their browser.
+It is not yet possible to use SPSS within Code Ocean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.^[For a Code Ocean capsule reproducing this manuscript: https://codeocean.com/capsule/8580632/tree/v1] Another solution is RMarkdown which enable researchers to write fully reproducible manuscripts.
 RMarkdown files load the raw data and allow researchers to compute each number reported in the manuscript from the data, instead of copy-pasting values.
@@
 This saves a lot of time matching the analysis code to the reported results, and thus speeds up the process of checking whether all results reported in the manuscripts are reproduced by the code.
-The current manuscript is an example of a reproducible RMarkdown file.^[see https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd] Additional solutions that help researchers to share reproducible analyses might become available in the future.
+The current manuscript is an example of a reproducible RMarkdown file.^[See https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd] Additional solutions that help researchers to share reproducible analyses might become available in the future.
 

### 2019-05-23 reproducing_registered_reports.tex
preprint

@@
 Eleven articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance.
-Hardwicke et al.~(2018) estimated that it took between 2-4 hours to reproduce the reported results, but they did not record the exact time.
+Hardwicke et al.~(2018) estimated that it took between 2-25 hours to reproduce the reported results, but they did not record the exact time.
 Stockemer, Koehler, and Lentz (2018) analyzed reproducibility in all articles published in 2015 in three political science journals.
@@
 
-To find Registered Reports published in psychology we drew from a database of registered reports maintained by by Center for Open Science.\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
+To find Registered Reports published in psychology we drew from a database of registered reports maintained by the Center for Open Science.\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
 Eighty-one articles in this database were published in the psychological literature.
@@
 For the current analysis, we considered a study reproducible as long as the more experienced coder could reproduce the main results.
-
 All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g.~overlooked script files).
@@
 We encountered several common issues that made results reported in Registered Reports difficult to reproduce (cf.~Hardwicke et al., 2018).
-This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output anaysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process.
+This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output analysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process.
 We will discuss each of these points below, and link to examples of good practices that we encountered.
@@
 In addition to the recommendations we have provided above, we believe novel technological solutions might improve the reproducibility of research articles.
-For example, CodeOcean is an online, cloud based, computational reproducibility platform (Clyburne-Sherin, Fei, \& Green, 2018).
-It provides a code environment (or container) that runs online, which means that researchers using CodeOcean do not have to download data, code, or software, but can analyze the data in their browser.
-It is not yet possible to use SPSS within CodeOcean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.
-Another solution is RMarkdown which enable researchers to write fully reproducible manuscripts.
+For example, Code Ocean is an online, cloud based, computational reproducibility platform (Clyburne-Sherin, Fei, \& Green, 2018).
+It provides a code environment (or container) that runs online, which means that researchers using Code Ocean do not have to download data, code, or software, but can analyze the data in their browser.
+It is not yet possible to use SPSS within Code Ocean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.\footnote{For a Code Ocean capsule reproducing this manuscript: \url{https://codeocean.com/capsule/8580632/tree/v1}} Another solution is RMarkdown which enable researchers to write fully reproducible manuscripts.
 RMarkdown files load the raw data and allow researchers to compute each number reported in the manuscript from the data, instead of copy-pasting values.
@@
 This saves a lot of time matching the analysis code to the reported results, and thus speeds up the process of checking whether all results reported in the manuscripts are reproduced by the code.
-The current manuscript is an example of a reproducible RMarkdown file.\footnote{see \url{https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd}} Additional solutions that help researchers to share reproducible analyses might become available in the future.
+The current manuscript is an example of a reproducible RMarkdown file.\footnote{See \url{https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd}} Additional solutions that help researchers to share reproducible analyses might become available in the future.
 

### 2019-05-23 reproducing_registered_reports.Rmd
Update reproducing_registered_reports.Rmd
* Comma in abstract for clarity
* MATLAB is a capitalized trademark

@@
 We examined data and code sharing, as well as computational reproducibility of the main results without contacting the original authors, for Registered Reports published in the in psychological literature between 2014 and 2018.
-Of the 62 articles that met our inclusion criteria data was available for 40 articles, and analysis scripts for 43 articles.
+Of the 62 articles that met our inclusion criteria, data was available for 40 articles, and analysis scripts for 43 articles.
 For the 35 articles that shared both data and code and performed analyses in SPSS, R, or JASP, we could run the scripts for 30 articles, and reproduce the main results for 19 articles.
@@
 This left `r length(all_data$doi)` studies in our sample.
-When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, Matlab), which led to the exclusion of `r sum(all_data$included_language == FALSE, na.rm = TRUE)` additional studies.
+When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, MATLAB), which led to the exclusion of `r sum(all_data$included_language == FALSE, na.rm = TRUE)` additional studies.
 
@@
 Note that we had access to SPSS and therefore reproduced the analyses using the original .sps scripts where available.
-The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files that were analyzed in matlab, which we could not reproduce using open source software.
-This left `r sum(all_data$not_software_specific, na.rm = TRUE)` papers where data was available in a non-software-specific format.
+The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files that were analyzed in
+, which we could not reproduce using open source software. This left `r sum(all_data$not_software_specific, na.rm = TRUE)` papers where data was available in a non-software-specific format.
 
@@
 For each article two coders examined whether the code could be run on the data.
-Of the original `r length(all_data$doi)` articles, `r sum(all_data$included_language == FALSE, na.rm = TRUE, na.rm = TRUE)` used Matlab and Python and were excluded from the analysis due to a lack of expertise in our team with these languages.
+Of the original `r length(all_data$doi)` articles, `r sum(all_data$included_language == FALSE, na.rm = TRUE, na.rm = TRUE)` used MATLAB and Python and were excluded from the analysis due to a lack of expertise in our team with these languages.
 In total code and data were available for `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)` articles, of which `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` used R, SPSS, or JASP.

### 2019-07-11 reproducing_registered_reports.Rmd
Update reproducing_registered_reports.Rmd
Mostly grammatical changes. The ones that maybe should be rejected (or are non-obvious):
1) removed a bit about open-source languages --if you were using SPSS in the first-place, that wasn't a limitation
2) I took out one code chunk about JASP papers because it was creating "the 2 articles that relied on JASP" but in such a context, the number should be spelled out
Happy to discuss anything else!

@@
 Because most researchers have not been trained in computational reproducibility, it is important to evaluate current practices to identify practices that can be improved.
-We examined data and code sharing, as well as computational reproducibility of the main results without contacting the original authors, for Registered Reports published in the in psychological literature between 2014 and 2018.
+We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the in psychological literature between 2014 and 2018.
 Of the 62 articles that met our inclusion criteria, data was available for 40 articles, and analysis scripts for 43 articles.
-For the 35 articles that shared both data and code and performed analyses in SPSS, R, or JASP, we could run the scripts for 30 articles, and reproduce the main results for 19 articles.
+For the 35 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 30 articles, and reproduce the main results for 19 articles.
 Although the percentage of articles that shared both data and code (61%) and articles that could be computationally reproduced (54%) was relatively high compared to other studies, there is clear room for improvement.
@@
 Eleven articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance.
-Hardwicke et al.
-(2018) estimated that it took between 2-25 hours to reproduce the reported results, but they did not record the exact time.
+The authors estimated that it took between 2-25 hours to reproduce the reported results per article, but they did not record the exact time.
 @stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals.
@@
 Our main interest was to examine the computational reproducibility of the main analyses reported in published articles, without contacting the original authors.
-One of the main benefits of sharing data and code with the article (compared to making these files available upon request) is that results can be reproduced, and data reused even if the original author can no longer be reached.
+One of the main benefits of sharing data and code with an article (compared to making these files available upon request) is that results can be reproduced, and data reused even if the original author can no longer be reached.
+
 Registered Reports are a novel development in psychology.
-Before data collection commences, the introduction and methods are peer-reviewed, after which authors can receive an 'in principle acceptance'.
+Before data collection commences, the introduction and methods are peer-reviewed, after which authors can receive an 'in-principle acceptance'.
 This means the article will be published as long as the authors follow their preregistered data collection and analysis plan [@chambers_instead_2014; @nosek_registered_2014].
@@
 The novelty of Registered Reports may attract early adopters who are also exploring other novel developments aimed at improving research practices in psychology, such as data and code sharing.
-We assumed that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
-In line with our assumptions, `r sum(all_data$availability, na.rm = TRUE)` out of `r length(all_data$doi)` articles in our final dataset shared data and code (`r round(100*sum(all_data$availability, na.rm = TRUE)/length(all_data$doi),1)`%).
+We hypothesized that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
+In line with our hypothesis, `r sum(all_data$availability, na.rm = TRUE)` out of `r length(all_data$doi)` articles in our final dataset shared data and code (`r round(100*sum(all_data$availability, na.rm = TRUE)/length(all_data$doi),1)`%).
 In comparison, after the journal *Cognition* introduced a mandatory data sharing policy, 136 out of 174 articles (78.2%) had a data availability statement, 85 of 174 articles (49%) had reusable data, and only 18 out of 174 articles (10.3%) provided the analysis code (Hardwicke et al., 2018).
-To evaluate the reproducibility of findings published in Registered Reports, we examined if data could be located, were available at the indicated location, could be opened in open-source software, were documented well enough to be understandable, and could be used to reproduce the main analyses reported in the published manuscript.
+To evaluate the reproducibility of findings published in Registered Reports, we examined if data could be located, were available at the indicated location, could be opened in open-source or accessible software, were documented well enough to be understandable, and could be used to reproduce the main analyses reported in the published manuscript.
 
@@
 This left `r length(all_data$doi)` studies in our sample.
-When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, MATLAB), which led to the exclusion of `r sum(all_data$included_language == FALSE, na.rm = TRUE)` additional studies.
+When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, Matlab), which led to the exclusion of `r sum(all_data$included_language == FALSE, na.rm = TRUE)` additional studies.
 
@@
 These five categories were inspired by FAIR data principles [@wilkinson_fair_2016] that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles.
-Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of meta-data (which is missing for practically all datasets).
+Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of metadata (which is missing for practically all datasets).
 We considered data and code to be linked when the manuscript included a unique link to the data and scripts.
@@
 Note that we had access to SPSS and therefore reproduced the analyses using the original .sps scripts where available.
-The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files that were analyzed in
-, which we could not reproduce using open source software. This left `r sum(all_data$not_software_specific, na.rm = TRUE)` papers where data was available in a non-software-specific format.
+The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files that were analyzed in MATLAB, which we could not reproduce.
+This left `r sum(all_data$not_software_specific, na.rm = TRUE)` papers where data was available in a non-software-specific format.
 
@@
 Out of the `r sum(all_data$not_software_specific, na.rm = TRUE)` papers with available data in a format that was not software specific, only `r sum(all_data$understandable, na.rm = TRUE)` datasets were described in enough detail to be understandable.
-This highlights the importance of adding a codebook with a datafile.
-For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript) see @arslan_how_2019.
+This highlights the importance of adding a codebook with a datafile.^[For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript) see @arslan_how_2019.]
 
@@
 Furthermore, coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article.
-After evaluating our initial coding round, we considered an article was reproducible when we could get the same *main results* as represented in the paper with at best *minor changes* to the analysis scripts.
+After evaluating our initial coding round, we considered an article reproducible when we could get the same *main results* as represented in the paper with at best *minor changes* to the analysis scripts.
 This means we considered the analysis reproducible, even if variables could only be found with reasonable effort or by making assumptions about how variable names mapped onto variables reported in the data analysis.
@@
 It is always clear which settings were used to generate results.
-Because of this useful feature, the `r sum(run_script_jasp)` articles that relied on JASP for the analyses always allowed us to reproduce the analyses.
+Because of this useful feature, the two articles that relied on JASP for the analyses both allowed us to reproduce the analyses.
 
@@
 Based on our experiences, we have several specific recommendations for data analyzed in R.
-First of all, most code in R relies on specific libraries (or packages).
+First, most code in R relies on specific libraries (also called packages).
 List all the packages that the code needs to run at the top of the script.
@@
 
-The main aim of this article was not to accurately estimate mean reproducibility rates, but to see what current standards are, and how the reproducibility of research articles using the Registered Report format could be improved.
+The main aim of this article was not to accurately estimate reproducibility rates, but to see what current standards are, and how the reproducibility of research articles using the Registered Report format could be improved.
 The sample size is small, and it is doubtful whether an accurate estimate of the reproducibility of Registered Reports is of much value, beyond examining where most room for improvement is.

### 2019-07-11 reproducing_registered_reports.Rmd
Update reproducing_registered_reports.Rmd
Added text and citations for Binder and Whole Tale;
Replaced 'reproducible' in Rmarkdown with 'executable' because, IMO, the bulk of computational reproducibility for a language like R isn't knowing what order to run things in, and what's what (which Rmarkdown takes care of), but dependency management, which Rmarkdown does not. This is of course a debatable point...

--- 2019-05-23 reproducing_registered_reports.Rmd
@@
 It provides a code environment (or container) that runs online, which means that researchers using Code Ocean do not have to download data, code, or software, but can analyze the data in their browser.
-It is not yet possible to use SPSS within Code Ocean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.^[For a Code Ocean capsule reproducing this manuscript: https://codeocean.com/capsule/8580632/tree/v1] Another solution is RMarkdown which enable researchers to write fully reproducible manuscripts.
+It is not yet possible to use SPSS within Code Ocean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.^[For a Code Ocean capsule reproducing this manuscript: https://codeocean.com/capsule/8580632/tree/v1] Other platforms in the reproducibility space include Whole Tale [@brinckman2019computing], "a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage" (p.
+855); and Binder [@ragan2018binder], an open-source, browser-based tool for creating and sharing reproducible environments.
+
+Another useful technology is RMarkdown, which enable researchers to write fully executable manuscripts.
 RMarkdown files load the raw data and allow researchers to compute each number reported in the manuscript from the data, instead of copy-pasting values.

### 2019-08-19 reproducing_registered_reports.Rmd

--- 2019-07-11 reproducing_registered_reports.Rmd
@@
 It is always clear which settings were used to generate results.
-Because of this useful feature, the two articles that relied on JASP for the analyses both allowed us to reproduce the analyses.
+Because of this useful feature, the `r sum(run_script_jasp)` articles that relied on JASP for the analyses always allowed us to reproduce the analyses.
 

### 2019-09-08 reproducing_registered_reports.Rmd
revision including python scripts

@@
 We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the in psychological literature between 2014 and 2018.
-Of the 62 articles that met our inclusion criteria, data was available for 40 articles, and analysis scripts for 43 articles.
-For the 35 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 30 articles, and reproduce the main results for 19 articles.
-Although the percentage of articles that shared both data and code (61%) and articles that could be computationally reproduced (54%) was relatively high compared to other studies, there is clear room for improvement.
+Of the 62 articles that met our inclusion criteria, data was available for 40 articles, and analysis scripts for 37 articles.
+For the 35 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 articles, and reproduce the main results for 20 articles.
+Although the articles that shared both data and code (35 out of 62, or 56%) and articles that could be computationally reproduced (20 out of 35, or 57%) was relatively high compared to other studies, there is clear room for improvement.
 We provide practical recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.
@@
 
-#Calculate number of studies using spss, r, or both.
+#Calculate number of studies using spss, r, or both or matlab or python.
 spss_or_r_or_jasp <- sum(all_data$programming_language == "spss", na.rm = TRUE) + sum(all_data$programming_language == "R", na.rm = TRUE) + 
-sum(all_data$programming_language == "R, spss", na.rm = TRUE) + sum(all_data$programming_language == "JASP", na.rm = TRUE)
+sum(all_data$programming_language == "R, spss", na.rm = TRUE) + sum(all_data$programming_language == "JASP", na.rm = TRUE) + sum(all_data$programming_language == "matlab", na.rm = TRUE) + sum(all_data$programming_language == "Python", na.rm = TRUE)
 
@@
 run_script_jasp <- subset(all_data$run_script_final, all_data$programming_language == "JASP")
+run_script_matlab <- subset(all_data$run_script_final, all_data$programming_language == "matlab")
+run_script_python <- subset(all_data$run_script_final, all_data$programming_language == "Python")
 
 # Compute average time for all coders for all studies
-average_time <- mean(c(all_data$time_reproducing_po, all_data$time_reproducing_nc, all_data$time_reproducing_jg, all_data$time_reproducing_dl), na.rm = TRUE)
+average_time <- mean(c(all_data$time_reproducing_po, all_data$time_reproducing_nc, all_data$time_reproducing_jg, all_data$time_reproducing_dl, all_data$time_reproducing_sg), na.rm = TRUE)
 
@@
 We hypothesized that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
-In line with our hypothesis, `r sum(all_data$availability, na.rm = TRUE)` out of `r length(all_data$doi)` articles in our final dataset shared data and code (`r round(100*sum(all_data$availability, na.rm = TRUE)/length(all_data$doi),1)`%).
+In line with our hypothesis, `r sum(all_data$availability, na.rm = TRUE)` out of `r length(all_data$doi)` articles in our final dataset shared at least some of the data and code (`r round(100*sum(all_data$availability, na.rm = TRUE)/length(all_data$doi),1)`%).
 In comparison, after the journal *Cognition* introduced a mandatory data sharing policy, 136 out of 174 articles (78.2%) had a data availability statement, 85 of 174 articles (49%) had reusable data, and only 18 out of 174 articles (10.3%) provided the analysis code (Hardwicke et al., 2018).
@@
 This left `r length(all_data$doi)` studies in our sample.
-When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, Matlab), which led to the exclusion of `r sum(all_data$included_language == FALSE, na.rm = TRUE)` additional studies.
+When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of `r sum(all_data$included_language == FALSE, na.rm = TRUE)` additional study.
 
@@
 
-Of the `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to data and/or code in the article.
-Linking to data does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable.
+Of the `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to data and/or code that were part of the article.
+Linking to data or code does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable.
 For one article the link no longer worked (highlighting the need to use a stable DOI when linking to data).
@@
 For one paper the data was linked but not available, as the data was embargoed until a future date.
-Altogether, data was available for `r sum(all_data$availability)` out of `r length(all_data$doi)` papers.
+Altogether, some data or code was available for `r sum(all_data$availability)` out of `r length(all_data$doi)` papers.
+For `r sum(all_data$analysis_script_included == TRUE, na.rm = TRUE)` articles the available code contained the statistical analyses, and for `r sum(all_data$data_complete == TRUE, na.rm = TRUE)` all the required data files were available to reproduce the reported results (for `r sum(all_data$data_complete == TRUE & all_data$analysis_script_included == TRUE, na.rm = TRUE)` articles both data and code were available.
 
@@
 Note that we had access to SPSS and therefore reproduced the analyses using the original .sps scripts where available.
-The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files that were analyzed in MATLAB, which we could not reproduce.
-This left `r sum(all_data$not_software_specific, na.rm = TRUE)` papers where data was available in a non-software-specific format.
+The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files required dedicated EEG software and could not be reproduced (we could also not find the analysis code for this article).
 
@@
 \caption{Of all articles in the Registered Report database 79 were psychology related, and `r length(all_data$doi)` were registered reports not part of a multi-lab Registered Replication Report.
-Of these `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to the data.
-After searching the OSF, data was available for `r sum(all_data$availability)` studies.
-Of these datasets, `r sum(all_data$understandable, na.rm = TRUE)` were documented well enough, for example through a codebook, so that variables were understandable.
-Of the `r length(all_data$doi)` papers `r sum(all_data$analysis_script_included, na.rm = TRUE)` shared the analysis script and data, for which `r spss_or_r_or_jasp` were in SPSS, R or JASP.
-Of these, the analysis script could be run for `r sum(all_data$run_script_final, na.rm = TRUE)`, of which `r sum(all_data$reproducible_final, na.rm = TRUE)` reproduced all main results.
+Of these `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to the data or code.
+After searching the OSF, data or code was available for `r sum(all_data$availability)` studies, of which `r spss_or_r_or_jasp` articles used SPSS, R, Matlab, Python, or JASP.
+Of the `r length(all_data$doi)` papers `r sum(all_data$analysis_script_included, na.rm = TRUE)` shared the analysis script and `r sum(all_data$data_complete, na.rm = TRUE)` shared all data.
+The analysis script could be run for `r sum(all_data$run_script_final, na.rm = TRUE)` articles.
+For the `r sum(all_data$data_complete == TRUE & all_data$analysis_script_included == TRUE, na.rm = TRUE)` articles for which data and code were available, the main results could be reproduced for `r sum(all_data$reproducible_final, na.rm = TRUE)`.
 }
@@
 
-Finally, we examined how many of the `r sum(all_data$not_software_specific, na.rm = TRUE)` non-software-specific papers could be reproduced.
+Finally, we examined how many of the `r sum(all_data$data_complete == TRUE & all_data$analysis_script_included == TRUE, na.rm = TRUE)` articles with data and code could be reproduced.
 It is possible that running the code on the data reproduces all analyses, even when the data file itself is not understandable (i.e., the data columns are not labeled).
-Two authors coded SPSS, R, and JASP analyses regarding (a) the executability of the script, and (b) the reproducibility of the results.
+Two authors coded SPSS, R, Matlab, Python, and JASP analyses regarding (a) the executability of the script, and (b) the reproducibility of the results.
 After the initial coding, inter-rater reliability was low (`r round(agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_jg == FALSE))$value,0)`% agreement on executability, and `r round(agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_jg == FALSE))$value,0)`% agreement on reproducibility for SPSS scripts, `r round(agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_nc == FALSE))$value,0)`% agreement on executability, and `r round(agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_nc == FALSE))$value,0)`% agreement on reproducibility for R scripts).
@@
 For each article two coders examined whether the code could be run on the data.
-Of the original `r length(all_data$doi)` articles, `r sum(all_data$included_language == FALSE, na.rm = TRUE, na.rm = TRUE)` used MATLAB and Python and were excluded from the analysis due to a lack of expertise in our team with these languages.
-In total code and data were available for `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)` articles, of which `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` used R, SPSS, or JASP.
-We were able to run the code for `r sum(all_data$run_script_final == TRUE, na.rm = TRUE)` out of the `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` articles that used SPSS, R, and JASP.
+Of the original `r length(all_data$doi)` articles, the analysis code and data were available for `r sum(all_data$analysis_script_included ==TRUE & all_data$data_complete == TRUE, na.rm = TRUE)` articles.
+We were able to run the code for `r sum(all_data$run_script_final == TRUE, na.rm = TRUE)` out of the `r sum(all_data$analysis_script_included ==TRUE, na.rm = TRUE)` articles.
 R was used as a coding language in `r length(run_script_r)`, of which `r sum(run_script_r)` scripts could be run on the data, `r length(run_script_spss)` papers used SPSS, for `r sum(run_script_spss)` of which the script could be run, and `r length(run_script_r_spss)` papers used both SPSS and R, for which the scripts could be run for all `r sum(run_script_r_spss)` papers.
@@
 Because of this useful feature, the `r sum(run_script_jasp)` articles that relied on JASP for the analyses always allowed us to reproduce the analyses.
-
 Being able to run the code on the data does not imply that all the main analyses reported in the manuscript are correctly reproduced.
 Some analyses in a paper might not be part of the code or the output.
-We found that `r sum(all_data$reproducible_final, na.rm = TRUE)` out of `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` papers (`r round(100*sum(all_data$reproducible_final, na.rm = TRUE)/sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE),1)`%) that included their data and code could be used to reproduce the main results in the article.
+We found that `r sum(all_data$reproducible_final, na.rm = TRUE)` out of `r sum(all_data$analysis_script_included ==TRUE & all_data$data_complete == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` papers (`r round(100*sum(all_data$reproducible_final, na.rm = TRUE)/sum(all_data$analysis_script_included ==TRUE & all_data$data_complete == TRUE, na.rm = TRUE),1)`%) that included their data and code could be used to reproduce the main results in the article.
+
 The average time to reproduce analyses reported in R was `r round(mean(time_r_po, na.rm = TRUE),2)` minutes for the first coder (SD = `r round(sd(time_r_po, na.rm = TRUE),2)`) and `r round(mean(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)` minutes (SD =  `r round(sd(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)`) for the second coder.
@@
 We analyzed data and scripts of `r length(all_data$doi)` Registered Reports to examine how many authors shared their data and code, and how often main results reported in the manuscript could be reproduced.
-In total, `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)` out of `r length(all_data$doi)` (or `r round(100*sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)/length(all_data$doi),1)`%) of the articles shared the underlying data and the code that was used to generate the results.
-Of the papers that shared both the data and the analysis code and used software we had experience with, we could reproduce the main results for `r round(100*sum(all_data$reproducible_final, na.rm = TRUE)/sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE),1)`% of the papers.
+In total, `r sum(all_data$analysis_script_included ==TRUE & all_data$data_complete == TRUE, na.rm = TRUE)` out of `r length(all_data$doi)` (or `r round(100*sum(all_data$analysis_script_included ==TRUE & all_data$data_complete == TRUE, na.rm = TRUE)/length(all_data$doi),1)`%) of the articles shared the underlying data and the code that was used to generate the results.
 Authors of Registered Reports in psychology seem to voluntarily choose to share data and code relatively often compared to authors of articles in political science [@stockemer_data_2018].

### 2019-09-08 reproducing_registered_reports.tex
revision including python scripts

@@
 Because most researchers have not been trained in computational reproducibility, it is important to evaluate current practices to identify practices that can be improved.
-We examined data and code sharing, as well as computational reproducibility of the main results without contacting the original authors, for Registered Reports published in the in psychological literature between 2014 and 2018.
-Of the 62 articles that met our inclusion criteria data was available for 40 articles, and analysis scripts for 43 articles.
-For the 35 articles that shared both data and code and performed analyses in SPSS, R, or JASP, we could run the scripts for 30 articles, and reproduce the main results for 19 articles.
-Although the percentage of articles that shared both data and code (61\%) and articles that could be computationally reproduced (54\%) was relatively high compared to other studies, there is clear room for improvement.
+We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the in psychological literature between 2014 and 2018.
+Of the 62 articles that met our inclusion criteria, data was available for 40 articles, and analysis scripts for 37 articles.
+For the 35 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 articles, and reproduce the main results for 20 articles.
+Although the articles that shared both data and code (35 out of 62, or 56\%) and articles that could be computationally reproduced (20 out of 35, or 57\%) was relatively high compared to other studies, there is clear room for improvement.
 We provide practical recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.
@@
 Eleven articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance.
-Hardwicke et al.~(2018) estimated that it took between 2-25 hours to reproduce the reported results, but they did not record the exact time.
+The authors estimated that it took between 2-25 hours to reproduce the reported results per article, but they did not record the exact time.
 Stockemer, Koehler, and Lentz (2018) analyzed reproducibility in all articles published in 2015 in three political science journals.
@@
 Our main interest was to examine the computational reproducibility of the main analyses reported in published articles, without contacting the original authors.
-One of the main benefits of sharing data and code with the article (compared to making these files available upon request) is that results can be reproduced, and data reused even if the original author can no longer be reached.
+One of the main benefits of sharing data and code with an article (compared to making these files available upon request) is that results can be reproduced, and data reused even if the original author can no longer be reached.
+
 Registered Reports are a novel development in psychology.
-Before data collection commences, the introduction and methods are peer-reviewed, after which authors can receive an \enquote{in principle acceptance}.
+Before data collection commences, the introduction and methods are peer-reviewed, after which authors can receive an \enquote{in-principle acceptance}.
 This means the article will be published as long as the authors follow their preregistered data collection and analysis plan (Chambers, Feredoes, Muthukumaraswamy, \& Etchells, 2014; Nosek \& Lakens, 2014).
@@
 The novelty of Registered Reports may attract early adopters who are also exploring other novel developments aimed at improving research practices in psychology, such as data and code sharing.
-We assumed that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
-In line with our assumptions, 43 out of 62 articles in our final dataset shared data and code (69.40\%).
+We hypothesized that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
+In line with our hypothesis, 43 out of 62 articles in our final dataset shared at least some of the data and code (69.40\%).
 In comparison, after the journal \emph{Cognition} introduced a mandatory data sharing policy, 136 out of 174 articles (78.2\%) had a data availability statement, 85 of 174 articles (49\%) had reusable data, and only 18 out of 174 articles (10.3\%) provided the analysis code (Hardwicke et al., 2018).
-To evaluate the reproducibility of findings published in Registered Reports, we examined if data could be located, were available at the indicated location, could be opened in open-source software, were documented well enough to be understandable, and could be used to reproduce the main analyses reported in the published manuscript.
+To evaluate the reproducibility of findings published in Registered Reports, we examined if data could be located, were available at the indicated location, could be opened in open-source or accessible software, were documented well enough to be understandable, and could be used to reproduce the main analyses reported in the published manuscript.
 
@@
 This left 62 studies in our sample.
-When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, Matlab), which led to the exclusion of 5 additional studies.
+When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of 1 additional study.
 
@@
 These five categories were inspired by FAIR data principles (Wilkinson et al., 2016) that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles.
-Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of meta-data (which is missing for practically all datasets).
+Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of metadata (which is missing for practically all datasets).
 We considered data and code to be linked when the manuscript included a unique link to the data and scripts.
@@
 
-Of the 62 papers, 45 linked to data and/or code in the article.
-Linking to data does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable.
+Of the 62 papers, 45 linked to data and/or code that were part of the article.
+Linking to data or code does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable.
 For one article the link no longer worked (highlighting the need to use a stable DOI when linking to data).
@@
 For one paper the data was linked but not available, as the data was embargoed until a future date.
-Altogether, data was available for 43 out of 62 papers.
+Altogether, some data or code was available for 43 out of 62 papers.
+For 37 articles the available code contained the statistical analyses, and for 40 all the required data files were available to reproduce the reported results (for 35 articles both data and code were available.
 
@@
 Note that we had access to SPSS and therefore reproduced the analyses using the original .sps scripts where available.
-The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files that were analyzed in matlab, which we could not reproduce using open source software.
-This left 42 papers where data was available in a non-software-specific format.
+The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files required dedicated EEG software and could not be reproduced (we could also not find the analysis code for this article).
 
@@
 \caption{Of all articles in the Registered Report database 79 were psychology related, and 62 were registered reports not part of a multi-lab Registered Replication Report.
-Of these 62 papers, 45 linked to the data.
-After searching the OSF, data was available for 43 studies.
-Of these datasets, 21 were documented well enough, for example through a codebook, so that variables were understandable.
-Of the 62 papers 40 shared the analysis script and data, for which 35 were in SPSS, R or JASP.
-Of these, the analysis script could be run for 30, of which 19 reproduced all main results.
+Of these 62 papers, 45 linked to the data or code.
+After searching the OSF, data or code was available for 43 studies, of which 39 articles used SPSS, R, Matlab, Python, or JASP.
+Of the 62 papers 37 shared the analysis script and 40 shared all data.
+The analysis script could be run for 31 articles.
+For the 35 articles for which data and code were available, the main results could be reproduced for 20.
 }
@@
 In our analyses, data were scored as \enquote{understandable} when all variables were clearly named (e.g., \enquote{Condition}) and the values for variables were labeled (e.g., 0 = control, 1 = experimental).
-Out of the 42 papers with available data in a format that was not software specific, only 21 datasets were described in enough detail to be understandable.
-This highlights the importance of adding a codebook with a datafile.
-For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript) see Arslan (2019).
+Out of the 44 papers with available data in a format that was not software specific, only 24 datasets were described in enough detail to be understandable.
+This highlights the importance of adding a codebook with a datafile.\footnote{For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript) see Arslan (2019).}
 
-Finally, we examined how many of the 42 non-software-specific papers could be reproduced.
+Finally, we examined how many of the 35 articles with data and code could be reproduced.
 It is possible that running the code on the data reproduces all analyses, even when the data file itself is not understandable (i.e., the data columns are not labeled).
-Two authors coded SPSS, R, and JASP analyses regarding (a) the executability of the script, and (b) the reproducibility of the results.
+Two authors coded SPSS, R, Matlab, Python, and JASP analyses regarding (a) the executability of the script, and (b) the reproducibility of the results.
 After the initial coding, inter-rater reliability was low (60\% agreement on executability, and 55\% agreement on reproducibility for SPSS scripts, 75\% agreement on executability, and 56\% agreement on reproducibility for R scripts).
@@
 Furthermore, coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article.
-After evaluating our initial coding round, we considered an article was reproducible when we could get the same \emph{main results} as represented in the paper with at best \emph{minor changes} to the analysis scripts.
+After evaluating our initial coding round, we considered an article reproducible when we could get the same \emph{main results} as represented in the paper with at best \emph{minor changes} to the analysis scripts.
 This means we considered the analysis reproducible, even if variables could only be found with reasonable effort or by making assumptions about how variable names mapped onto variables reported in the data analysis.
@@
 For each article two coders examined whether the code could be run on the data.
-Of the original 62 articles, 5 used Matlab and Python and were excluded from the analysis due to a lack of expertise in our team with these languages.
-In total code and data were available for 38 articles, of which 35 used R, SPSS, or JASP.
-We were able to run the code for 30 out of the 35 articles that used SPSS, R, and JASP.
+Of the original 62 articles, the analysis code and data were available for 35 articles.
+We were able to run the code for 31 out of the 37 articles.
 R was used as a coding language in 13, of which 10 scripts could be run on the data, 17 papers used SPSS, for 15 of which the script could be run, and 3 papers used both SPSS and R, for which the scripts could be run for all 3 papers.
@@
 Because of this useful feature, the 2 articles that relied on JASP for the analyses always allowed us to reproduce the analyses.
-
 Being able to run the code on the data does not imply that all the main analyses reported in the manuscript are correctly reproduced.
 Some analyses in a paper might not be part of the code or the output.
-We found that 19 out of 35 papers (54.30\%) that included their data and code could be used to reproduce the main results in the article.
+We found that 20 out of 35 papers (57.10\%) that included their data and code could be used to reproduce the main results in the article.
+
 The average time to reproduce analyses reported in R was 27.08 minutes for the first coder (SD = 28.55) and 32.50 minutes (SD = 20.95) for the second coder.
@@
 We analyzed data and scripts of 62 Registered Reports to examine how many authors shared their data and code, and how often main results reported in the manuscript could be reproduced.
-In total, 38 out of 62 (or 61.30\%) of the articles shared the underlying data and the code that was used to generate the results.
-Of the papers that shared both the data and the analysis code and used software we had experience with, we could reproduce the main results for 54.30\% of the papers.
+In total, 35 out of 62 (or 56.50\%) of the articles shared the underlying data and the code that was used to generate the results.
 Authors of Registered Reports in psychology seem to voluntarily choose to share data and code relatively often compared to authors of articles in political science (Stockemer et al., 2018).
@@
 It provides a code environment (or container) that runs online, which means that researchers using Code Ocean do not have to download data, code, or software, but can analyze the data in their browser.
-It is not yet possible to use SPSS within Code Ocean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.\footnote{For a Code Ocean capsule reproducing this manuscript: \url{https://codeocean.com/capsule/8580632/tree/v1}} Another solution is RMarkdown which enable researchers to write fully reproducible manuscripts.
+It is not yet possible to use SPSS within Code Ocean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.\footnote{For a Code Ocean capsule reproducing this manuscript: \url{https://codeocean.com/capsule/8580632/tree/v1}} Other platforms in the reproducibility space include Whole Tale (Brinckman et al., 2019), \enquote{a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage} (p.~855); and Binder (Ragan-Kelley \& Willing, 2018), an open-source, browser-based tool for creating and sharing reproducible environments.
+
+Another useful technology is RMarkdown, which enable researchers to write fully executable manuscripts.
 RMarkdown files load the raw data and allow researchers to compute each number reported in the manuscript from the data, instead of copy-pasting values.
@@
 doi:\href{https://doi.org/10.1177/2515245919838783}{10.1177/2515245919838783}
+
+\leavevmode\hypertarget{ref-brinckman2019computing}{}%
+Brinckman, A., Chard, K., Gaffney, N., Hategan, M., Jones, M.
+B., Kowalik, K., \ldots{} others.
+(2019).
+Computing environments for reproducibility: Capturing the ``whole tale''.
+\emph{Future Generation Computer Systems}, \emph{94}, 854--867.
 
@@
 
+\leavevmode\hypertarget{ref-ragan2018binder}{}%
+Ragan-Kelley, B., \& Willing, C. (2018). Binder 2.0-reproducible, interactive, sharable environments for science at scale.
+
 \leavevmode\hypertarget{ref-stockemer_data_2018}{}%

### 2019-09-09 reproducing_registered_reports.tex
added new author info (Seth & Code Ocean)

@@
             pdftitle={Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology},
-            pdfauthor={Pepijn Obels, Daniel Lakens, Nicholas A. Coles, \& Jaroslav Gottfried},
+            pdfauthor={Pepijn Obels, Daniel Lakens, Nicholas A. Coles, Jaroslav Gottfried, \& Seth Ariel Green},
             pdfkeywords={reproducibility, Registered Reports, data sharing, open science},
@@
   \title{Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology}
-    \author{Pepijn Obels\textsuperscript{1}, Daniel Lakens\textsuperscript{1}, Nicholas A. Coles\textsuperscript{2}, \& Jaroslav Gottfried\textsuperscript{3}}
+    \author{Pepijn Obels\textsuperscript{1}, Daniel Lakens\textsuperscript{1}, Nicholas A.
+Coles\textsuperscript{2}, Jaroslav Gottfried\textsuperscript{3}, \& Seth Ariel Green\textsuperscript{Code Ocean}}
     \date{}

### 2019-09-09 reproducing_registered_reports.Rmd
added new author info (Seth & Code Ocean)
now with the affiliation right

@@
     affiliation   : "3"
+  - name          : "Seth Ariel Green"
+    affiliation   : "4"
 
@@
     institution   : "Masaryk University, Brno, Czech Republic"
+  - id            : "4"
+    institution   : "Code Ocean"
 

### 2019-09-09 reproducing_registered_reports.tex
now with the affiliation right

@@
   \title{Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology}
-    \author{Pepijn Obels\textsuperscript{1}, Daniel Lakens\textsuperscript{1}, Nicholas A.
-Coles\textsuperscript{2}, Jaroslav Gottfried\textsuperscript{3}, \& Seth Ariel Green\textsuperscript{Code Ocean}}
+    \author{Pepijn Obels\textsuperscript{1}, Daniel Lakens\textsuperscript{1}, Nicholas A. Coles\textsuperscript{2}, Jaroslav Gottfried\textsuperscript{3}, \& Seth Ariel Green\textsuperscript{4}}
     \date{}
@@
 \vspace{0.5cm}
-\textsuperscript{1} Eindhoven University of Technology, The Netherlands\\\textsuperscript{2} University of Tennessee, Knoxville, USA\\\textsuperscript{3} Masaryk University, Brno, Czech Republic}
+\textsuperscript{1} Eindhoven University of Technology, The Netherlands\\\textsuperscript{2} University of Tennessee, Knoxville, USA\\\textsuperscript{3} Masaryk University, Brno, Czech Republic\\\textsuperscript{4} Code Ocean}
 \keywords{reproducibility, Registered Reports, data sharing, open science\newline\indent Word count: 4926}

### 2019-09-09 reproducing_registered_reports.Rmd
affiliation now has location

@@
   - id            : "4"
-    institution   : "Code Ocean"
+    institution   : "Code Ocean, New York, USA"
 

### 2019-09-09 reproducing_registered_reports.tex
affiliation now has location

@@
 \vspace{0.5cm}
-\textsuperscript{1} Eindhoven University of Technology, The Netherlands\\\textsuperscript{2} University of Tennessee, Knoxville, USA\\\textsuperscript{3} Masaryk University, Brno, Czech Republic\\\textsuperscript{4} Code Ocean}
+\textsuperscript{1} Eindhoven University of Technology, The Netherlands\\\textsuperscript{2} University of Tennessee, Knoxville, USA\\\textsuperscript{3} Masaryk University, Brno, Czech Republic\\\textsuperscript{4} Code Ocean, New York, USA}
 \keywords{reproducibility, Registered Reports, data sharing, open science\newline\indent Word count: 4926}

### 2019-09-09 reproducing_registered_reports.Rmd
changes through line 91

@@
 Researchers are currently exploring ways to make science more open and transparent.
-Among novel developments such as pre-registration, pre-prints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., [@morey_peer_2016].
+Among novel developments such as pre-registration, preprints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., [@morey_peer_2016].
 Sharing data and analysis code with scientific publications allows others to more easily reproduce, check, and build on existing work.
@@
 The availability of analysis code makes it possible for peers to check and correct published findings.
-According to @kitzes_practice_2017, computational reproducibility means that ”a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.” For scientific research to be computationally reproducible, the data and code needs to be shared.
+According to @kitzes_practice_2017, computational reproducibility means that ”a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.” For scientific research to be computationally reproducible, the data and code need to be shared.
 
@@
 
-Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the published article.
+Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the articles.
 @hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal *Cognition*.
@@
 @stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals.
-They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one could not be reproduced due to a lack of a software license, and 16 articles could not be reproduced with access to the required software.
-For the remaining articles, 32 could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results.
+They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one paper's results could not be reproduced due to a lack of a software license, and 16 articles' findings could not be reproduced with access to the required software.
+For the remaining articles, 32 sets of results could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results.
 @stodden_empirical_2018 analyzed data availability in the journal *Science* in 2011-2012 and found that 26 of 204 (or 13%) of articles provided information to retrieve data and/or code without contacting the authors.

### 2019-09-09 reproducing_registered_reports.Rmd
changes through line 105

@@
 @stodden_empirical_2018 analyzed data availability in the journal *Science* in 2011-2012 and found that 26 of 204 (or 13%) of articles provided information to retrieve data and/or code without contacting the authors.
-For all datasets they acquired after e-mailing authors for data and code, 26% was estimated to be computationally reproducible.
+For all datasets they acquired after e-mailing authors for data and code, 26% were estimated to be computationally reproducible.
 These studies reveal that there is clear room for improvement in how reproducible published articles are.
@@
 Our main interest was to examine the computational reproducibility of the main analyses reported in published articles, without contacting the original authors.
-One of the main benefits of sharing data and code with an article (compared to making these files available upon request) is that results can be reproduced, and data reused even if the original author can no longer be reached.
+One of the main benefits of sharing data and code alongside an article (compared to making these files available upon request) is that results can be reproduced, and data reused even if the original author can no longer be reached.
 
@@
 
-Our main objective was to examine how reusable data and code underlying Registered Reports are, based purely on the information provided in the published literature.
+Our main objective was to examine how reusable data and code underlying Registered Reports are, based solely on the information provided in those articles.
 We examined how many authors voluntarily shared data and code, and the extent to which we could reproduce reported analyses without contacting the original authors.
-While reproducing the results reported in Registered Reports, we kept track of factors that facilitated reproducibility or that made reproducing the result more difficult.
+While reproducing the results reported in Registered Reports, we kept track of factors that facilitated reproducibility or that made reproducing results more difficult.
 We report these qualitative findings with an aim to highlight how current practices can be improved.
@@
 This left `r length(all_data$doi)` studies in our sample.
-When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of `r sum(all_data$included_language == FALSE, na.rm = TRUE)` additional study.
+When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of one additional study.
 

### 2019-09-09 reproducing_registered_reports.tex
changes through line 105

@@
 Researchers are currently exploring ways to make science more open and transparent.
-Among novel developments such as pre-registration, pre-prints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., (Morey et al., 2016).
+Among novel developments such as pre-registration, preprints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., (Morey et al., 2016).
 Sharing data and analysis code with scientific publications allows others to more easily reproduce, check, and build on existing work.
@@
 The availability of analysis code makes it possible for peers to check and correct published findings.
-According to Kitzes, Turek, and Deniz (2017), computational reproducibility means that ''a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.'' For scientific research to be computationally reproducible, the data and code needs to be shared.
+According to Kitzes, Turek, and Deniz (2017), computational reproducibility means that ''a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.'' For scientific research to be computationally reproducible, the data and code need to be shared.
 
@@
 
-Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the published article.
+Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the articles.
 Hardwicke et al.
@@
 Stockemer, Koehler, and Lentz (2018) analyzed reproducibility in all articles published in 2015 in three political science journals.
-They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one could not be reproduced due to a lack of a software license, and 16 articles could not be reproduced with access to the required software.
-For the remaining articles, 32 could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results.
+They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one paper's results could not be reproduced due to a lack of a software license, and 16 articles' findings could not be reproduced with access to the required software.
+For the remaining articles, 32 sets of results could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results.
 Stodden, Seiler, and Ma (2018) analyzed data availability in the journal \emph{Science} in 2011-2012 and found that 26 of 204 (or 13\%) of articles provided information to retrieve data and/or code without contacting the authors.
-For all datasets they acquired after e-mailing authors for data and code, 26\% was estimated to be computationally reproducible.
+For all datasets they acquired after e-mailing authors for data and code, 26\% were estimated to be computationally reproducible.
 These studies reveal that there is clear room for improvement in how reproducible published articles are.
@@
 This left 62 studies in our sample.
-When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of 1 additional study.
+When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of one additional study.
 

### 2019-09-09 reproducing_registered_reports.Rmd
changes through line 111

@@
 
-To find Registered Reports published in psychology we drew from a database of registered reports maintained by the Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
+To find Registered Reports published in psychology, we drew from a database of registered reports maintained by the Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
 Eighty-one articles in this database were published in the psychological literature.
@@
 
-We set out to reproduce the `r length(all_data$doi)` papers that met our inclusion criteria.
-For each article we coded whether the data and code were (a) linked, (b) available, (c) not software-specific, (d) understandable, and (e) reproducible.
+We set out to reproduce the findings of `r length(all_data$doi)` papers that met our inclusion criteria.
+For each article, we coded whether the data and code were (a) linked, (b) available, (c) not software-specific, (d) understandable, and (e) reproducible.
 These five categories were inspired by FAIR data principles [@wilkinson_fair_2016] that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles.
-Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of metadata (which is missing for practically all datasets).
+Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of metadata (which was missing for practically all datasets).
 We considered data and code to be linked when the manuscript included a unique link to the data and scripts.
 Ideally, such a link consists of a stable digital object identifier (DOI).
-A hyperlink to a website that contains the data and script also suffices, although normal hyperlinks are known to break over time [@gertler_reference_2017].
-
+A hyperlink to a website that contains the data and script also suffices, although hyperlinks are known to break over time [@gertler_reference_2017].
++
 Of the `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to data and/or code that were part of the article.
 Linking to data or code does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable.
-For one article the link no longer worked (highlighting the need to use a stable DOI when linking to data).
-For three articles the link still worked, but there was no data at the linked destination.
+For one article the link no longer worked (highlighting the benefit of using a stable DOI for linking to data).
+For three articles, the link still worked, but there was no data at the linked destination.
 For three articles where there was no link to the data in the article, we were nevertheless able to find data on the Open Science Framework when searching for the title of the paper.
 For one paper the data was linked but not available, as the data was embargoed until a future date.
-Altogether, some data or code was available for `r sum(all_data$availability)` out of `r length(all_data$doi)` papers.
-For `r sum(all_data$analysis_script_included == TRUE, na.rm = TRUE)` articles the available code contained the statistical analyses, and for `r sum(all_data$data_complete == TRUE, na.rm = TRUE)` all the required data files were available to reproduce the reported results (for `r sum(all_data$data_complete == TRUE & all_data$analysis_script_included == TRUE, na.rm = TRUE)` articles both data and code were available.
+Altogether, some data or code was available for `r sum(all_data$availability)` of `r length(all_data$doi)` papers.
+For `r sum(all_data$analysis_script_included == TRUE, na.rm = TRUE)` articles, the available code contained the statistical analyses, and for `r sum(all_data$data_complete == TRUE, na.rm = TRUE)`, all the required data files were available to reproduce the reported results (for `r sum(all_data$data_complete == TRUE & all_data$analysis_script_included == TRUE, na.rm = TRUE)` articles both data and code were available).
 

### 2019-09-09 reproducing_registered_reports.tex
changes through line 111

@@
 
-To find Registered Reports published in psychology we drew from a database of registered reports maintained by the Center for Open Science.\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
+To find Registered Reports published in psychology, we drew from a database of registered reports maintained by the Center for Open Science.\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
 Eighty-one articles in this database were published in the psychological literature.
@@
 
-We set out to reproduce the 62 papers that met our inclusion criteria.
-For each article we coded whether the data and code were (a) linked, (b) available, (c) not software-specific, (d) understandable, and (e) reproducible.
+We set out to reproduce the findings of 62 papers that met our inclusion criteria.
+For each article, we coded whether the data and code were (a) linked, (b) available, (c) not software-specific, (d) understandable, and (e) reproducible.
 These five categories were inspired by FAIR data principles (Wilkinson et al., 2016) that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles.
-Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of metadata (which is missing for practically all datasets).
+Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of metadata (which was missing for practically all datasets).
 We considered data and code to be linked when the manuscript included a unique link to the data and scripts.
 Ideally, such a link consists of a stable digital object identifier (DOI).
-A hyperlink to a website that contains the data and script also suffices, although normal hyperlinks are known to break over time (Gertler \& Bullock, 2017).
-
+A hyperlink to a website that contains the data and script also suffices, although hyperlinks are known to break over time (Gertler \& Bullock, 2017).
++
 Of the 62 papers, 45 linked to data and/or code that were part of the article.
 Linking to data or code does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable.
-For one article the link no longer worked (highlighting the need to use a stable DOI when linking to data).
-For three articles the link still worked, but there was no data at the linked destination.
+For one article the link no longer worked (highlighting the benefit of using a stable DOI for linking to data).
+For three articles, the link still worked, but there was no data at the linked destination.
 For three articles where there was no link to the data in the article, we were nevertheless able to find data on the Open Science Framework when searching for the title of the paper.
 For one paper the data was linked but not available, as the data was embargoed until a future date.
-Altogether, some data or code was available for 43 out of 62 papers.
-For 37 articles the available code contained the statistical analyses, and for 40 all the required data files were available to reproduce the reported results (for 35 articles both data and code were available.
+Altogether, some data or code was available for 43 of 62 papers.
+For 37 articles, the available code contained the statistical analyses, and for 40, all the required data files were available to reproduce the reported results (for 35 articles both data and code were available).
 

### 2019-09-09 reproducing_registered_reports.Rmd
changes through line 113

@@
 
-We also coded the extent to which data and code was specific to software that was not freely available.
-When open source software is used, the analyses can be reproduced by anyone with a computer and internet, regardless of whether they have bought the same software package.
-When proprietary software is used, results might still be reproducible by anyone, but it could require more effort to do so.
+We also coded the extent to which data and code were specific to software that was not freely available.
+When open source software is used, the analyses can be reproduced by anyone with time, a computer and internet.
+When proprietary software is used, results might still be reproducible in principle, but could require more effort to do so.
 For example, SPSS produces proprietary .sav and .sps files.
-However, .sav files can be opened in R, and .sps files can be opened by a text editor and the code can be rewritten, as long the code is annotated well enough to be recoded into R.
+However, .sav files can be opened in R, and .sps files can be opened by a text editor and the code can be rewritten, as long the code is annotated well enough to be recoded in R.
 Note that we had access to SPSS and therefore reproduced the analyses using the original .sps scripts where available.

### 2019-09-09 reproducing_registered_reports.Rmd
changes through line 148

@@
 Note that we had access to SPSS and therefore reproduced the analyses using the original .sps scripts where available.
-The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files required dedicated EEG software and could not be reproduced (we could also not find the analysis code for this article).
+The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files, which require dedicated EEG software and could not be reproduced (we also could not find the analysis code for this article).
 
@@
 Of these `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to the data or code.
-After searching the OSF, data or code was available for `r sum(all_data$availability)` studies, of which `r spss_or_r_or_jasp` articles used SPSS, R, Matlab, Python, or JASP.
+After searching the OSF, data or code was available for `r sum(all_data$availability)` studies, of which `r spss_or_r_or_jasp` articles used SPSS, R, MATLAB, Python, or JASP.
 Of the `r length(all_data$doi)` papers `r sum(all_data$analysis_script_included, na.rm = TRUE)` shared the analysis script and `r sum(all_data$data_complete, na.rm = TRUE)` shared all data.
@@
 If the data can be understood by others, they can be used to answer novel research questions.
-This is one of the reasons why it is recommended to describe the dataset variables in a codebook.
+This is one of the reasons why it is considered best practice to describe the dataset variables in a codebook.
 If the variables are not clearly described (e.g., the dataset consists of variables identified by abbreviations that only make sense to the original researcher), other researchers will not be able to reuse the data to answer novel questions.
 In our analyses, data were scored as 'understandable' when all variables were clearly named (e.g., 'Condition') and the values for variables were labeled (e.g., 0 = control, 1 = experimental).
-Out of the `r sum(all_data$not_software_specific, na.rm = TRUE)` papers with available data in a format that was not software specific, only `r sum(all_data$understandable, na.rm = TRUE)` datasets were described in enough detail to be understandable.
-This highlights the importance of adding a codebook with a datafile.^[For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript) see @arslan_how_2019.]
+Out of the `r sum(all_data$not_software_specific, na.rm = TRUE)` papers with available data in a format that was not software-specific, only `r sum(all_data$understandable, na.rm = TRUE)` datasets were described in enough detail to be understandable.
+This highlights the importance of adding a codebook with a datafile.^[For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript), see @arslan_how_2019.]
 
@@
 It is possible that running the code on the data reproduces all analyses, even when the data file itself is not understandable (i.e., the data columns are not labeled).
-Two authors coded SPSS, R, Matlab, Python, and JASP analyses regarding (a) the executability of the script, and (b) the reproducibility of the results.
+Two authors coded SPSS, R, MATLAB, Python, and JASP analyses regarding (a) the executability of the script, and (b) the reproducibility of the results.
 After the initial coding, inter-rater reliability was low (`r round(agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_jg == FALSE))$value,0)`% agreement on executability, and `r round(agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_jg == FALSE))$value,0)`% agreement on reproducibility for SPSS scripts, `r round(agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_nc == FALSE))$value,0)`% agreement on executability, and `r round(agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_nc == FALSE))$value,0)`% agreement on reproducibility for R scripts).
@@
 This means we considered the analysis reproducible, even if variables could only be found with reasonable effort or by making assumptions about how variable names mapped onto variables reported in the data analysis.
-Furthermore, we changed folder locations when needed and loaded libraries that were required.
+Furthermore, we changed folder locations when needed, and installed and/or loaded required libraries.
 Finally, even though sometimes figures were generated in R and contained relevant information (e.g., the pattern of means) we did not require all figures to be reproducible.
 
-There were differences between coders in how much expertise they had with R, SPSS, and JASP (PO had less experience, while JG and NC had more experience).
+There were differences between coders in how much expertise they had with R, SPSS, and JASP (PO had less experience, while JG and NC had more experience; SG ran all MATLAB and Python code).
 The more expertise coders had, the easier it was to reproduce findings (which lead to lower inter-rater reliability).
@@
 The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve).
-It should be noted that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.
+(It may bear repeating that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.)
 
-For each article two coders examined whether the code could be run on the data.
+For each article, two coders examined whether the code could be run on the data.
 Of the original `r length(all_data$doi)` articles, the analysis code and data were available for `r sum(all_data$analysis_script_included ==TRUE & all_data$data_complete == TRUE, na.rm = TRUE)` articles.
@@
 The structure of analysis scripts can often be improved by creating different sections in the code, or creating different files for different parts of the data analysis (e.g., data cleaning, data preparation, exploratory data analysis, and confirmatory data analysis scripts).
-Third, it is highly recommended to perform a final check after the peer-review process has been completed to make sure any changes in the code introduced during the peer-review process are reflected in the shared data and code.
+Third, we recommend that researchers perform a final check after peer review has been completed to make sure any changes in the code introduced during the peer-review process are reflected in the shared data and code.
 
@@
 List all the packages that the code needs to run at the top of the script.
-Because packages update, it is necessary to report the version numbers of packages that were used (for example using packrat of copying the output of the the sessionInfo() function as a comment in the script).
+Because packages update, it is necessary to report the version numbers of packages that were used (for example using packrat, or copying the output of the the sessionInfo() function as a comment in the script).
 Remember that folder names and folder structures differ between computers, and therefore you should use relative locations (and not “c:/user/myfolder/code”).

### 2019-09-09 reproducing_registered_reports.tex
changes through line 148

@@
 
-We also coded the extent to which data and code was specific to software that was not freely available.
-When open source software is used, the analyses can be reproduced by anyone with a computer and internet, regardless of whether they have bought the same software package.
-When proprietary software is used, results might still be reproducible by anyone, but it could require more effort to do so.
+We also coded the extent to which data and code were specific to software that was not freely available.
+When open source software is used, the analyses can be reproduced by anyone with time, a computer and internet.
+When proprietary software is used, results might still be reproducible in principle, but could require more effort to do so.
 For example, SPSS produces proprietary .sav and .sps files.
-However, .sav files can be opened in R, and .sps files can be opened by a text editor and the code can be rewritten, as long the code is annotated well enough to be recoded into R.
+However, .sav files can be opened in R, and .sps files can be opened by a text editor and the code can be rewritten, as long the code is annotated well enough to be recoded in R.
 Note that we had access to SPSS and therefore reproduced the analyses using the original .sps scripts where available.
-The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files required dedicated EEG software and could not be reproduced (we could also not find the analysis code for this article).
+The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files, which require dedicated EEG software and could not be reproduced (we also could not find the analysis code for this article).
 
@@
 Of these 62 papers, 45 linked to the data or code.
-After searching the OSF, data or code was available for 43 studies, of which 39 articles used SPSS, R, Matlab, Python, or JASP.
+After searching the OSF, data or code was available for 43 studies, of which 39 articles used SPSS, R, MATLAB, Python, or JASP.
 Of the 62 papers 37 shared the analysis script and 40 shared all data.
@@
 If the data can be understood by others, they can be used to answer novel research questions.
-This is one of the reasons why it is recommended to describe the dataset variables in a codebook.
+This is one of the reasons why it is considered best practice to describe the dataset variables in a codebook.
 If the variables are not clearly described (e.g., the dataset consists of variables identified by abbreviations that only make sense to the original researcher), other researchers will not be able to reuse the data to answer novel questions.
 In our analyses, data were scored as \enquote{understandable} when all variables were clearly named (e.g., \enquote{Condition}) and the values for variables were labeled (e.g., 0 = control, 1 = experimental).
-Out of the 44 papers with available data in a format that was not software specific, only 24 datasets were described in enough detail to be understandable.
-This highlights the importance of adding a codebook with a datafile.\footnote{For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript) see Arslan (2019).}
+Out of the 44 papers with available data in a format that was not software-specific, only 24 datasets were described in enough detail to be understandable.
+This highlights the importance of adding a codebook with a datafile.\footnote{For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript), see Arslan (2019).}
 
@@
 It is possible that running the code on the data reproduces all analyses, even when the data file itself is not understandable (i.e., the data columns are not labeled).
-Two authors coded SPSS, R, Matlab, Python, and JASP analyses regarding (a) the executability of the script, and (b) the reproducibility of the results.
+Two authors coded SPSS, R, MATLAB, Python, and JASP analyses regarding (a) the executability of the script, and (b) the reproducibility of the results.
 After the initial coding, inter-rater reliability was low (60\% agreement on executability, and 55\% agreement on reproducibility for SPSS scripts, 75\% agreement on executability, and 56\% agreement on reproducibility for R scripts).
@@
 The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve).
-It should be noted that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.
+(It may bear repeating that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.)
 
-For each article two coders examined whether the code could be run on the data.
+For each article, two coders examined whether the code could be run on the data.
 Of the original 62 articles, the analysis code and data were available for 35 articles.
@@
 List all the packages that the code needs to run at the top of the script.
-Because packages update, it is necessary to report the version numbers of packages that were used (for example using packrat of copying the output of the the sessionInfo() function as a comment in the script).
+Because packages update, it is necessary to report the version numbers of packages that were used (for example using packrat, or copying the output of the the sessionInfo() function as a comment in the script).
 Remember that folder names and folder structures differ between computers, and therefore you should use relative locations (and not \enquote{c:/user/myfolder/code}).

### 2019-09-09 reproducing_registered_reports.Rmd
changes through COI statement

@@
 The absence of understandable variable and value labels in more than half of all SPSS scripts hindered our attempts to reproduce these results.
-Often the only time-efficient way to check if an article was reproducible so was to run the whole script, and search try to identify specific *p*-values or effect sizes from the article in the SPSS output.
-SPSS users should take greater care to clearly organize their analysis scripts by adding comments or a README file that links results generated by the SPSS script to the analyses reported in the manuscript.
-Another frequent problem consisted of missing or incorrectly labeled variables in the dataset, so the script could not run properly.
+Often the only time-efficient way to check if an article was reproducible was to run the whole script, and try to identify specific *p*-values or effect sizes from the article in the SPSS output.
+SPSS users should take care to clearly organize their analysis scripts by adding comments or a README file that links results generated by the SPSS script to the analyses reported in the manuscript.
+Another frequent problem was missing or incorrectly labeled variables in the dataset, so the scripts could not run properly.
 We expect this is the result of authors updating or modifying either their datasets or their scripts during the publication process.
-This issue could be easily detected if a second author of the manuscript attempted to reproduce the analyses reported in the final manuscript before the data and scripts are shared publicly.
+This issue could be easily detected if a second author of the manuscript attempted to reproduce the analyses reported in the final manuscript before data and scripts are shared publicly.
 
@@
 We limited our analysis to Registered Reports based on the idea that these article formats might be used by people who are early adopters of innovations in science, and would therefore be more likely to also share data and code.
-The default rate with which data and code was shared was relatively high, compared to other studies on the reproducibility of analyses (e.g, Hardwicke et al., 2018, Stockemer et al., 2018), but we do not have data that gives insights into the motivations of these authors.
+We found that the rate at  which data and code was shared in our sample was high, relative to studies anlayzed in other reproducibility-focused reviews (e.g, Hardwicke et al., 2018, Stockemer et al., 2018), but we do not have data that gives insights into the motivations of these authors.
 Registered Reports are written by a diverse set of researchers, working in different subfields in psychology, and it would be interesting for future research to qualitatively examine the motivations of researchers who published Registered Reports for sharing or not sharing data and code.
-There are several good reasons why data can not be shared, and researchers should be able to explain why data is not available when they publish a scientific article [@morey_peer_2016].
+There are several good reasons why some data should not be shared, and when applicable, researchers should be encouraged to explain their reasons [@morey_peer_2016].
 
-The main aim of this article was not to accurately estimate reproducibility rates, but to see what current standards are, and how the reproducibility of research articles using the Registered Report format could be improved.
-The sample size is small, and it is doubtful whether an accurate estimate of the reproducibility of Registered Reports is of much value, beyond examining where most room for improvement is.
+The main aim of this article was not to precisely estimate reproducibility rates, but to see what current standards are, and how the reproducibility of research articles using the Registered Report format could be improved.
+The sample size is small, and it is doubtful whether a precise estimate of the reproducibility of Registered Reports is of much value, beyond examining where most room for improvement is.
 Data and code sharing are relatively new, researchers typically lack training in reproducible data analysis, and therefore the main contribution of this article is the identification of common issues that can be improved.
@@
 It provides a code environment (or container) that runs online, which means that researchers using Code Ocean do not have to download data, code, or software, but can analyze the data in their browser.
-It is not yet possible to use SPSS within Code Ocean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.^[For a Code Ocean capsule reproducing this manuscript: https://codeocean.com/capsule/8580632/tree/v1] Other platforms in the reproducibility space include Whole Tale [@brinckman2019computing], "a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage" (p.
+It is not currently possible to use SPSS within Code Ocean, but for R code, it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.^[For a Code Ocean capsule reproducing this manuscript, see https://doi.org/10.24433/CO.4275368.v1] Other platforms in the reproducibility space include Whole Tale [@brinckman2019computing], "a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage" (p.
 855); and Binder [@ragan2018binder], an open-source, browser-based tool for creating and sharing reproducible environments.
@@
 This means that, as long as the data and require packages can be loaded, all reported numbers can be reproduced.
-This saves a lot of time matching the analysis code to the reported results, and thus speeds up the process of checking whether all results reported in the manuscripts are reproduced by the code.
-The current manuscript is an example of a reproducible RMarkdown file.^[See https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd] Additional solutions that help researchers to share reproducible analyses might become available in the future.
+This saves time when matching the analysis code's output to reported results, and thus speeds up the process of checking whether all results reported in the manuscripts are reproduced.
+The current manuscript is an example of a reproducible RMarkdown file.^[See https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd] Additional solutions that help researchers to share reproducible analyses may become available in the future.
 
-Finally, journals who value reproducibility might find it worthwhile to check whether the data and analysis code shared with a submission can be used to reproduce the results.
+Finally, journals that value reproducibility might find it worthwhile to check whether the data and analysis code shared with a submission can be used to reproduce the results.
 The average time it took our team to check that the analysis code could reproduce the results reported in the paper was `r round(average_time,0)` minutes.
 This is slightly shorter than the time it took Hardwicke and colleagues (2018), who estimated (without keeping track of the time explicitly) that reproducibility reports took between 2 and 25 person-hours, depending on whether the paper eventually fell in the reproducible or not-reproducible category, and whether author assistance was needed.
-The main difference might be that we did not write 'reproducibility reports' for each article.
+One major difference between our approaches is that we did not write 'reproducibility reports' for each article.
 Documenting the process of reproducing a paper adds transparency and allows others to check the the decisions about every value in an article.
@@
 The required time might be reduced by explicitly asking authors to submit files in a format or structure that facilitates such checks, or automating part of the work that is needed to check the reproducibility of results.
-Overall, we feel that the time required for a basic check of the reproducibility of manuscripts (i.e., where one checks whether the *main* results in the paper are reproduced by the analysis scripts, but without documenting this step at the level of each individual number) is not an insurmountable problem for scientific journals that aim to add value, and would substantially improve the computational reproducibility of the published literature.
+Overall, we feel that the time required for a basic check of the reproducibility of manuscripts (i.e., where one checks whether the *main* results in the paper are reproduced by the analysis scripts, but without documenting this step at the level of each individual number) is a surmountable hurdle for journals, and would substantially improve the computational reproducibility of the published literature.
 
-In addition to novel technologies, most progress can probably be made by developing standards within a research community, and educating researchers about best practices that guarantee reproducibility.
-Most researchers are not trained in reproducible data analysis, and can not be expected to invent best practices from scratch.
+In addition to novel technologies, most progress can probably be made by developing standards within research communities, and educating researchers about best practices that guarantee reproducibility.
+Most researchers are not trained in reproducible data analysis, and cannot be expected to invent best practices from scratch.
 As good examples appear in the published literature over time, and best practices within subdisciplines crystalize, standards should emerge that improve reproducibility, and that allow researchers to share data and code in such a way that others with basic scientific training can reproduce their results and reuse their data.
+
+# Conflict of Interest Statement
+One author (SG) worked at Code Ocean during the writing of this manuscript.
+SG joined the project after its accompanying Code Ocean component was already submitted and published, and did not write any of the text concerning Code Ocean.
 

### 2019-09-09 reproducing_registered_reports.tex
changes through COI statement and also knit the Rmd

@@
 The absence of understandable variable and value labels in more than half of all SPSS scripts hindered our attempts to reproduce these results.
-Often the only time-efficient way to check if an article was reproducible so was to run the whole script, and search try to identify specific \emph{p}-values or effect sizes from the article in the SPSS output.
-SPSS users should take greater care to clearly organize their analysis scripts by adding comments or a README file that links results generated by the SPSS script to the analyses reported in the manuscript.
-Another frequent problem consisted of missing or incorrectly labeled variables in the dataset, so the script could not run properly.
+Often the only time-efficient way to check if an article was reproducible was to run the whole script, and try to identify specific \emph{p}-values or effect sizes from the article in the SPSS output.
+SPSS users should take care to clearly organize their analysis scripts by adding comments or a README file that links results generated by the SPSS script to the analyses reported in the manuscript.
+Another frequent problem was missing or incorrectly labeled variables in the dataset, so the scripts could not run properly.
 We expect this is the result of authors updating or modifying either their datasets or their scripts during the publication process.
-This issue could be easily detected if a second author of the manuscript attempted to reproduce the analyses reported in the final manuscript before the data and scripts are shared publicly.
+This issue could be easily detected if a second author of the manuscript attempted to reproduce the analyses reported in the final manuscript before data and scripts are shared publicly.
 
@@
 We limited our analysis to Registered Reports based on the idea that these article formats might be used by people who are early adopters of innovations in science, and would therefore be more likely to also share data and code.
-The default rate with which data and code was shared was relatively high, compared to other studies on the reproducibility of analyses (e.g, Hardwicke et al., 2018, Stockemer et al., 2018), but we do not have data that gives insights into the motivations of these authors.
+We found that the rate at which data and code was shared in our sample was high, relative to studies anlayzed in other reproducibility-focused reviews (e.g, Hardwicke et al., 2018, Stockemer et al., 2018), but we do not have data that gives insights into the motivations of these authors.
 Registered Reports are written by a diverse set of researchers, working in different subfields in psychology, and it would be interesting for future research to qualitatively examine the motivations of researchers who published Registered Reports for sharing or not sharing data and code.
-There are several good reasons why data can not be shared, and researchers should be able to explain why data is not available when they publish a scientific article (Morey et al., 2016).
+There are several good reasons why some data should not be shared, and when applicable, researchers should be encouraged to explain their reasons (Morey et al., 2016).
 
-The main aim of this article was not to accurately estimate reproducibility rates, but to see what current standards are, and how the reproducibility of research articles using the Registered Report format could be improved.
-The sample size is small, and it is doubtful whether an accurate estimate of the reproducibility of Registered Reports is of much value, beyond examining where most room for improvement is.
+The main aim of this article was not to precisely estimate reproducibility rates, but to see what current standards are, and how the reproducibility of research articles using the Registered Report format could be improved.
+The sample size is small, and it is doubtful whether a precise estimate of the reproducibility of Registered Reports is of much value, beyond examining where most room for improvement is.
 Data and code sharing are relatively new, researchers typically lack training in reproducible data analysis, and therefore the main contribution of this article is the identification of common issues that can be improved.
@@
 It provides a code environment (or container) that runs online, which means that researchers using Code Ocean do not have to download data, code, or software, but can analyze the data in their browser.
-It is not yet possible to use SPSS within Code Ocean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.\footnote{For a Code Ocean capsule reproducing this manuscript: \url{https://codeocean.com/capsule/8580632/tree/v1}} Other platforms in the reproducibility space include Whole Tale (Brinckman et al., 2019), \enquote{a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage} (p.~855); and Binder (Ragan-Kelley \& Willing, 2018), an open-source, browser-based tool for creating and sharing reproducible environments.
+It is not currently possible to use SPSS within Code Ocean, but for R code, it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.\footnote{For a Code Ocean capsule reproducing this manuscript, see \url{https://doi.org/10.24433/CO.4275368.v1}} Other platforms in the reproducibility space include Whole Tale (Brinckman et al., 2019), \enquote{a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage} (p.~855); and Binder (Ragan-Kelley \& Willing, 2018), an open-source, browser-based tool for creating and sharing reproducible environments.
 
@@
 This means that, as long as the data and require packages can be loaded, all reported numbers can be reproduced.
-This saves a lot of time matching the analysis code to the reported results, and thus speeds up the process of checking whether all results reported in the manuscripts are reproduced by the code.
-The current manuscript is an example of a reproducible RMarkdown file.\footnote{See \url{https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd}} Additional solutions that help researchers to share reproducible analyses might become available in the future.
+This saves time when matching the analysis code's output to reported results, and thus speeds up the process of checking whether all results reported in the manuscripts are reproduced.
+The current manuscript is an example of a reproducible RMarkdown file.\footnote{See \url{https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd}} Additional solutions that help researchers to share reproducible analyses may become available in the future.
 
-Finally, journals who value reproducibility might find it worthwhile to check whether the data and analysis code shared with a submission can be used to reproduce the results.
+Finally, journals that value reproducibility might find it worthwhile to check whether the data and analysis code shared with a submission can be used to reproduce the results.
 The average time it took our team to check that the analysis code could reproduce the results reported in the paper was 24 minutes.
 This is slightly shorter than the time it took Hardwicke and colleagues (2018), who estimated (without keeping track of the time explicitly) that reproducibility reports took between 2 and 25 person-hours, depending on whether the paper eventually fell in the reproducible or not-reproducible category, and whether author assistance was needed.
-The main difference might be that we did not write \enquote{reproducibility reports} for each article.
+One major difference between our approaches is that we did not write \enquote{reproducibility reports} for each article.
 Documenting the process of reproducing a paper adds transparency and allows others to check the the decisions about every value in an article.
@@
 The required time might be reduced by explicitly asking authors to submit files in a format or structure that facilitates such checks, or automating part of the work that is needed to check the reproducibility of results.
-Overall, we feel that the time required for a basic check of the reproducibility of manuscripts (i.e., where one checks whether the \emph{main} results in the paper are reproduced by the analysis scripts, but without documenting this step at the level of each individual number) is not an insurmountable problem for scientific journals that aim to add value, and would substantially improve the computational reproducibility of the published literature.
+Overall, we feel that the time required for a basic check of the reproducibility of manuscripts (i.e., where one checks whether the \emph{main} results in the paper are reproduced by the analysis scripts, but without documenting this step at the level of each individual number) is a surmountable hurdle for journals, and would substantially improve the computational reproducibility of the published literature.
 
-In addition to novel technologies, most progress can probably be made by developing standards within a research community, and educating researchers about best practices that guarantee reproducibility.
-Most researchers are not trained in reproducible data analysis, and can not be expected to invent best practices from scratch.
+In addition to novel technologies, most progress can probably be made by developing standards within research communities, and educating researchers about best practices that guarantee reproducibility.
+Most researchers are not trained in reproducible data analysis, and cannot be expected to invent best practices from scratch.
 As good examples appear in the published literature over time, and best practices within subdisciplines crystalize, standards should emerge that improve reproducibility, and that allow researchers to share data and code in such a way that others with basic scientific training can reproduce their results and reuse their data.
+
+\hypertarget{conflict-of-interest-statement}{%
+\section{Conflict of Interest Statement}\label{conflict-of-interest-statement}}
+
+One author (SG) worked at Code Ocean during the writing of this manuscript.
+SG joined the project after its accompanying Code Ocean component was already submitted and published, and did not write any of the text concerning Code Ocean.
 

### 2019-09-10 reproducing_registered_reports.Rmd
submission version

@@
 Because most researchers have not been trained in computational reproducibility, it is important to evaluate current practices to identify practices that can be improved.
-We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the in psychological literature between 2014 and 2018.
+We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the psychological literature between 2014 and 2018.
 Of the 62 articles that met our inclusion criteria, data was available for 40 articles, and analysis scripts for 37 articles.
@@
 
-There were differences between coders in how much expertise they had with R, SPSS, and JASP (PO had less experience, while JG and NC had more experience; SG ran all MATLAB and Python code).
+There were differences between coders in how much expertise they had with R, SPSS, and JASP (PO had less experience, while JG, NC and DL had more experience; SG ran all MATLAB and Python code).
 The more expertise coders had, the easier it was to reproduce findings (which lead to lower inter-rater reliability).

### 2019-09-11 reproducing_registered_reports.Rmd
submission

@@
   This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
-All code used to create this manuscript is provided in an OSF repository at https://osf.io/suqz3/.
 
@@
 We report these qualitative findings with an aim to highlight how current practices can be improved.
+
+### Data
+
+All data and the code used to create this manuscript is provided in an OSF repository at https://osf.io/suqz3/.
 
@@
 
+# Author Contributions
+
+P.
+Obels and D.
+Lakens developed the idea.
+All authors contributed data by reproducing analyses.
+P.
+Obels drafted the initial version of the manuscript, D.
+Lakens wrote the final version, all authors revised the manuscript.
+
 # Conflict of Interest Statement
+
 One author (SG) worked at Code Ocean during the writing of this manuscript.

### 2019-09-11 reproducing_registered_reports.tex
submission

@@
 \authornote{This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
-All code used to create this manuscript is provided in an OSF repository at \url{https://osf.io/suqz3/}.
 
@@
 We report these qualitative findings with an aim to highlight how current practices can be improved.
+
+\hypertarget{data}{%
+\subsubsection{Data}\label{data}}
+
+All data and the code used to create this manuscript is provided in an OSF repository at \url{https://osf.io/suqz3/}.
 
@@
 
+\hypertarget{author-contributions}{%
+\section{Author Contributions}\label{author-contributions}}
+
+P.
+Obels and D.
+Lakens developed the idea.
+All authors contributed data by reproducing analyses.
+P.
+Obels drafted the initial version of the manuscript, D.
+Lakens wrote the final version, all authors revised the manuscript.
+
 \hypertarget{conflict-of-interest-statement}{%

### 2020-01-12 reply_to_review.Rmd
first draft revision

---
title: "Reply to Review"
author: "Obels, Lakens, Coles, Gottfried, Green"
date: "23-11-2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

20-Nov-2019

Dear Dr. Lakens:

Thank you for submitting your General Article (AMPPS-19-0139) entitled "Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology" to Advances in Methods and Practices in Psychological Science (AMPPS). The manuscript has now been reviewed, and the reviewer comments appear at the end of this letter.

Both reviewers provided helpful suggestions for clarifying the methodology by providing additional detail. In the manuscript, it says “we considered an article reproducible when we could get the same main results as represented in the paper with at best minor changes to the analysis scripts” (p. 3). The reviewers noted that it could be helpful to specify how the main results were identified, and also what were considered to be minor changes. Reviewer 1 also asked for an operational definition of “reproducible” (e.g., was a result considered reproducible if there were only minor deviations between the reported and reproduced result?). The reviewers also requested further details about the reasons for low inter-rater reliability, the way you calculated average time to reproduce analyses, and the issues that were encountered when attempting to reproduce R scripts. I think these added clarifications could give readers an even fuller picture of how to maximize the reproducibility of their own work.

On a related note, Reviewer 2 mentioned that they would be interested to see your suggestions regarding developing standards and educating researchers about best practices. I agree with this reviewer that this is potentially an important contribution of the current paper, but I also see the recommendations you make on pp. 5-6 as an effort to provide such guidance. I’ll leave it up to you as to whether you think there is more to be said about standards and educating researchers at this point.

If you choose to submit a revision, please include include a letter detailing your point-by-point responses to each reviewer comment and indicating how you changed the manuscript to address them. The revised manuscript may undergo further peer review. We ask that you submit your revision within three months. Please let us know if you will not be able to meet this deadline.

To submit your revision, log into manuscript central and enter your Author Center, where you will find your manuscript title listed under "Manuscripts with Decisions." Under "Actions," click on "Create a Revision." Your manuscript number has been appended to denote a revision.

IMPORTANT: Your original files are available to you when you upload your revised manuscript. Please delete any redundant or outdated files before completing the submission.

Once again, thank you for submitting your manuscript to AMPPS and I look forward to receiving your revision.

Sincerely,

Alexa Tullett
Associate Editor, Advances in Methods and Practices in Psychological Science

Reviewer(s)' Comments to Author:
Reviewer: 1

Comments to the Author
Manuscript ID: AMPPS-19-0139
Manuscript title: Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology

Summary

This article reports an observational study designed to examine data sharing practices and computational reproducibility in the context of Registered Reports published in the field of psychology. Computational reproducibility is a minimal standard we should expect from all scientific manuscripts that involve data analysis and this is therefore an important topic to address.

The study is generally well designed, the reporting is reasonably clear and concise, conclusions appear well calibrated to the obtained evidence, limitations have been appropriately considered, and, generally, transparent research practices have been adopted (data and analysis scripts are publicly available and shared in a computational environment which enables reproducibility of the article). I am therefore satisfied that the article makes a quality contribution to the literature on this topic.

I have a few comments and suggestions which I hope might be a helpful.
Major Comments

1. It is reported that “After evaluating our initial coding round, we considered an article reproducible when we could get the same main results as represented in the paper with at best minor changes to the analysis scripts.” – could a more precise operationalization of these variables be provided? It is not always clear what the main results of a paper are for example, particularly if the paper reports multiple outcomes and/or experiments.

2. “Reproducibility” is not actually defined operationally. Presumably, if values matched exactly, they were considered reproducible, but was any deviation from exactly identical considered to be non-reproducible? It is also not entirely clear which values were examined. For example, were all numerical values related to the ‘main results’ examined, including say, sample sizes, means, standard deviations, degrees of freedom, test statistics, p-values? Or just some subset of these? More detail would be welcome.

3. The findings are reported in terms of how many “articles that could be computationally reproduced” (from the abstract) but it is also stated that only the “main findings” were checked.

4. According to statements in the discussion, it seems that the reproducibility assessments conducted have not been documented in a step-by-step manner or themselves made reproducible. This is explained on the grounds that it would have taken a lot of time - but it does seem a bit unfortunate given the topic and recommendations of the paper. Without this level of detail, it is not clear to me how an independent researcher could systematically repeat and verify the methods employed.
Minor Comments

1. The description of Hardwicke et al. (2018) in the introduction states that “Eleven articles could be reproduced…”. Actually Hardwicke et al. report that they only examined a subset of the results reported in each article they examined.

2. In the introduction it states that “The novelty of Registered Reports may attract early adopters who are also exploring other novel developments aimed at improving research practices in psychology, such as data and code sharing. We hypothesized that researchers who publish Registered Reports would also be likely to share data and code in public repositories”. It may also be worth mentioning that journals that adopt Registered Reports are probably more likely to be adopting policies that encourage or mandate data sharing.

3. Later in the manuscript it states that “We examined how many authors voluntarily shared data and code” – but it is not clear how it was determined that the sharing was voluntarily (rather than a response to a journal mandate or request from a reviewer/editor).

4. Several comparisons are made to a study by Hardwicke et al. (2018) and so it might be worth noting that in that study the researchers were assessing analytic reproducibility whereas in the present study the focus was on computational reproducibility. The two terms are very similar and sometimes used interchangeably – however in the former case, the researchers wrote their own code from scratch in an attempt to repeat the original analysis as it was reported in the original studies (most original analysis scripts were not available). By contrast, in the present study, the focus was on re-running the scripts provided by the original authors. This difference may be particularly pertinent to the comparison of time taken to complete the reproducibility checks (for example).

5. The structure of the paper is a little erratic, with both methodological information and discussion blending into the results section and some results appearing in the introduction.

6. The low inter-rater reliability between coders trying to execute scripts was surprising because this seems (naively perhaps!) like a fairly straightforward mechanical task to perform – could more details and examples could be provided to illustrate why there were problems with this.

7. The study does not appear to have been pre-registered (there is no mention of it). Although some benefit may have been gained by pre-registering, this omission is not overly concerning given that (a) the study is being reported; (b) the study is fairly clearly exploratory and descriptive in nature. Nevertheless, I would recommend stating the absence of a pre-registration explicitly and providing a disclosure statement which states whether all data collected, all measured variables, and all analyses conducted have been reported in the manuscript.

Reviewer: 2

Comments to the Author
This manuscript discusses issues related to computational reproducibility within Registered Reports in psychology. Computational reproducibility is an aspect of (open) science that is, in my view, often overlooked or regarded as being of lesser importance (compared to, for example, preregistration or other forms of reproducibility).

Overall, I think this manuscript does a good job of conveying not only the issue that there are still many findings out there that lack the data and code to reproduce results, but also that achieving reproducibility entails much more than merely sharing that data and code. I think it is particularly worrisome that of the 35 RRs in your sample that linked to data and code, only 20 contained actual reproducible results. This means that even those researchers who appear to have the best intentions, still often don't get it right. Especially taking into account that these are RRs, which are up there in the *league of good research practices*.

Naturally, I checked out the OSF page associated with this manuscript, and tried to reproduce it all. Even though I had some issues with the Markdown script (I'm running R 3.6.1 which does not run papaja), your README file provided me with enough information to get me the results I wanted to see. I also appreciate the use of a comprehensive codebook and the multiple output files (.tex, .Rmd etc.). The low inter-rater reliability just shows how hard it is to make something completely reproducible and accessible for as many people as possible, on as many different systems as possible.

Generally, I am positive about this paper. I think it is a timely contribution to the literature, and relevant to any researcher working with (shareable) data and code. I very much like that you've included novel technological solutions such as Code Ocean and Whole Tale, as well as references to examples of best practices. Overall, I would accept this article for publication, and the only reason I ticked "revise and resubmit" is because of the following small remarks and clarification questions, that are easy to solve. In order of the manuscript (not importance):

Page 2, method section: you state you found 81 articles that were published in psychology, which I think should be 79.

Page 2: inconsistent number of decimal points (e.g., in percentages).

Page 3, there is a random "+" after the Gertler & Bullock reference.

Page 3, sentence starting with "We used a dichotomous" is worded a bit weird.

Page 3: I did not fully get the following part: "even if variables could only be found with reasonable effort". Do you mean "data" that could be found?

Page 3 - You state you would consider an analysis reproducible, even if you had to make "minor changes". A bit earlier on the page you reference the possibility of rewriting SPSS .sps syntax to R syntax. Does this fall under the minor changes you mention? (I would call that a major change). In general, could you clarify the minor changes a bit more?

Page 4 – It wasn’t immediately clear to me if the average time to reproduce analyses includes everything, from reading the manuscript for the first time to matching the reported and reproduced results? If so, I commend you on your speed (even though I can assume that it must have felt very tedious at times)!

Page 5 - In the discussion section, you state issues you encountered with SPSS scripts. However, the R analyses took longer to reproduce, and the issues with R scripts were not clear to me. In the paragraph before the SPSS script one, you state researchers should be clear on the order of R scripts- was that the biggest issue with the R scripts?

Page 5 - You introduce in the "Nevertheless," paragraph 4 points researchers should focus on (ABCD). The next paragraph ("First,") has A, the paragraph after that ("Second,") has B and D, and the paragraph after ("Based") has C. It is minor but the change in order distracted me while reading it for the first time.

Page 7 - You state developing standards and educating researchers about best practices could help progress. Are there any examples that you could add here? If this is such an important point, I think some clarification could help.

Datafile, codebook tab: I don't fully understand the included_language variable on line 20. To me it reads as if the programming language should be included in the final dataset and I do not understand why.

That's all! Please let me know if I can provide any clarification on some points.

### 2020-01-12 manuscript_version_1/reproducing_registered_reports.Rmd
first draft revision

--- 2019-09-11 reproducing_registered_reports.Rmd
@@
 List all the packages that the code needs to run at the top of the script.
-Because packages update, it is necessary to report the version numbers of packages that were used (for example using packrat, or copying the output of the the sessionInfo() function as a comment in the script).
+Because packages update, it is necessary to report the version numbers of packages that were used (for example using packrat, or copying the output of the sessionInfo() function as a comment in the script).
 Remember that folder names and folder structures differ between computers, and therefore you should use relative locations (and not “c:/user/myfolder/code”).

### 2020-01-12 manuscript_version_2/reproducing_registered_reports.Rmd
first draft revision

--- 2020-01-12 manuscript_version_1/reproducing_registered_reports.Rmd
@@
 We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the psychological literature between 2014 and 2018.
-Of the 62 articles that met our inclusion criteria, data was available for 40 articles, and analysis scripts for 37 articles.
-For the 35 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 articles, and reproduce the main results for 20 articles.
-Although the articles that shared both data and code (35 out of 62, or 56%) and articles that could be computationally reproduced (20 out of 35, or 57%) was relatively high compared to other studies, there is clear room for improvement.
+Of the 62 articles that met our inclusion criteria, data was available for 41 articles, and analysis scripts for 37 articles.
+For the 36 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 articles, and reproduce the main results for 20 articles.
+Although the articles that shared both data and code (36 out of 62, or 58%) and articles that could be computationally reproduced (20 out of 36, or 56%) was relatively high compared to other studies, there is clear room for improvement.
 We provide practical recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.
@@
 
-all_data <- read_excel("Data_for_Analysis_of_Open_Data_and_Computational_Reproducibility_in_Registered_Reports_in_Psychology.xlsx", n_max = 62)
+all_data <- read_excel("../Data_for_Analysis_of_Open_Data_and_Computational_Reproducibility_in_Registered_Reports_in_Psychology.xlsx", n_max = 62)
 
@@
 We hypothesized that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
-In line with our hypothesis, `r sum(all_data$availability, na.rm = TRUE)` out of `r length(all_data$doi)` articles in our final dataset shared at least some of the data and code (`r round(100*sum(all_data$availability, na.rm = TRUE)/length(all_data$doi),1)`%).
-In comparison, after the journal *Cognition* introduced a mandatory data sharing policy, 136 out of 174 articles (78.2%) had a data availability statement, 85 of 174 articles (49%) had reusable data, and only 18 out of 174 articles (10.3%) provided the analysis code (Hardwicke et al., 2018).
+In line with our hypothesis, `r sum(all_data$availability, na.rm = TRUE)` out of `r length(all_data$doi)` articles in our final dataset shared at least some of the data and code (`r sprintf("%.1f", round(100*sum(all_data$availability, na.rm = TRUE)/length(all_data$doi),1))`%).
+In comparison, after the journal *Cognition* introduced a mandatory data sharing policy, 136 out of 174 articles (78.2%) had a data availability statement, 85 of 174 articles (49.0%) had reusable data, and only 18 out of 174 articles (10.3%) provided the analysis code (Hardwicke et al., 2018).
 To evaluate the reproducibility of findings published in Registered Reports, we examined if data could be located, were available at the indicated location, could be opened in open-source or accessible software, were documented well enough to be understandable, and could be used to reproduce the main analyses reported in the published manuscript.
@@
 To find Registered Reports published in psychology, we drew from a database of registered reports maintained by the Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
-Eighty-one articles in this database were published in the psychological literature.
+Seventy-nine articles in this database were published in the psychological literature.
 We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018].
@@
 A hyperlink to a website that contains the data and script also suffices, although hyperlinks are known to break over time [@gertler_reference_2017].
-+
+
 Of the `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to data and/or code that were part of the article.
@@
 Note that we had access to SPSS and therefore reproduced the analyses using the original .sps scripts where available.
+When examining whether analyses were reproducible, we only used the same software packages as had been used by the original authors.
 The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files, which require dedicated EEG software and could not be reproduced (we also could not find the analysis code for this article).
@@
 
-We used a dichotomous coding scheme to when coding whether the script could be executed whether the results could be reproduced ('yes' or 'no'), but coders often reported 'partial' reproducibility.
-Code often needed minor adjustments to run on the data, such as changing file locations, or loading packages in R, and coders sometimes took different approaches to how much they would adjust the code to make it run on the data.
+When coding whether the script could be executed and the results could be reproduced we resorted to a dichotomous classification ('yes' or 'no'), but coders often reported 'partial' reproducibility.
+Code often needed minor adjustments to run on the data, such as changing file locations, or loading packages in R, and coders sometimes took different approaches to how much they would adjust the code to make it run on the data (for detailed comments, see our data file).
 Furthermore, coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article.
 After evaluating our initial coding round, we considered an article reproducible when we could get the same *main results* as represented in the paper with at best *minor changes* to the analysis scripts.
-This means we considered the analysis reproducible, even if variables could only be found with reasonable effort or by making assumptions about how variable names mapped onto variables reported in the data analysis.
+This means we considered the analysis reproducible, even if in absence of a codebook coders had to search through the analysis code and dataset to identify how variable and label names related to the results reported in the paper.
 Furthermore, we changed folder locations when needed, and installed and/or loaded required libraries.
 Finally, even though sometimes figures were generated in R and contained relevant information (e.g., the pattern of means) we did not require all figures to be reproducible.
+For each study reported in the article we identified main results (i.e., any reported descriptives and statistical tests) based on the research question highlighted in the title and abstract.
+Approximately half of the Registered Reports consisted of replication studies, where the main analysis was explicitly stated based on a previous study.
+In the remaining Registered Reports the main research question was often stated clearly in a 'confirmatory analyses' section, and were the analyses the sample size justification was based on.
+Nevertheless, some arbitrary judgments were required when deciding which analyses were part of the main results.
 
@@
 R was used as a coding language in `r length(run_script_r)`, of which `r sum(run_script_r)` scripts could be run on the data, `r length(run_script_spss)` papers used SPSS, for `r sum(run_script_spss)` of which the script could be run, and `r length(run_script_r_spss)` papers used both SPSS and R, for which the scripts could be run for all `r sum(run_script_r_spss)` papers.
-JASP does not seperate the data and code, but instead stores both in a single JASP file.
+JASP does not separate the data and code, but instead stores both in a single JASP file.
 This means that the analyses are always directly linked to the code for every output.
@@
 
-The average time to reproduce analyses reported in R was `r round(mean(time_r_po, na.rm = TRUE),2)` minutes for the first coder (SD = `r round(sd(time_r_po, na.rm = TRUE),2)`) and `r round(mean(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)` minutes (SD =  `r round(sd(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)`) for the second coder.
+After the data and code had been downloaded, and the reported results were identified by looking through the article, the average time to reproduce analyses reported in R was `r round(mean(time_r_po, na.rm = TRUE),2)` minutes for the first coder (SD = `r round(sd(time_r_po, na.rm = TRUE),2)`) and `r round(mean(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)` minutes (SD =  `r round(sd(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)`) for the second coder.
 Reproducing the SPSS analysis took on average `r round(mean(time_spss_po, na.rm = TRUE),2)` minutes (SD = `r round(sd(time_spss_po, na.rm = TRUE),2)`) for the first coder and  `r round(mean(as.numeric(all_data$time_reproducing_jg), na.rm = TRUE),2)` minutes (SD = `r round(sd(as.numeric(all_data$time_reproducing_jg), na.rm = TRUE),2)`) for the second coder.
@@
 Hardwicke et al., 2018).
-This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output analysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process.
+This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output analysis code creates, (c) check whether the code you shared still reproduces all analyses after revisions during the peer review process, and (d) list packages that are required in R and the versions used at the top of your R file.
 We will discuss each of these points below, and link to examples of good practices that we encountered.
@@
 Second, code should be well-annotated, so that it is understandable for researchers who did not write the code.
-Well-annotated code makes clear what the analysis code does, in which order it should be run, and which output each section of analysis code generates.
+Well-annotated code makes clear what the analysis code does, in which order scripts should be run if there are multiple scripts (e.g., to pre-process the raw data, compute sum scores, analyze the results, and generate graphs), and which output each section of analysis code generates.
 A good example of well-annotated code can be found in the materials of @weston_role_2018.
@@
 It provides a code environment (or container) that runs online, which means that researchers using Code Ocean do not have to download data, code, or software, but can analyze the data in their browser.
-It is not currently possible to use SPSS within Code Ocean, but for R code, it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.^[For a Code Ocean capsule reproducing this manuscript, see https://doi.org/10.24433/CO.4275368.v1] Other platforms in the reproducibility space include Whole Tale [@brinckman2019computing], "a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage" (p.
+It is not currently possible to use SPSS within Code Ocean, but for R code, it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.^[For a Code Ocean capsule reproducing this manuscript, see https://doi.org/10.24433/CO.4275368.v1] Other platforms in the reproducibility space include Whole Tale [@brinckman_computing_2019], "a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage" (p.
 855); and Binder [@ragan2018binder], an open-source, browser-based tool for creating and sharing reproducible environments.
-
 Another useful technology is RMarkdown, which enable researchers to write fully executable manuscripts.

### 2020-01-12 manuscript_version_2/reproducing_registered_reports.tex
first draft revision

--- 2019-09-11 reproducing_registered_reports.tex
@@
-\documentclass[,jou, a4paper,floatsintext]{apa6}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  ,jou, a4paper,floatsintext]{apa6}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
   \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
   pdftitle={Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology},
@@
   pdfkeywords={reproducibility, Registered Reports, data sharing, open science},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-  \title{Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology}
-    \author{Pepijn Obels\textsuperscript{1}, Daniel Lakens\textsuperscript{1}, Nicholas A. Coles\textsuperscript{2}, Jaroslav Gottfried\textsuperscript{3}, \& Seth Ariel Green\textsuperscript{4}}
-    \date{}
-
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 \shorttitle{Reproducing Registered Reports}
@@
 
+\title{Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology}
+\author{Pepijn Obels\textsuperscript{1}, Daniel Lakens\textsuperscript{1}, Nicholas A. Coles\textsuperscript{2}, Jaroslav Gottfried\textsuperscript{3}, \& Seth Ariel Green\textsuperscript{4}}
+\date{}
+
 \authornote{This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
@@
 We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the psychological literature between 2014 and 2018.
-Of the 62 articles that met our inclusion criteria, data was available for 40 articles, and analysis scripts for 37 articles.
-For the 35 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 articles, and reproduce the main results for 20 articles.
-Although the articles that shared both data and code (35 out of 62, or 56\%) and articles that could be computationally reproduced (20 out of 35, or 57\%) was relatively high compared to other studies, there is clear room for improvement.
+Of the 62 articles that met our inclusion criteria, data was available for 41 articles, and analysis scripts for 37 articles.
+For the 36 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 articles, and reproduce the main results for 20 articles.
+Although the articles that shared both data and code (36 out of 62, or 58\%) and articles that could be computationally reproduced (20 out of 36, or 56\%) was relatively high compared to other studies, there is clear room for improvement.
 We provide practical recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.
@@
 The availability of analysis code makes it possible for peers to check and correct published findings.
-According to Kitzes, Turek, and Deniz (2017), computational reproducibility means that ''a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.'' For scientific research to be computationally reproducible, the data and code need to be shared.
+According to Kitzes, Turek, \& Deniz (2017), computational reproducibility means that ''a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.'' For scientific research to be computationally reproducible, the data and code need to be shared.
 
@@
 The authors estimated that it took between 2-25 hours to reproduce the reported results per article, but they did not record the exact time.
-Stockemer, Koehler, and Lentz (2018) analyzed reproducibility in all articles published in 2015 in three political science journals.
+Stockemer, Koehler, \& Lentz (2018) analyzed reproducibility in all articles published in 2015 in three political science journals.
 They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one paper's results could not be reproduced due to a lack of a software license, and 16 articles' findings could not be reproduced with access to the required software.
 For the remaining articles, 32 sets of results could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results.
-Stodden, Seiler, and Ma (2018) analyzed data availability in the journal \emph{Science} in 2011-2012 and found that 26 of 204 (or 13\%) of articles provided information to retrieve data and/or code without contacting the authors.
+Stodden, Seiler, \& Ma (2018) analyzed data availability in the journal \emph{Science} in 2011-2012 and found that 26 of 204 (or 13\%) of articles provided information to retrieve data and/or code without contacting the authors.
 For all datasets they acquired after e-mailing authors for data and code, 26\% were estimated to be computationally reproducible.
@@
 We hypothesized that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
-In line with our hypothesis, 43 out of 62 articles in our final dataset shared at least some of the data and code (69.40\%).
-In comparison, after the journal \emph{Cognition} introduced a mandatory data sharing policy, 136 out of 174 articles (78.2\%) had a data availability statement, 85 of 174 articles (49\%) had reusable data, and only 18 out of 174 articles (10.3\%) provided the analysis code (Hardwicke et al., 2018).
+In line with our hypothesis, 43 out of 62 articles in our final dataset shared at least some of the data and code (69.4\%).
+In comparison, after the journal \emph{Cognition} introduced a mandatory data sharing policy, 136 out of 174 articles (78.2\%) had a data availability statement, 85 of 174 articles (49.0\%) had reusable data, and only 18 out of 174 articles (10.3\%) provided the analysis code (Hardwicke et al., 2018).
 To evaluate the reproducibility of findings published in Registered Reports, we examined if data could be located, were available at the indicated location, could be opened in open-source or accessible software, were documented well enough to be understandable, and could be used to reproduce the main analyses reported in the published manuscript.
@@
 To find Registered Reports published in psychology, we drew from a database of registered reports maintained by the Center for Open Science.\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
-Eighty-one articles in this database were published in the psychological literature.
+Seventy-nine articles in this database were published in the psychological literature.
 We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports (Hagger et al., 2016) and Many Labs projects (Klein et al., 2014, 2018).
@@
 A hyperlink to a website that contains the data and script also suffices, although hyperlinks are known to break over time (Gertler \& Bullock, 2017).
-+
+
 Of the 62 papers, 45 linked to data and/or code that were part of the article.
@@
 Altogether, some data or code was available for 43 of 62 papers.
-For 37 articles, the available code contained the statistical analyses, and for 40, all the required data files were available to reproduce the reported results (for 35 articles both data and code were available).
+For 37 articles, the available code contained the statistical analyses, and for 41, all the required data files were available to reproduce the reported results (for 36 articles both data and code were available).
 
@@
 After searching the OSF, data or code was available for 43 studies, of which 39 articles used SPSS, R, MATLAB, Python, or JASP.
-Of the 62 papers 37 shared the analysis script and 40 shared all data.
+Of the 62 papers 37 shared the analysis script and 41 shared all data.
 The analysis script could be run for 31 articles.
-For the 35 articles for which data and code were available, the main results could be reproduced for 20.
+For the 36 articles for which data and code were available, the main results could be reproduced for 20.
 }
@@
 
-Finally, we examined how many of the 35 articles with data and code could be reproduced.
+Finally, we examined how many of the 36 articles with data and code could be reproduced.
 It is possible that running the code on the data reproduces all analyses, even when the data file itself is not understandable (i.e., the data columns are not labeled).
@@
 
-We used a dichotomous coding scheme to when coding whether the script could be executed whether the results could be reproduced (\enquote{yes} or \enquote{no}), but coders often reported \enquote{partial} reproducibility.
-Code often needed minor adjustments to run on the data, such as changing file locations, or loading packages in R, and coders sometimes took different approaches to how much they would adjust the code to make it run on the data.
+When coding whether the script could be executed and the results could be reproduced we resorted to a dichotomous classification (\enquote{yes} or \enquote{no}), but coders often reported \enquote{partial} reproducibility.
+Code often needed minor adjustments to run on the data, such as changing file locations, or loading packages in R, and coders sometimes took different approaches to how much they would adjust the code to make it run on the data (for detailed comments, see our data file).
 Furthermore, coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article.
 After evaluating our initial coding round, we considered an article reproducible when we could get the same \emph{main results} as represented in the paper with at best \emph{minor changes} to the analysis scripts.
-This means we considered the analysis reproducible, even if variables could only be found with reasonable effort or by making assumptions about how variable names mapped onto variables reported in the data analysis.
+This means we considered the analysis reproducible, even if in absence of a codebook coders had to search through the analysis code and dataset to identify how variable and label names related to the results reported in the paper.
 Furthermore, we changed folder locations when needed, and installed and/or loaded required libraries.
 Finally, even though sometimes figures were generated in R and contained relevant information (e.g., the pattern of means) we did not require all figures to be reproducible.
+For each study reported in the article we identified main results (i.e., any reported descriptives and statistical tests) based on the research question highlighted in the title and abstract.
+Approximately half of the Registered Reports consisted of replication studies, where the main analysis was explicitly stated based on a previous study.
+In the remaining Registered Reports the main research question was often stated clearly in a \enquote{confirmatory analyses} section, and were the analyses the sample size justification was based on.
+Nevertheless, some arbitrary judgments were required when deciding which analyses were part of the main results.
 
@@
 For each article, two coders examined whether the code could be run on the data.
-Of the original 62 articles, the analysis code and data were available for 35 articles.
+Of the original 62 articles, the analysis code and data were available for 36 articles.
 We were able to run the code for 31 out of the 37 articles.
 R was used as a coding language in 13, of which 10 scripts could be run on the data, 17 papers used SPSS, for 15 of which the script could be run, and 3 papers used both SPSS and R, for which the scripts could be run for all 3 papers.
-JASP does not seperate the data and code, but instead stores both in a single JASP file.
+JASP does not separate the data and code, but instead stores both in a single JASP file.
 This means that the analyses are always directly linked to the code for every output.
@@
 Some analyses in a paper might not be part of the code or the output.
-We found that 20 out of 35 papers (57.10\%) that included their data and code could be used to reproduce the main results in the article.
+We found that 20 out of 36 papers (55.60\%) that included their data and code could be used to reproduce the main results in the article.
 
-The average time to reproduce analyses reported in R was 27.08 minutes for the first coder (SD = 28.55) and 32.50 minutes (SD = 20.95) for the second coder.
+After the data and code had been downloaded, and the reported results were identified by looking through the article, the average time to reproduce analyses reported in R was 27.08 minutes for the first coder (SD = 28.55) and 32.50 minutes (SD = 20.95) for the second coder.
 Reproducing the SPSS analysis took on average 17.35 minutes (SD = 9.54) for the first coder and 25.50 minutes (SD = 9.72) for the second coder.
@@
 We analyzed data and scripts of 62 Registered Reports to examine how many authors shared their data and code, and how often main results reported in the manuscript could be reproduced.
-In total, 35 out of 62 (or 56.50\%) of the articles shared the underlying data and the code that was used to generate the results.
+In total, 36 out of 62 (or 58.10\%) of the articles shared the underlying data and the code that was used to generate the results.
 Authors of Registered Reports in psychology seem to voluntarily choose to share data and code relatively often compared to authors of articles in political science (Stockemer et al., 2018).
@@
 We encountered several common issues that made results reported in Registered Reports difficult to reproduce (cf.~Hardwicke et al., 2018).
-This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output analysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process.
+This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output analysis code creates, (c) check whether the code you shared still reproduces all analyses after revisions during the peer review process, and (d) list packages that are required in R and the versions used at the top of your R file.
 We will discuss each of these points below, and link to examples of good practices that we encountered.
@@
 Second, code should be well-annotated, so that it is understandable for researchers who did not write the code.
-Well-annotated code makes clear what the analysis code does, in which order it should be run, and which output each section of analysis code generates.
-A good example of well-annotated code can be found in the materials of Weston and Jackson (2018).
+Well-annotated code makes clear what the analysis code does, in which order scripts should be run if there are multiple scripts (e.g., to pre-process the raw data, compute sum scores, analyze the results, and generate graphs), and which output each section of analysis code generates.
+A good example of well-annotated code can be found in the materials of Weston \& Jackson (2018).
 It helps to make clear how the analysis code relates to the analyses reported in the paper, to make it easier for others to identify which code generates which results in the paper.
@@
 Explicitly linking code in the analysis script to the final manuscript also helps researchers to check whether all results in the article are reproduced by the shared code.
-An example of a data analysis file that clearly links the code to the final articles can be found in the materials of Voorspoels, Bartlema, and Vanpaemel (2014).
+An example of a data analysis file that clearly links the code to the final articles can be found in the materials of Voorspoels, Bartlema, \& Vanpaemel (2014).
 If analyses are performed that are not included in the manuscript, this should be stated explicitly (e.g., assumption checks, exploratory analyses, etc.).
@@
 List all the packages that the code needs to run at the top of the script.
-Because packages update, it is necessary to report the version numbers of packages that were used (for example using packrat, or copying the output of the the sessionInfo() function as a comment in the script).
+Because packages update, it is necessary to report the version numbers of packages that were used (for example using packrat, or copying the output of the sessionInfo() function as a comment in the script).
 Remember that folder names and folder structures differ between computers, and therefore you should use relative locations (and not \enquote{c:/user/myfolder/code}).
@@
 It is not currently possible to use SPSS within Code Ocean, but for R code, it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.\footnote{For a Code Ocean capsule reproducing this manuscript, see \url{https://doi.org/10.24433/CO.4275368.v1}} Other platforms in the reproducibility space include Whole Tale (Brinckman et al., 2019), \enquote{a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage} (p.~855); and Binder (Ragan-Kelley \& Willing, 2018), an open-source, browser-based tool for creating and sharing reproducible environments.
-
 Another useful technology is RMarkdown, which enable researchers to write fully executable manuscripts.
@@
 
-\leavevmode\hypertarget{ref-brinckman2019computing}{}%
+\leavevmode\hypertarget{ref-brinckman_computing_2019}{}%
 Brinckman, A., Chard, K., Gaffney, N., Hategan, M., Jones, M.
-B., Kowalik, K., \ldots{} others.
+B., Kowalik, K., \ldots{} Turner, K.
 (2019).
-Computing environments for reproducibility: Capturing the ``whole tale''.
+Computing environments for reproducibility: Capturing the ``Whole Tale''.
 \emph{Future Generation Computer Systems}, \emph{94}, 854--867.
+doi:\href{https://doi.org/10.1016/j.future.2017.12.029}{10.1016/j.future.2017.12.029}
+
+\leavevmode\hypertarget{ref-campbell_self-esteem_2018}{}%
+Campbell, L., Balzarini, R.
+N., Kohut, T., Dobson, K., Hahn, C.
+M., Moroz, S.
+E., \& Stanton, S.
+C.
+E.
+(2018).
+Self-esteem, relationship threat, and dependency regulation: Independent replication of Murray, Rose, Bellavia, Holmes, and Kusche (2002) Study 3.
+\emph{Journal of Research in Personality}, \emph{72}, 5--9.
+doi:\href{https://doi.org/10.1016/j.jrp.2017.04.001}{10.1016/j.jrp.2017.04.001}
+
+\leavevmode\hypertarget{ref-chambers_instead_2014}{}%
+Chambers, C.
+D., Feredoes, E., Muthukumaraswamy, S.
+D., \& Etchells, P.
+(2014).
+Instead of "playing the game" it is time to change the rules: Registered Reports at AIMS Neuroscience and beyond.
+\emph{AIMS Neuroscience}, \emph{1}, 4--17.
+doi:\href{https://doi.org/10.3934/Neuroscience2014.1.4}{10.3934/Neuroscience2014.1.4}
+
+\leavevmode\hypertarget{ref-clyburne-sherin_computational_2018}{}%
+Clyburne-Sherin, A., Fei, X., \& Green, S. A. (2018). Computational Reproducibility via Containers in Social Psychology. doi:\href{https://doi.org/10.31234/osf.io/mf82t}{10.31234/osf.io/mf82t}
+
+\leavevmode\hypertarget{ref-gertler_reference_2017}{}%
+Gertler, A.
+L., \& Bullock, J.
+G.
+(2017).
+Reference Rot: An Emerging Threat to Transparency in Political Science.
+\emph{PS: Political Science \& Politics}, \emph{50}(1), 166--171.
+doi:\href{https://doi.org/10.1017/S1049096516002353}{10.1017/S1049096516002353}
+
+\leavevmode\hypertarget{ref-hagger_multilab_2016}{}%
+Hagger, M.
+S., Chatzisarantis, N.
+L.
+D., Alberts, H., Anggono, C.
+O., Batailler, C., Birt, A.
+R., \ldots{} Zwienenberg, M.
+(2016).
+A Multilab Preregistered Replication of the Ego-Depletion Effect.
+\emph{Perspectives on Psychological Science}, \emph{11}(4), 546--573.
+doi:\href{https://doi.org/10.1177/1745691616652873}{10.1177/1745691616652873}
+
+\leavevmode\hypertarget{ref-hardwicke_data_2018}{}%
+Hardwicke, T.
+E., Mathur, M.
+B., MacDonald, K., Nilsonne, G., Banks, G.
+C., Kidwell, M.
+C., \ldots{} Frank, M.
+C.
+(2018).
+Data availability, reusability, and analytic reproducibility: Evaluating the impact of a mandatory open data policy at the journal Cognition.
+\emph{Open Science}, \emph{5}(8), 180448.
+doi:\href{https://doi.org/10.1098/rsos.180448}{10.1098/rsos.180448}
+
+\leavevmode\hypertarget{ref-kitzes_practice_2017}{}%
+Kitzes, J., Turek, D., \& Deniz, F. (2017). \emph{The Practice of Reproducible Research: Case Studies and Lessons from the Data-Intensive Sciences}. Univ of California Press.
+
+\leavevmode\hypertarget{ref-klein_investigating_2014}{}%
+Klein, R.
+A., Ratliff, K.
+A., Vianello, M., Adams, R.
+B., Bahník, Š., Bernstein, M.
+J., \ldots{} Nosek, B.
+A.
+(2014).
+Investigating Variation in Replicability.
+\emph{Social Psychology}, \emph{45}(3), 142--152.
+doi:\href{https://doi.org/10.1027/1864-9335/a000178}{10.1027/1864-9335/a000178}
+
+\leavevmode\hypertarget{ref-klein_many_2018}{}%
+Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams, R.
+B., Alper, S., \ldots{} Nosek, B.
+A.
+(2018).
+Many Labs 2: Investigating Variation in Replicability Across Samples and Settings.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 443--490.
+doi:\href{https://doi.org/10.1177/2515245918810225}{10.1177/2515245918810225}
+
+\leavevmode\hypertarget{ref-le_open_2018}{}%
+Le, B. (2018, May). Open Science Manual. https://bit.ly/2w2F6Xu.
+
+\leavevmode\hypertarget{ref-morey_peer_2016}{}%
+Morey, R.
+D., Chambers, C.
+D., Etchells, P.
+J., Harris, C.
+R., Hoekstra, R., Lakens, D., \ldots{} others.
+(2016).
+The Peer Reviewers' Openness Initiative: Incentivizing open research practices through peer review.
+\emph{Royal Society Open Science}, \emph{3}(1), 150547.
+
+\leavevmode\hypertarget{ref-nosek_registered_2014}{}%
+Nosek, B. A., \& Lakens, D. (2014). Registered Reports. \emph{Social Psychology}, \emph{45}(3), 137--141. doi:\href{https://doi.org/10.1027/1864-9335/a000192}{10.1027/1864-9335/a000192}
+
+\leavevmode\hypertarget{ref-ragan2018binder}{}%
+Ragan-Kelley, B., \& Willing, C. (2018). Binder 2.0-reproducible, interactive, sharable environments for science at scale.
+
+\leavevmode\hypertarget{ref-stockemer_data_2018}{}%
+Stockemer, D., Koehler, S., \& Lentz, T.
+(2018).
+Data Access, Transparency, and Replication: New Insights from the Political Behavior Literature.
+\emph{PS: Political Science \& Politics}, \emph{51}(4), 799--803.
+doi:\href{https://doi.org/10.1017/S1049096518000926}{10.1017/S1049096518000926}
+
+\leavevmode\hypertarget{ref-stodden_empirical_2018}{}%
+Stodden, V., Seiler, J., \& Ma, Z.
+(2018).
+An empirical analysis of journal policy effectiveness for computational reproducibility.
+\emph{Proceedings of the National Academy of Sciences}, \emph{115}(11), 2584--2589.
+doi:\href{https://doi.org/10.1073/pnas.1708290115}{10.1073/pnas.1708290115}
+
+\leavevmode\hypertarget{ref-voorspoels_can_2014}{}%
+Voorspoels, W., Bartlema, A., \& Vanpaemel, W.
+(2014).
+Can race really be erased?
+A pre-registered replication study.
+\emph{Frontiers in Psychology}, \emph{5}.
+doi:\href{https://doi.org/10.3389/fpsyg.2014.01035}{10.3389/fpsyg.2014.01035}
+
+\leavevmode\hypertarget{ref-wesselmann_revisiting_2014}{}%
+Wesselmann, E.
+D., Williams, K.
+D., Pryor, J.
+B., Eichler, F.
+A., Gill, D.
+M., \& Hogue, J.
+D.
+(2014).
+Revisiting Schachter's Research on Rejection, Deviance, and Communication (1951).
+\emph{Social Psychology}, \emph{45}(3), 164--169.
+doi:\href{https://doi.org/10.1027/1864-9335/a000180}{10.1027/1864-9335/a000180}
+
+\leavevmode\hypertarget{ref-weston_role_2018}{}%
+Weston, S.
+J., \& Jackson, J.
+J.
+(2018).
+The role of vigilance in the relationship between neuroticism and health: A registered report.
+\emph{Journal of Research in Personality}, \emph{73}, 27--34.
+doi:\href{https://doi.org/10.1016/j.jrp.2017.10.005}{10.1016/j.jrp.2017.10.005}
+
+\leavevmode\hypertarget{ref-wilkinson_fair_2016}{}%
+Wilkinson, M.
+D., Dumontier, M., Aalbersberg, I.
+J., Appleton, G., Axton, M., Baak, A., \ldots{} Mons, B.
+(2016).
+The FAIR Guiding Principles for scientific data management and stewardship.
+\emph{Scientific Data}, \emph{3}, 160018.
+doi:\href{https://doi.org/10.1038/sdata.2016.18}{10.1038/sdata.2016.18}
+
+\leavevmode\hypertarget{ref-arslan_how_2019}{}%
+Arslan, R.
+C.
+(2019).
+How to Automatically Document Data With the codebook Package to Facilitate Data Reuse.
+\emph{Advances in Methods and Practices in Psychological Science}, 2515245919838783.
+doi:\href{https://doi.org/10.1177/2515245919838783}{10.1177/2515245919838783}
+
+\leavevmode\hypertarget{ref-brinckman_computing_2019}{}%
+Brinckman, A., Chard, K., Gaffney, N., Hategan, M., Jones, M.
+B., Kowalik, K., \ldots{} Turner, K.
+(2019).
+Computing environments for reproducibility: Capturing the ``Whole Tale''.
+\emph{Future Generation Computer Systems}, \emph{94}, 854--867.
+doi:\href{https://doi.org/10.1016/j.future.2017.12.029}{10.1016/j.future.2017.12.029}
 

### 2020-01-13 manuscript_version_2/reproducing_registered_reports.Rmd
first draft revision

@@
 We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the psychological literature between 2014 and 2018.
-Of the 62 articles that met our inclusion criteria, data was available for 41 articles, and analysis scripts for 37 articles.
-For the 36 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 articles, and reproduce the main results for 20 articles.
-Although the articles that shared both data and code (36 out of 62, or 58%) and articles that could be computationally reproduced (20 out of 36, or 56%) was relatively high compared to other studies, there is clear room for improvement.
+Of the main results from 62 articles that met our inclusion criteria, data was available for 41 articles, and analysis scripts for 37 articles.
+For the main results in 36 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 analyses, and reproduce the main results for 20 articles.
+Although the articles that shared both data and code (36 out of 62, or 58%) and articles for which main results could be computationally reproduced (21 out of 36, or 58%) was relatively high compared to other studies, there is clear room for improvement.
 We provide practical recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.
@@
 Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the articles.
-@hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal *Cognition*.
-Eleven articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance.
+@hardwicke_data_2018 examined the analytic reproducibility of 35 articles published in the journal *Cognition*.
+Target outcomes that supported the identified substantive finding of eleven articles could be reproduced by independently writing analysis code, without assistance from the original authors, and 13 sets of target outcomes contained at least one outcome that could not be reproduced even with author assistance.
 The authors estimated that it took between 2-25 hours to reproduce the reported results per article, but they did not record the exact time.
@@
 The novelty of Registered Reports may attract early adopters who are also exploring other novel developments aimed at improving research practices in psychology, such as data and code sharing.
-We hypothesized that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
-In line with our hypothesis, `r sum(all_data$availability, na.rm = TRUE)` out of `r length(all_data$doi)` articles in our final dataset shared at least some of the data and code (`r sprintf("%.1f", round(100*sum(all_data$availability, na.rm = TRUE)/length(all_data$doi),1))`%).
-In comparison, after the journal *Cognition* introduced a mandatory data sharing policy, 136 out of 174 articles (78.2%) had a data availability statement, 85 of 174 articles (49.0%) had reusable data, and only 18 out of 174 articles (10.3%) provided the analysis code (Hardwicke et al., 2018).
+In addition, one journal that publishes Registered Reports (Royal Society Open Science) requires authors to deposit data and code, and several other journals that publish Registered Reports 'strongly encourage' data and/or code sharing.
+We therefore hypothesized that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
 To evaluate the reproducibility of findings published in Registered Reports, we examined if data could be located, were available at the indicated location, could be opened in open-source or accessible software, were documented well enough to be understandable, and could be used to reproduce the main analyses reported in the published manuscript.
@@
 Our main objective was to examine how reusable data and code underlying Registered Reports are, based solely on the information provided in those articles.
-We examined how many authors voluntarily shared data and code, and the extent to which we could reproduce reported analyses without contacting the original authors.
+We examined how many authors shared data and code without our solicitation, and the extent to which we could reproduce reported analyses without contacting the original authors.
 While reproducing the results reported in Registered Reports, we kept track of factors that facilitated reproducibility or that made reproducing results more difficult.
@@
 
-All data and the code used to create this manuscript is provided in an OSF repository at https://osf.io/suqz3/.
+All data and the code used to create this manuscript is provided in an OSF repository at https://osf.io/suqz3/. We report all measured variables and conducted analyses.
 
@@
 For one paper the data was linked but not available, as the data was embargoed until a future date.
-Altogether, some data or code was available for `r sum(all_data$availability)` of `r length(all_data$doi)` papers.
+
+In line with our predictions that authors of Registered Reports would be relatively likely to also adopt other open science practices, such as data and code sharing, `r sum(all_data$availability, na.rm = TRUE)` out of `r length(all_data$doi)` articles in our final dataset shared at least some of the data and code (`r sprintf("%.1f", round(100*sum(all_data$availability, na.rm = TRUE)/length(all_data$doi),1))`%).
+In comparison, after the journal *Cognition* introduced a mandatory data sharing policy, 136 out of 174 articles (78.2%) had a data availability statement, 85 of 174 articles (49.0%) had reusable data, and only 18 out of 174 articles (10.3%) provided the analysis code (Hardwicke et al., 2018).
 For `r sum(all_data$analysis_script_included == TRUE, na.rm = TRUE)` articles, the available code contained the statistical analyses, and for `r sum(all_data$data_complete == TRUE, na.rm = TRUE)`, all the required data files were available to reproduce the reported results (for `r sum(all_data$data_complete == TRUE & all_data$analysis_script_included == TRUE, na.rm = TRUE)` articles both data and code were available).
@@
 Code often needed minor adjustments to run on the data, such as changing file locations, or loading packages in R, and coders sometimes took different approaches to how much they would adjust the code to make it run on the data (for detailed comments, see our data file).
-Furthermore, coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article.
+When judging if the code ran on the data, we allowed for minor errors, but categorized code as not running when it was unclear how analysis code related to data files, or when there were a substantial number of errors when attempting to run all the code, even after attempts to make minor corrections.
+Furthermore, we did not preregister this study, and had no clearly defined coding scheme based on pilot data, and as a consequence coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article.
 After evaluating our initial coding round, we considered an article reproducible when we could get the same *main results* as represented in the paper with at best *minor changes* to the analysis scripts.
-This means we considered the analysis reproducible, even if in absence of a codebook coders had to search through the analysis code and dataset to identify how variable and label names related to the results reported in the paper.
+This means we considered the analysis reproducible, even if in the absence of a codebook coders had to search through the analysis code and dataset to identify how variable and label names related to the results reported in the paper.
 Furthermore, we changed folder locations when needed, and installed and/or loaded required libraries.
@@
 Approximately half of the Registered Reports consisted of replication studies, where the main analysis was explicitly stated based on a previous study.
-In the remaining Registered Reports the main research question was often stated clearly in a 'confirmatory analyses' section, and were the analyses the sample size justification was based on.
+In the remaining Registered Reports the main research question was often stated clearly in a 'confirmatory analyses' section.
 Nevertheless, some arbitrary judgments were required when deciding which analyses were part of the main results.
@@
 The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve).
-(It may bear repeating that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.)
+It may bear repeating that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make their work more reproducible.
 
-For each article, two coders examined whether the code could be run on the data.
+For each article, two coders examined whether the code could be run on the data, and for five articles where some uncertainty remained, a third coder attempted to reproduce the results.
 Of the original `r length(all_data$doi)` articles, the analysis code and data were available for `r sum(all_data$analysis_script_included ==TRUE & all_data$data_complete == TRUE, na.rm = TRUE)` articles.
@@
 
+For the `r sum(all_data$analysis_script_included ==TRUE & all_data$data_complete == TRUE, na.rm = TRUE) - sum(all_data$reproducible_final, na.rm = TRUE)` articles that could not be reproduced, the main reasons were that 1) code to reproduce some values was missing (e.g., dedicated code to run the a macro in SPSS), which occurred `r sum(all_data$main_reason_not_reproducible == "code missing", na.rm = TRUE)` times, 2) code gave errors (e.g., because variables in the dataset were missing, or because functions did not run as expected), which occurred `r sum(all_data$main_reason_not_reproducible == "code errors", na.rm = TRUE)` times, and 3) in one case the code might have been reproducible, but the code was so complex that after 40 minutes only a small part of the results could be reproduced, and it was judged that the time needed to reproduce the results fell outside of a reasonable time span.
+Two small errors were observed (one value of 0.89 was rounded to 0.88, and probable type where a value of 0.06 should have been 0.03) but since dozens of other values in these articles reproduced perfectly, these errors were not considered severe enough to deem the main results not computationally reproducible.
+
 After the data and code had been downloaded, and the reported results were identified by looking through the article, the average time to reproduce analyses reported in R was `r round(mean(time_r_po, na.rm = TRUE),2)` minutes for the first coder (SD = `r round(sd(time_r_po, na.rm = TRUE),2)`) and `r round(mean(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)` minutes (SD =  `r round(sd(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)`) for the second coder.
@@
 In total, `r sum(all_data$analysis_script_included ==TRUE & all_data$data_complete == TRUE, na.rm = TRUE)` out of `r length(all_data$doi)` (or `r round(100*sum(all_data$analysis_script_included ==TRUE & all_data$data_complete == TRUE, na.rm = TRUE)/length(all_data$doi),1)`%) of the articles shared the underlying data and the code that was used to generate the results.
-Authors of Registered Reports in psychology seem to voluntarily choose to share data and code relatively often compared to authors of articles in political science [@stockemer_data_2018].
-Compared to authors of non-registered reports in psychology, voluntary data and code sharing is also relatively high, as is the reproducibility rate (taking into account that we reproduced articles without contacting the original authors).
+Authors of Registered Reports in psychology seem to share data and code relatively often compared to authors of articles in political science [@stockemer_data_2018].
+Compared to authors of non-registered reports in psychology, data and code sharing is also relatively high, as is the reproducibility rate (taking into account that we reproduced articles without contacting the original authors).
 The reproducibility rate was higher than the 31% rate observed by Hardwicke et al.
-(2018), and both voluntary data sharing as reproducibility were higher than in the sample of papers from the journal *Science* in 2011-2012 analyzed in @stodden_empirical_2018.
+(2018), and both data sharing as reproducibility were higher than in the sample of papers from the journal *Science* in 2011-2012 analyzed in @stodden_empirical_2018.
 
@@
 This is slightly shorter than the time it took Hardwicke and colleagues (2018), who estimated (without keeping track of the time explicitly) that reproducibility reports took between 2 and 25 person-hours, depending on whether the paper eventually fell in the reproducible or not-reproducible category, and whether author assistance was needed.
-One major difference between our approaches is that we did not write 'reproducibility reports' for each article.
+One major difference between our approaches is that we did not write our own code to analyze the data, as Hardwicke and colleagues did, but simply ran the code written by the original authors on the shared data.
+We also did not create 'reproducibility reports' for each article.
 Documenting the process of reproducing a paper adds transparency and allows others to check the the decisions about every value in an article.
@@
 
-In addition to novel technologies, most progress can probably be made by developing standards within research communities, and educating researchers about best practices that guarantee reproducibility.
+In addition to novel technologies, most progress can probably be made by developing standards within research communities, and educating researchers about best practices that guarantee reproducibility (for recent examples, see [@klein_practical_2018-1; liu_successes_2019].
 Most researchers are not trained in reproducible data analysis, and cannot be expected to invent best practices from scratch.

### 2020-01-13 manuscript_version_2/reproducing_registered_reports.tex
first draft revision

@@
 We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the psychological literature between 2014 and 2018.
-Of the 62 articles that met our inclusion criteria, data was available for 41 articles, and analysis scripts for 37 articles.
-For the 36 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 articles, and reproduce the main results for 20 articles.
-Although the articles that shared both data and code (36 out of 62, or 58\%) and articles that could be computationally reproduced (20 out of 36, or 56\%) was relatively high compared to other studies, there is clear room for improvement.
+Of the main results from 62 articles that met our inclusion criteria, data was available for 41 articles, and analysis scripts for 37 articles.
+For the main results in 36 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 analyses, and reproduce the main results for 20 articles.
+Although the articles that shared both data and code (36 out of 62, or 58\%) and articles for which main results could be computationally reproduced (21 out of 36, or 58\%) was relatively high compared to other studies, there is clear room for improvement.
 We provide practical recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.
@@
 Hardwicke et al.
-(2018) examined the reproducibility of 35 articles published in the journal \emph{Cognition}.
-Eleven articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance.
+(2018) examined the analytic reproducibility of 35 articles published in the journal \emph{Cognition}.
+Target outcomes that supported the identified substantive finding of eleven articles could be reproduced by independently writing analysis code, without assistance from the original authors, and 13 sets of target outcomes contained at least one outcome that could not be reproduced even with author assistance.
 The authors estimated that it took between 2-25 hours to reproduce the reported results per article, but they did not record the exact time.
@@
 The novelty of Registered Reports may attract early adopters who are also exploring other novel developments aimed at improving research practices in psychology, such as data and code sharing.
-We hypothesized that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
-In line with our hypothesis, 43 out of 62 articles in our final dataset shared at least some of the data and code (69.4\%).
-In comparison, after the journal \emph{Cognition} introduced a mandatory data sharing policy, 136 out of 174 articles (78.2\%) had a data availability statement, 85 of 174 articles (49.0\%) had reusable data, and only 18 out of 174 articles (10.3\%) provided the analysis code (Hardwicke et al., 2018).
+In addition, one journal that publishes Registered Reports (Royal Society Open Science) requires authors to deposit data and code, and several other journals that publish Registered Reports \enquote{strongly encourage} data and/or code sharing.
+We therefore hypothesized that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
 To evaluate the reproducibility of findings published in Registered Reports, we examined if data could be located, were available at the indicated location, could be opened in open-source or accessible software, were documented well enough to be understandable, and could be used to reproduce the main analyses reported in the published manuscript.
@@
 
-All data and the code used to create this manuscript is provided in an OSF repository at \url{https://osf.io/suqz3/}.
+All data and the code used to create this manuscript is provided in an OSF repository at \url{https://osf.io/suqz3/}. We report all measured variables and conducted analyses.
 
@@
 Seventy-nine articles in this database were published in the psychological literature.
-We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports (Hagger et al., 2016) and Many Labs projects (Klein et al., 2014, 2018).
+We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports (Hagger et al., 2016) and Many Labs projects (Klein et al., 2014; R.
+A.
+Klein et al., 2018).
 Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports.
@@
 For one paper the data was linked but not available, as the data was embargoed until a future date.
-Altogether, some data or code was available for 43 of 62 papers.
+
+In line with our predictions that authors of Registered Reports would be relatively likely to also adopt other open science practices, such as data and code sharing, 43 out of 62 articles in our final dataset shared at least some of the data and code (69.4\%).
+In comparison, after the journal \emph{Cognition} introduced a mandatory data sharing policy, 136 out of 174 articles (78.2\%) had a data availability statement, 85 of 174 articles (49.0\%) had reusable data, and only 18 out of 174 articles (10.3\%) provided the analysis code (Hardwicke et al., 2018).
 For 37 articles, the available code contained the statistical analyses, and for 41, all the required data files were available to reproduce the reported results (for 36 articles both data and code were available).
@@
 The analysis script could be run for 31 articles.
-For the 36 articles for which data and code were available, the main results could be reproduced for 20.
+For the 36 articles for which data and code were available, the main results could be reproduced for 21.
 }
@@
 Code often needed minor adjustments to run on the data, such as changing file locations, or loading packages in R, and coders sometimes took different approaches to how much they would adjust the code to make it run on the data (for detailed comments, see our data file).
-Furthermore, coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article.
+When judging if the code ran on the data, we allowed for minor errors, but categorized code as not running when it was unclear how analysis code related to data files, or when there were a substantial number of errors when attempting to run all the code, even after attempts to make minor corrections.
+Furthermore, we did not preregister this study, and had no clearly defined coding scheme based on pilot data, and as a consequence coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article.
 After evaluating our initial coding round, we considered an article reproducible when we could get the same \emph{main results} as represented in the paper with at best \emph{minor changes} to the analysis scripts.
-This means we considered the analysis reproducible, even if in absence of a codebook coders had to search through the analysis code and dataset to identify how variable and label names related to the results reported in the paper.
+This means we considered the analysis reproducible, even if in the absence of a codebook coders had to search through the analysis code and dataset to identify how variable and label names related to the results reported in the paper.
 Furthermore, we changed folder locations when needed, and installed and/or loaded required libraries.
@@
 Approximately half of the Registered Reports consisted of replication studies, where the main analysis was explicitly stated based on a previous study.
-In the remaining Registered Reports the main research question was often stated clearly in a \enquote{confirmatory analyses} section, and were the analyses the sample size justification was based on.
+In the remaining Registered Reports the main research question was often stated clearly in a \enquote{confirmatory analyses} section.
 Nevertheless, some arbitrary judgments were required when deciding which analyses were part of the main results.
@@
 The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve).
-(It may bear repeating that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.)
+It may bear repeating that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make their work more reproducible.
 
-For each article, two coders examined whether the code could be run on the data.
+For each article, two coders examined whether the code could be run on the data, and for five articles where some uncertainty remained, a third coder attempted to reproduce the results.
 Of the original 62 articles, the analysis code and data were available for 36 articles.
@@
 Some analyses in a paper might not be part of the code or the output.
-We found that 20 out of 36 papers (55.60\%) that included their data and code could be used to reproduce the main results in the article.
+We found that 21 out of 36 papers (58.30\%) that included their data and code could be used to reproduce the main results in the article.
+
+For the 15 articles that could not be reproduced, the main reasons were that 1) code to reproduce some values was missing (e.g., dedicated code to run the a macro in SPSS), which occurred 8 times, 2) code gave errors (e.g., because variables in the dataset were missing, or because functions did not run as expected), which occurred 6 times, and 3) in one case the code might have been reproducible, but the code was so complex that after 40 minutes only a small part of the results could be reproduced, and it was judged that the time needed to reproduce the results fell outside of a reasonable time span.
+Two small errors were observed (one value of 0.89 was rounded to 0.88, and probable type where a value of 0.06 should have been 0.03) but since dozens of other values in these articles reproduced perfectly, these errors were not considered severe enough to deem the main results not computationally reproducible.
 
@@
 In total, 36 out of 62 (or 58.10\%) of the articles shared the underlying data and the code that was used to generate the results.
-Authors of Registered Reports in psychology seem to voluntarily choose to share data and code relatively often compared to authors of articles in political science (Stockemer et al., 2018).
-Compared to authors of non-registered reports in psychology, voluntary data and code sharing is also relatively high, as is the reproducibility rate (taking into account that we reproduced articles without contacting the original authors).
-The reproducibility rate was higher than the 31\% rate observed by Hardwicke et al.~(2018), and both voluntary data sharing as reproducibility were higher than in the sample of papers from the journal \emph{Science} in 2011-2012 analyzed in Stodden et al.
+Authors of Registered Reports in psychology seem to share data and code relatively often compared to authors of articles in political science (Stockemer et al., 2018).
+Compared to authors of non-registered reports in psychology, data and code sharing is also relatively high, as is the reproducibility rate (taking into account that we reproduced articles without contacting the original authors).
+The reproducibility rate was higher than the 31\% rate observed by Hardwicke et al.~(2018), and both data sharing as reproducibility were higher than in the sample of papers from the journal \emph{Science} in 2011-2012 analyzed in Stodden et al.
 (2018).
@@
 It provides a code environment (or container) that runs online, which means that researchers using Code Ocean do not have to download data, code, or software, but can analyze the data in their browser.
-It is not currently possible to use SPSS within Code Ocean, but for R code, it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.\footnote{For a Code Ocean capsule reproducing this manuscript, see \url{https://doi.org/10.24433/CO.4275368.v1}} Other platforms in the reproducibility space include Whole Tale (Brinckman et al., 2019), \enquote{a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage} (p.~855); and Binder (Ragan-Kelley \& Willing, 2018), an open-source, browser-based tool for creating and sharing reproducible environments.
+It is not currently possible to use SPSS within Code Ocean, but for R code, it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.\footnote{For a Code Ocean capsule reproducing this manuscript, see \url{https://doi.org/10.24433/CO.4275368.v1}} Other platforms in the reproducibility space include Whole Tale ({\textbf{???}}), \enquote{a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage} (p.~855); and Binder ({\textbf{???}}), an open-source, browser-based tool for creating and sharing reproducible environments.
 Another useful technology is RMarkdown, which enable researchers to write fully executable manuscripts.
@@
 This is slightly shorter than the time it took Hardwicke and colleagues (2018), who estimated (without keeping track of the time explicitly) that reproducibility reports took between 2 and 25 person-hours, depending on whether the paper eventually fell in the reproducible or not-reproducible category, and whether author assistance was needed.
-One major difference between our approaches is that we did not write \enquote{reproducibility reports} for each article.
+One major difference between our approaches is that we did not write our own code to analyze the data, as Hardwicke and colleagues did, but simply ran the code written by the original authors on the shared data.
+We also did not create \enquote{reproducibility reports} for each article.
 Documenting the process of reproducing a paper adds transparency and allows others to check the the decisions about every value in an article.
@@
 
-In addition to novel technologies, most progress can probably be made by developing standards within research communities, and educating researchers about best practices that guarantee reproducibility.
+In addition to novel technologies, most progress can probably be made by developing standards within research communities, and educating researchers about best practices that guarantee reproducibility (for recent examples, see {[}O.
+Klein et al.
+(2018); liu\_successes\_2019{]}.
 Most researchers are not trained in reproducible data analysis, and cannot be expected to invent best practices from scratch.
@@
 doi:\href{https://doi.org/10.1177/2515245919838783}{10.1177/2515245919838783}
-
-\leavevmode\hypertarget{ref-brinckman_computing_2019}{}%
-Brinckman, A., Chard, K., Gaffney, N., Hategan, M., Jones, M.
-B., Kowalik, K., \ldots{} Turner, K.
-(2019).
-Computing environments for reproducibility: Capturing the ``Whole Tale''.
-\emph{Future Generation Computer Systems}, \emph{94}, 854--867.
-doi:\href{https://doi.org/10.1016/j.future.2017.12.029}{10.1016/j.future.2017.12.029}
 
@@
 
+\leavevmode\hypertarget{ref-klein_practical_2018-1}{}%
+Klein, O., Hardwicke, T.
+E., Aust, F., Breuer, J., Danielsson, H., Mohr, A.
+H., \ldots{} Frank, M.
+C.
+(2018).
+A Practical Guide for Transparency in Psychological Science.
+\emph{Collabra: Psychology}, \emph{4}(1), 20.
+doi:\href{https://doi.org/10.1525/collabra.158}{10.1525/collabra.158}
+
 \leavevmode\hypertarget{ref-klein_investigating_2014}{}%
@@
 Nosek, B. A., \& Lakens, D. (2014). Registered Reports. \emph{Social Psychology}, \emph{45}(3), 137--141. doi:\href{https://doi.org/10.1027/1864-9335/a000192}{10.1027/1864-9335/a000192}
-
-\leavevmode\hypertarget{ref-ragan2018binder}{}%
-Ragan-Kelley, B., \& Willing, C. (2018). Binder 2.0-reproducible, interactive, sharable environments for science at scale.
 
@@
 
-\leavevmode\hypertarget{ref-brinckman_computing_2019}{}%
-Brinckman, A., Chard, K., Gaffney, N., Hategan, M., Jones, M.
-B., Kowalik, K., \ldots{} Turner, K.
-(2019).
-Computing environments for reproducibility: Capturing the ``Whole Tale''.
-\emph{Future Generation Computer Systems}, \emph{94}, 854--867.
-doi:\href{https://doi.org/10.1016/j.future.2017.12.029}{10.1016/j.future.2017.12.029}
-
 \leavevmode\hypertarget{ref-campbell_self-esteem_2018}{}%

### 2020-01-13 manuscript_version_2/reproducing_registered_reports.tex
update refs data

@@
 It provides a code environment (or container) that runs online, which means that researchers using Code Ocean do not have to download data, code, or software, but can analyze the data in their browser.
-It is not currently possible to use SPSS within Code Ocean, but for R code, it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.\footnote{For a Code Ocean capsule reproducing this manuscript, see \url{https://doi.org/10.24433/CO.4275368.v1}} Other platforms in the reproducibility space include Whole Tale ({\textbf{???}}), \enquote{a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage} (p.~855); and Binder ({\textbf{???}}), an open-source, browser-based tool for creating and sharing reproducible environments.
+It is not currently possible to use SPSS within Code Ocean, but for R code, it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.\footnote{For a Code Ocean capsule reproducing this manuscript, see \url{https://doi.org/10.24433/CO.4275368.v1}} Other platforms in the reproducibility space include Whole Tale ({\textbf{???}}), \enquote{a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage} (p.~855); and Binder (Ragan-Kelley \& Willing, 2018), an open-source, browser-based tool for creating and sharing reproducible environments.
 Another useful technology is RMarkdown, which enable researchers to write fully executable manuscripts.
@@
 Nosek, B. A., \& Lakens, D. (2014). Registered Reports. \emph{Social Psychology}, \emph{45}(3), 137--141. doi:\href{https://doi.org/10.1027/1864-9335/a000192}{10.1027/1864-9335/a000192}
+
+\leavevmode\hypertarget{ref-ragan2018binder}{}%
+Ragan-Kelley, B., \& Willing, C. (2018). Binder 2.0-reproducible, interactive, sharable environments for science at scale.
 

### 2020-01-13 manuscript_version_2/reproducing_registered_reports.Rmd
fix references

@@
 It provides a code environment (or container) that runs online, which means that researchers using Code Ocean do not have to download data, code, or software, but can analyze the data in their browser.
-It is not currently possible to use SPSS within Code Ocean, but for R code, it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.^[For a Code Ocean capsule reproducing this manuscript, see https://doi.org/10.24433/CO.4275368.v1] Other platforms in the reproducibility space include Whole Tale [@brinckman_computing_2019], "a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage" (p.
+It is not currently possible to use SPSS within Code Ocean, but for R code, it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.^[For a Code Ocean capsule reproducing this manuscript, see https://doi.org/10.24433/CO.4275368.v1] Other platforms in the reproducibility space include Whole Tale [@brinckman2019computing], "a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage" (p.
 855); and Binder [@ragan2018binder], an open-source, browser-based tool for creating and sharing reproducible environments.

### 2020-01-13 manuscript_version_2/reproducing_registered_reports.tex
fix references

@@
 The availability of analysis code makes it possible for peers to check and correct published findings.
-According to Kitzes, Turek, \& Deniz (2017), computational reproducibility means that ''a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.'' For scientific research to be computationally reproducible, the data and code need to be shared.
+According to Kitzes, Turek, and Deniz (2017), computational reproducibility means that ''a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.'' For scientific research to be computationally reproducible, the data and code need to be shared.
 
@@
 The authors estimated that it took between 2-25 hours to reproduce the reported results per article, but they did not record the exact time.
-Stockemer, Koehler, \& Lentz (2018) analyzed reproducibility in all articles published in 2015 in three political science journals.
+Stockemer, Koehler, and Lentz (2018) analyzed reproducibility in all articles published in 2015 in three political science journals.
 They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one paper's results could not be reproduced due to a lack of a software license, and 16 articles' findings could not be reproduced with access to the required software.
 For the remaining articles, 32 sets of results could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results.
-Stodden, Seiler, \& Ma (2018) analyzed data availability in the journal \emph{Science} in 2011-2012 and found that 26 of 204 (or 13\%) of articles provided information to retrieve data and/or code without contacting the authors.
+Stodden, Seiler, and Ma (2018) analyzed data availability in the journal \emph{Science} in 2011-2012 and found that 26 of 204 (or 13\%) of articles provided information to retrieve data and/or code without contacting the authors.
 For all datasets they acquired after e-mailing authors for data and code, 26\% were estimated to be computationally reproducible.
@@
 Well-annotated code makes clear what the analysis code does, in which order scripts should be run if there are multiple scripts (e.g., to pre-process the raw data, compute sum scores, analyze the results, and generate graphs), and which output each section of analysis code generates.
-A good example of well-annotated code can be found in the materials of Weston \& Jackson (2018).
+A good example of well-annotated code can be found in the materials of Weston and Jackson (2018).
 It helps to make clear how the analysis code relates to the analyses reported in the paper, to make it easier for others to identify which code generates which results in the paper.
@@
 Explicitly linking code in the analysis script to the final manuscript also helps researchers to check whether all results in the article are reproduced by the shared code.
-An example of a data analysis file that clearly links the code to the final articles can be found in the materials of Voorspoels, Bartlema, \& Vanpaemel (2014).
+An example of a data analysis file that clearly links the code to the final articles can be found in the materials of Voorspoels, Bartlema, and Vanpaemel (2014).
 If analyses are performed that are not included in the manuscript, this should be stated explicitly (e.g., assumption checks, exploratory analyses, etc.).
@@
 It provides a code environment (or container) that runs online, which means that researchers using Code Ocean do not have to download data, code, or software, but can analyze the data in their browser.
-It is not currently possible to use SPSS within Code Ocean, but for R code, it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.\footnote{For a Code Ocean capsule reproducing this manuscript, see \url{https://doi.org/10.24433/CO.4275368.v1}} Other platforms in the reproducibility space include Whole Tale ({\textbf{???}}), \enquote{a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage} (p.~855); and Binder (Ragan-Kelley \& Willing, 2018), an open-source, browser-based tool for creating and sharing reproducible environments.
+It is not currently possible to use SPSS within Code Ocean, but for R code, it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.\footnote{For a Code Ocean capsule reproducing this manuscript, see \url{https://doi.org/10.24433/CO.4275368.v1}} Other platforms in the reproducibility space include Whole Tale (Brinckman et al., 2019), \enquote{a research environment that captures and, at the time of publication, exposes salient details of the entire research process via access to persistent versions of the data and code used, provenance, and data lineage} (p.~855); and Binder (Ragan-Kelley \& Willing, 2018), an open-source, browser-based tool for creating and sharing reproducible environments.
 Another useful technology is RMarkdown, which enable researchers to write fully executable manuscripts.
@@
 
-\leavevmode\hypertarget{ref-campbell_self-esteem_2018}{}%
-Campbell, L., Balzarini, R.
-N., Kohut, T., Dobson, K., Hahn, C.
-M., Moroz, S.
-E., \& Stanton, S.
-C.
-E.
-(2018).
-Self-esteem, relationship threat, and dependency regulation: Independent replication of Murray, Rose, Bellavia, Holmes, and Kusche (2002) Study 3.
-\emph{Journal of Research in Personality}, \emph{72}, 5--9.
-doi:\href{https://doi.org/10.1016/j.jrp.2017.04.001}{10.1016/j.jrp.2017.04.001}
-
-\leavevmode\hypertarget{ref-chambers_instead_2014}{}%
-Chambers, C.
-D., Feredoes, E., Muthukumaraswamy, S.
-D., \& Etchells, P.
-(2014).
-Instead of "playing the game" it is time to change the rules: Registered Reports at AIMS Neuroscience and beyond.
-\emph{AIMS Neuroscience}, \emph{1}, 4--17.
-doi:\href{https://doi.org/10.3934/Neuroscience2014.1.4}{10.3934/Neuroscience2014.1.4}
-
-\leavevmode\hypertarget{ref-clyburne-sherin_computational_2018}{}%
-Clyburne-Sherin, A., Fei, X., \& Green, S. A. (2018). Computational Reproducibility via Containers in Social Psychology. doi:\href{https://doi.org/10.31234/osf.io/mf82t}{10.31234/osf.io/mf82t}
-
-\leavevmode\hypertarget{ref-gertler_reference_2017}{}%
-Gertler, A.
-L., \& Bullock, J.
-G.
-(2017).
-Reference Rot: An Emerging Threat to Transparency in Political Science.
-\emph{PS: Political Science \& Politics}, \emph{50}(1), 166--171.
-doi:\href{https://doi.org/10.1017/S1049096516002353}{10.1017/S1049096516002353}
-
-\leavevmode\hypertarget{ref-hagger_multilab_2016}{}%
-Hagger, M.
-S., Chatzisarantis, N.
-L.
-D., Alberts, H., Anggono, C.
-O., Batailler, C., Birt, A.
-R., \ldots{} Zwienenberg, M.
-(2016).
-A Multilab Preregistered Replication of the Ego-Depletion Effect.
-\emph{Perspectives on Psychological Science}, \emph{11}(4), 546--573.
-doi:\href{https://doi.org/10.1177/1745691616652873}{10.1177/1745691616652873}
-
-\leavevmode\hypertarget{ref-hardwicke_data_2018}{}%
-Hardwicke, T.
-E., Mathur, M.
-B., MacDonald, K., Nilsonne, G., Banks, G.
-C., Kidwell, M.
-C., \ldots{} Frank, M.
-C.
-(2018).
-Data availability, reusability, and analytic reproducibility: Evaluating the impact of a mandatory open data policy at the journal Cognition.
-\emph{Open Science}, \emph{5}(8), 180448.
-doi:\href{https://doi.org/10.1098/rsos.180448}{10.1098/rsos.180448}
-
-\leavevmode\hypertarget{ref-kitzes_practice_2017}{}%
-Kitzes, J., Turek, D., \& Deniz, F. (2017). \emph{The Practice of Reproducible Research: Case Studies and Lessons from the Data-Intensive Sciences}. Univ of California Press.
-
-\leavevmode\hypertarget{ref-klein_practical_2018-1}{}%
-Klein, O., Hardwicke, T.
-E., Aust, F., Breuer, J., Danielsson, H., Mohr, A.
-H., \ldots{} Frank, M.
-C.
-(2018).
-A Practical Guide for Transparency in Psychological Science.
-\emph{Collabra: Psychology}, \emph{4}(1), 20.
-doi:\href{https://doi.org/10.1525/collabra.158}{10.1525/collabra.158}
-
-\leavevmode\hypertarget{ref-klein_investigating_2014}{}%
-Klein, R.
-A., Ratliff, K.
-A., Vianello, M., Adams, R.
-B., Bahník, Š., Bernstein, M.
-J., \ldots{} Nosek, B.
-A.
-(2014).
-Investigating Variation in Replicability.
-\emph{Social Psychology}, \emph{45}(3), 142--152.
-doi:\href{https://doi.org/10.1027/1864-9335/a000178}{10.1027/1864-9335/a000178}
-
-\leavevmode\hypertarget{ref-klein_many_2018}{}%
-Klein, R.
-A., Vianello, M., Hasselman, F., Adams, B.
-G., Adams, R.
-B., Alper, S., \ldots{} Nosek, B.
-A.
-(2018).
-Many Labs 2: Investigating Variation in Replicability Across Samples and Settings.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 443--490.
-doi:\href{https://doi.org/10.1177/2515245918810225}{10.1177/2515245918810225}
-
-\leavevmode\hypertarget{ref-le_open_2018}{}%
-Le, B. (2018, May). Open Science Manual. https://bit.ly/2w2F6Xu.
-
-\leavevmode\hypertarget{ref-morey_peer_2016}{}%
-Morey, R.
-D., Chambers, C.
-D., Etchells, P.
-J., Harris, C.
-R., Hoekstra, R., Lakens, D., \ldots{} others.
-(2016).
-The Peer Reviewers' Openness Initiative: Incentivizing open research practices through peer review.
-\emph{Royal Society Open Science}, \emph{3}(1), 150547.
-
-\leavevmode\hypertarget{ref-nosek_registered_2014}{}%
-Nosek, B. A., \& Lakens, D. (2014). Registered Reports. \emph{Social Psychology}, \emph{45}(3), 137--141. doi:\href{https://doi.org/10.1027/1864-9335/a000192}{10.1027/1864-9335/a000192}
-
-\leavevmode\hypertarget{ref-ragan2018binder}{}%
-Ragan-Kelley, B., \& Willing, C. (2018). Binder 2.0-reproducible, interactive, sharable environments for science at scale.
-
-\leavevmode\hypertarget{ref-stockemer_data_2018}{}%
-Stockemer, D., Koehler, S., \& Lentz, T.
-(2018).
-Data Access, Transparency, and Replication: New Insights from the Political Behavior Literature.
-\emph{PS: Political Science \& Politics}, \emph{51}(4), 799--803.
-doi:\href{https://doi.org/10.1017/S1049096518000926}{10.1017/S1049096518000926}
-
-\leavevmode\hypertarget{ref-stodden_empirical_2018}{}%
-Stodden, V., Seiler, J., \& Ma, Z.
-(2018).
-An empirical analysis of journal policy effectiveness for computational reproducibility.
-\emph{Proceedings of the National Academy of Sciences}, \emph{115}(11), 2584--2589.
-doi:\href{https://doi.org/10.1073/pnas.1708290115}{10.1073/pnas.1708290115}
-
-\leavevmode\hypertarget{ref-voorspoels_can_2014}{}%
-Voorspoels, W., Bartlema, A., \& Vanpaemel, W.
-(2014).
-Can race really be erased?
-A pre-registered replication study.
-\emph{Frontiers in Psychology}, \emph{5}.
-doi:\href{https://doi.org/10.3389/fpsyg.2014.01035}{10.3389/fpsyg.2014.01035}
-
-\leavevmode\hypertarget{ref-wesselmann_revisiting_2014}{}%
-Wesselmann, E.
-D., Williams, K.
-D., Pryor, J.
-B., Eichler, F.
-A., Gill, D.
-M., \& Hogue, J.
-D.
-(2014).
-Revisiting Schachter's Research on Rejection, Deviance, and Communication (1951).
-\emph{Social Psychology}, \emph{45}(3), 164--169.
-doi:\href{https://doi.org/10.1027/1864-9335/a000180}{10.1027/1864-9335/a000180}
-
-\leavevmode\hypertarget{ref-weston_role_2018}{}%
-Weston, S.
-J., \& Jackson, J.
-J.
-(2018).
-The role of vigilance in the relationship between neuroticism and health: A registered report.
-\emph{Journal of Research in Personality}, \emph{73}, 27--34.
-doi:\href{https://doi.org/10.1016/j.jrp.2017.10.005}{10.1016/j.jrp.2017.10.005}
-
-\leavevmode\hypertarget{ref-wilkinson_fair_2016}{}%
-Wilkinson, M.
-D., Dumontier, M., Aalbersberg, I.
-J., Appleton, G., Axton, M., Baak, A., \ldots{} Mons, B.
-(2016).
-The FAIR Guiding Principles for scientific data management and stewardship.
-\emph{Scientific Data}, \emph{3}, 160018.
-doi:\href{https://doi.org/10.1038/sdata.2016.18}{10.1038/sdata.2016.18}
-
-\leavevmode\hypertarget{ref-arslan_how_2019}{}%
-Arslan, R.
-C.
+\leavevmode\hypertarget{ref-brinckman2019computing}{}%
+Brinckman, A., Chard, K., Gaffney, N., Hategan, M., Jones, M.
+B., Kowalik, K., \ldots{} others.
 (2019).
-How to Automatically Document Data With the codebook Package to Facilitate Data Reuse.
-\emph{Advances in Methods and Practices in Psychological Science}, 2515245919838783.
-doi:\href{https://doi.org/10.1177/2515245919838783}{10.1177/2515245919838783}
+Computing environments for reproducibility: Capturing the ``whole tale''.
+\emph{Future Generation Computer Systems}, \emph{94}, 854--867.
 

### 2020-01-23 manuscript_version_2/reproducing_registered_reports.Rmd
revision after co-author feedback

@@
 Sharing data and analysis code makes it easier for other researchers to re-use or check published research.
-These benefits will only emerge if researchers can reproduce the analysis reported in published articles, and if data is annotated well enough so that it is clear what all variables mean.
-Because most researchers have not been trained in computational reproducibility, it is important to evaluate current practices to identify practices that can be improved.
-We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the psychological literature between 2014 and 2018.
-Of the main results from 62 articles that met our inclusion criteria, data was available for 41 articles, and analysis scripts for 37 articles.
-For the main results in 36 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 analyses, and reproduce the main results for 20 articles.
+However, these benefits will only emerge if researchers can reproduce the analysis reported in published articles and if data is annotated well enough so that it is clear what all variables mean.
+Because most researchers are not trained in computational reproducibility, it is important to evaluate current practices to identify practices that can be improved.
+We examined data and code sharing for Registered Reports published in the psychological literature between 2014 and 2018, and attempted to independently computationally reproduce the main results in each article.
+Of the main results from 62 articles that met our inclusion criteria, data were available for 41 articles, and analysis scripts for 37 articles.
+For the main results in 36 articles that shared both data and code we could run the scripts for 31 analyses, and reproduce the main results for 20 articles.
 Although the articles that shared both data and code (36 out of 62, or 58%) and articles for which main results could be computationally reproduced (21 out of 36, or 58%) was relatively high compared to other studies, there is clear room for improvement.
-We provide practical recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.
+We provide practical recommendations based on our observations and link to examples of good research practices in the papers we reproduced.
 
@@
 Researchers are currently exploring ways to make science more open and transparent.
-Among novel developments such as pre-registration, preprints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., [@morey_peer_2016].
+Among novel developments such as pre-registration, preprints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., @morey_peer_2016).
 Sharing data and analysis code with scientific publications allows others to more easily reproduce, check, and build on existing work.
@@
 It is important to evaluate how data and code are currently being shared, and how easy it is to reproduce analyses reported in the published literature, to learn what can be improved.
-With this goal in mind, we computationally reproduced the main results of Registered Reports published in the psychological literature.
+With this goal in mind, we computationally reproduced the main results of Registered Reports published in the psychology literature.
 
@@
 
-Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the articles.
+Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analyses reported in the articles.
 @hardwicke_data_2018 examined the analytic reproducibility of 35 articles published in the journal *Cognition*.
@@
 @stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals.
-They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one paper's results could not be reproduced due to a lack of a software license, and 16 articles' findings could not be reproduced with access to the required software.
+They emailed authors for the code and data, which they received for 71 articles.
+The results of one article could not be reproduced due to a lack of a software license, and 16 articles' findings could not be reproduced with access to the required software.
 For the remaining articles, 32 sets of results could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results.
@@
 Our main interest was to examine the computational reproducibility of the main analyses reported in published articles, without contacting the original authors.
-One of the main benefits of sharing data and code alongside an article (compared to making these files available upon request) is that results can be reproduced, and data reused even if the original author can no longer be reached.
+One of the main benefits of sharing data and code alongside an article (compared to making these files available upon request) is that results can be reproduced and data reused even if the original author can no longer be reached.
 
@@
 The novelty of Registered Reports may attract early adopters who are also exploring other novel developments aimed at improving research practices in psychology, such as data and code sharing.
-In addition, one journal that publishes Registered Reports (Royal Society Open Science) requires authors to deposit data and code, and several other journals that publish Registered Reports 'strongly encourage' data and/or code sharing.
-We therefore hypothesized that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
+In addition, one journal that publishes Registered Reports (Royal Society Open Science) requires authors to deposit data and code, and several other journals that publish Registered Reports strongly encourage data and/or code sharing.
+We expected researchers who publish Registered Reports to be likely to share data and code in public repositories, and to embrace computational reproducibility.
 To evaluate the reproducibility of findings published in Registered Reports, we examined if data could be located, were available at the indicated location, could be opened in open-source or accessible software, were documented well enough to be understandable, and could be used to reproduce the main analyses reported in the published manuscript.
@@
 Our main objective was to examine how reusable data and code underlying Registered Reports are, based solely on the information provided in those articles.
-We examined how many authors shared data and code without our solicitation, and the extent to which we could reproduce reported analyses without contacting the original authors.
+We examined how many authors shared data and code without our solicitation and the extent to which we could reproduce reported analyses without contacting the original authors.
 While reproducing the results reported in Registered Reports, we kept track of factors that facilitated reproducibility or that made reproducing results more difficult.
@@
 To find Registered Reports published in psychology, we drew from a database of registered reports maintained by the Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
-Seventy-nine articles in this database were published in the psychological literature.
+Seventy-nine articles in this database were published in the psychology literature.
 We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018].
@@
 This left `r length(all_data$doi)` studies in our sample.
-When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of one additional study.
+When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we were not trained in (e.g., dedicated EEG software), which led to the exclusion of one additional study.
 
@@
 For each article, we coded whether the data and code were (a) linked, (b) available, (c) not software-specific, (d) understandable, and (e) reproducible.
-These five categories were inspired by FAIR data principles [@wilkinson_fair_2016] that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles.
-Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of metadata (which was missing for practically all datasets).
+These five categories were inspired by FAIR data principles that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles [@wilkinson_fair_2016].
+Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of metadata (which was missing for all datasets).
 We considered data and code to be linked when the manuscript included a unique link to the data and scripts.
@@
 For three articles, the link still worked, but there was no data at the linked destination.
-For three articles where there was no link to the data in the article, we were nevertheless able to find data on the Open Science Framework when searching for the title of the paper.
+For three articles where there was no link to the data in the article, but we were nevertheless able to find data on the Open Science Framework when searching for the title of the paper.
 For one paper the data was linked but not available, as the data was embargoed until a future date.
@@
 We also coded the extent to which data and code were specific to software that was not freely available.
-When open source software is used, the analyses can be reproduced by anyone with time, a computer and internet.
+When open-source software is used, the analyses can be reproduced by anyone with time, a computer and internet.
 When proprietary software is used, results might still be reproducible in principle, but could require more effort to do so.
@@
 However, .sav files can be opened in R, and .sps files can be opened by a text editor and the code can be rewritten, as long the code is annotated well enough to be recoded in R.
-Note that we had access to SPSS and therefore reproduced the analyses using the original .sps scripts where available.
+Note that we had access to SPSS and MATLAB and therefore reproduced the analyses using the original .sps scripts where available.
 When examining whether analyses were reproducible, we only used the same software packages as had been used by the original authors.
@@
 
-When coding whether the script could be executed and the results could be reproduced we resorted to a dichotomous classification ('yes' or 'no'), but coders often reported 'partial' reproducibility.
+When coding whether the script could be executed and the results could be reproduced we used a dichotomous classification ('yes' or 'no'), but coders often reported 'partial' reproducibility.
 Code often needed minor adjustments to run on the data, such as changing file locations, or loading packages in R, and coders sometimes took different approaches to how much they would adjust the code to make it run on the data (for detailed comments, see our data file).
 When judging if the code ran on the data, we allowed for minor errors, but categorized code as not running when it was unclear how analysis code related to data files, or when there were a substantial number of errors when attempting to run all the code, even after attempts to make minor corrections.
-Furthermore, we did not preregister this study, and had no clearly defined coding scheme based on pilot data, and as a consequence coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article.
+Furthermore, we did not preregister this study, and had no clearly defined coding scheme based on pilot data.
+As a consequence coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article.
 After evaluating our initial coding round, we considered an article reproducible when we could get the same *main results* as represented in the paper with at best *minor changes* to the analysis scripts.
@@
 Furthermore, we changed folder locations when needed, and installed and/or loaded required libraries.
-Finally, even though sometimes figures were generated in R and contained relevant information (e.g., the pattern of means) we did not require all figures to be reproducible.
+Finally, even though some figures were generated in R and contained relevant information (e.g., the pattern of means) we did not require all figures to be reproducible.
 For each study reported in the article we identified main results (i.e., any reported descriptives and statistical tests) based on the research question highlighted in the title and abstract.
@@
 For the current analysis, we considered a study reproducible as long as the more experienced coder could reproduce the main results.
-All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g.
+All authors collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g.
 overlooked script files).
@@
 
-For the `r sum(all_data$analysis_script_included ==TRUE & all_data$data_complete == TRUE, na.rm = TRUE) - sum(all_data$reproducible_final, na.rm = TRUE)` articles that could not be reproduced, the main reasons were that 1) code to reproduce some values was missing (e.g., dedicated code to run the a macro in SPSS), which occurred `r sum(all_data$main_reason_not_reproducible == "code missing", na.rm = TRUE)` times, 2) code gave errors (e.g., because variables in the dataset were missing, or because functions did not run as expected), which occurred `r sum(all_data$main_reason_not_reproducible == "code errors", na.rm = TRUE)` times, and 3) in one case the code might have been reproducible, but the code was so complex that after 40 minutes only a small part of the results could be reproduced, and it was judged that the time needed to reproduce the results fell outside of a reasonable time span.
-Two small errors were observed (one value of 0.89 was rounded to 0.88, and probable type where a value of 0.06 should have been 0.03) but since dozens of other values in these articles reproduced perfectly, these errors were not considered severe enough to deem the main results not computationally reproducible.
+For the `r sum(all_data$analysis_script_included ==TRUE & all_data$data_complete == TRUE, na.rm = TRUE) - sum(all_data$reproducible_final, na.rm = TRUE)` articles that could not be reproduced, the main reasons were that 1) code to reproduce some values was missing (e.g., dedicated code to run a macro in SPSS), which occurred `r sum(all_data$main_reason_not_reproducible == "code missing", na.rm = TRUE)` times, 2) code gave errors (e.g., because variables in the dataset were missing, or because functions did not run as expected), which occurred `r sum(all_data$main_reason_not_reproducible == "code errors", na.rm = TRUE)` times, and 3) in one case the code might have been reproducible, but the code was so complex that after 40 minutes only a small part of the results could be reproduced, and it was judged that the time needed to reproduce the results fell outside of a reasonable time span.
+In the articles that were coded as reproducible, two small errors were observed (one value of 0.89 was rounded to 0.88, and probable type where a value of 0.06 should have been 0.03) but since dozens of other values in these articles reproduced perfectly, these errors were not considered severe enough to deem the main results not computationally reproducible.
 
-After the data and code had been downloaded, and the reported results were identified by looking through the article, the average time to reproduce analyses reported in R was `r round(mean(time_r_po, na.rm = TRUE),2)` minutes for the first coder (SD = `r round(sd(time_r_po, na.rm = TRUE),2)`) and `r round(mean(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)` minutes (SD =  `r round(sd(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)`) for the second coder.
+After the data and code had been downloaded, and the reported results were identified by looking through the article, the average time to reproduce analyses reported in R was `r round(mean(time_r_po, na.rm = TRUE),2)` minutes (SD = `r round(sd(time_r_po, na.rm = TRUE),2)`) for the first coder and `r round(mean(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)` minutes (SD =  `r round(sd(as.numeric(all_data$time_reproducing_nc), na.rm = TRUE),2)`) for the second coder.
 Reproducing the SPSS analysis took on average `r round(mean(time_spss_po, na.rm = TRUE),2)` minutes (SD = `r round(sd(time_spss_po, na.rm = TRUE),2)`) for the first coder and  `r round(mean(as.numeric(all_data$time_reproducing_jg), na.rm = TRUE),2)` minutes (SD = `r round(sd(as.numeric(all_data$time_reproducing_jg), na.rm = TRUE),2)`) for the second coder.
@@
 
-Nevertheless, the reproducibility rate for articles where data and code were available show there is clear room for improvement in how reproducible published Registered Reports are, when we attempted to reproduce main analyses without contacting the authors.
+Nevertheless, our results indicate that that there is clear room for improvements in the computational reproducibility of Registered Reports.
 One of the main goals of our project was to identify ways to improve the reproducibility of published articles.
@@
 
-In addition to novel technologies, most progress can probably be made by developing standards within research communities, and educating researchers about best practices that guarantee reproducibility (for recent examples, see [@klein_practical_2018-1; liu_successes_2019].
+In addition to novel technologies, most progress can probably be made by developing standards within research communities, and educating researchers about best practices that guarantee reproducibility (for recent examples, see [@klein_practical_2018-1; @liu_successes_2019].
 Most researchers are not trained in reproducible data analysis, and cannot be expected to invent best practices from scratch.

### 2020-01-23 manuscript_version_2/reproducing_registered_reports.tex
revision after co-author feedback

@@
 Sharing data and analysis code makes it easier for other researchers to re-use or check published research.
-These benefits will only emerge if researchers can reproduce the analysis reported in published articles, and if data is annotated well enough so that it is clear what all variables mean.
-Because most researchers have not been trained in computational reproducibility, it is important to evaluate current practices to identify practices that can be improved.
-We examined data and code sharing, as well as computational reproducibility of the main results, without contacting the original authors, for Registered Reports published in the psychological literature between 2014 and 2018.
-Of the main results from 62 articles that met our inclusion criteria, data was available for 41 articles, and analysis scripts for 37 articles.
-For the main results in 36 articles that shared both data and code and performed analyses in SPSS, R, Python, MATLAB, or JASP, we could run the scripts for 31 analyses, and reproduce the main results for 20 articles.
+However, these benefits will only emerge if researchers can reproduce the analysis reported in published articles and if data is annotated well enough so that it is clear what all variables mean.
+Because most researchers are not trained in computational reproducibility, it is important to evaluate current practices to identify practices that can be improved.
+We examined data and code sharing for Registered Reports published in the psychological literature between 2014 and 2018, and attempted to independently computationally reproduce the main results in each article.
+Of the main results from 62 articles that met our inclusion criteria, data were available for 41 articles, and analysis scripts for 37 articles.
+For the main results in 36 articles that shared both data and code we could run the scripts for 31 analyses, and reproduce the main results for 20 articles.
 Although the articles that shared both data and code (36 out of 62, or 58\%) and articles for which main results could be computationally reproduced (21 out of 36, or 58\%) was relatively high compared to other studies, there is clear room for improvement.
-We provide practical recommendations based on our observations, and link to examples of good research practices in the papers we reproduced.
+We provide practical recommendations based on our observations and link to examples of good research practices in the papers we reproduced.
 
@@
 Researchers are currently exploring ways to make science more open and transparent.
-Among novel developments such as pre-registration, preprints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., (Morey et al., 2016).
+Among novel developments such as pre-registration, preprints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., Morey et al.
+(2016)).
 Sharing data and analysis code with scientific publications allows others to more easily reproduce, check, and build on existing work.
@@
 
-Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the articles.
+Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analyses reported in the articles.
 Hardwicke et al.
@@
 Stockemer, Koehler, and Lentz (2018) analyzed reproducibility in all articles published in 2015 in three political science journals.
-They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one paper's results could not be reproduced due to a lack of a software license, and 16 articles' findings could not be reproduced with access to the required software.
+They emailed authors for the code and data, which they received for 71 articles.
+The results of one article could not be reproduced due to a lack of a software license, and 16 articles' findings could not be reproduced with access to the required software.
 For the remaining articles, 32 sets of results could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results.
@@
 The novelty of Registered Reports may attract early adopters who are also exploring other novel developments aimed at improving research practices in psychology, such as data and code sharing.
-In addition, one journal that publishes Registered Reports (Royal Society Open Science) requires authors to deposit data and code, and several other journals that publish Registered Reports \enquote{strongly encourage} data and/or code sharing.
-We therefore hypothesized that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility.
+In addition, one journal that publishes Registered Reports (Royal Society Open Science) requires authors to deposit data and code, and several other journals that publish Registered Reports strongly encourage data and/or code sharing.
+We expected researchers who publish Registered Reports to be likely to share data and code in public repositories, and to embrace computational reproducibility.
 To evaluate the reproducibility of findings published in Registered Reports, we examined if data could be located, were available at the indicated location, could be opened in open-source or accessible software, were documented well enough to be understandable, and could be used to reproduce the main analyses reported in the published manuscript.
@@
 To find Registered Reports published in psychology, we drew from a database of registered reports maintained by the Center for Open Science.\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports.
-Seventy-nine articles in this database were published in the psychological literature.
+Seventy-nine articles in this database were published in the psychology literature.
 We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports (Hagger et al., 2016) and Many Labs projects (Klein et al., 2014; R.
@@
 This left 62 studies in our sample.
-When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of one additional study.
+When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we were not trained in (e.g., dedicated EEG software), which led to the exclusion of one additional study.
 
@@
 For each article, we coded whether the data and code were (a) linked, (b) available, (c) not software-specific, (d) understandable, and (e) reproducible.
-These five categories were inspired by FAIR data principles (Wilkinson et al., 2016) that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles.
-Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of metadata (which was missing for practically all datasets).
+These five categories were inspired by FAIR data principles that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles (Wilkinson et al., 2016).
+Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of metadata (which was missing for all datasets).
 We considered data and code to be linked when the manuscript included a unique link to the data and scripts.
@@
 
-When coding whether the script could be executed and the results could be reproduced we resorted to a dichotomous classification (\enquote{yes} or \enquote{no}), but coders often reported \enquote{partial} reproducibility.
+When coding whether the script could be executed and the results could be reproduced we used a dichotomous classification (\enquote{yes} or \enquote{no}), but coders often reported \enquote{partial} reproducibility.
 Code often needed minor adjustments to run on the data, such as changing file locations, or loading packages in R, and coders sometimes took different approaches to how much they would adjust the code to make it run on the data (for detailed comments, see our data file).
 When judging if the code ran on the data, we allowed for minor errors, but categorized code as not running when it was unclear how analysis code related to data files, or when there were a substantial number of errors when attempting to run all the code, even after attempts to make minor corrections.
-Furthermore, we did not preregister this study, and had no clearly defined coding scheme based on pilot data, and as a consequence coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article.
+Furthermore, we did not preregister this study, and had no clearly defined coding scheme based on pilot data.
+As a consequence coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article.
 After evaluating our initial coding round, we considered an article reproducible when we could get the same \emph{main results} as represented in the paper with at best \emph{minor changes} to the analysis scripts.
@@
 For the current analysis, we considered a study reproducible as long as the more experienced coder could reproduce the main results.
-All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g.~overlooked script files).
+All authors collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g.~overlooked script files).
 The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve).
@@
 
-For the 15 articles that could not be reproduced, the main reasons were that 1) code to reproduce some values was missing (e.g., dedicated code to run the a macro in SPSS), which occurred 8 times, 2) code gave errors (e.g., because variables in the dataset were missing, or because functions did not run as expected), which occurred 6 times, and 3) in one case the code might have been reproducible, but the code was so complex that after 40 minutes only a small part of the results could be reproduced, and it was judged that the time needed to reproduce the results fell outside of a reasonable time span.
-Two small errors were observed (one value of 0.89 was rounded to 0.88, and probable type where a value of 0.06 should have been 0.03) but since dozens of other values in these articles reproduced perfectly, these errors were not considered severe enough to deem the main results not computationally reproducible.
+For the 15 articles that could not be reproduced, the main reasons were that 1) code to reproduce some values was missing (e.g., dedicated code to run a macro in SPSS), which occurred 8 times, 2) code gave errors (e.g., because variables in the dataset were missing, or because functions did not run as expected), which occurred 6 times, and 3) in one case the code might have been reproducible, but the code was so complex that after 40 minutes only a small part of the results could be reproduced, and it was judged that the time needed to reproduce the results fell outside of a reasonable time span.
+In the articles that were coded as reproducible, two small errors were observed (one value of 0.89 was rounded to 0.88, and probable type where a value of 0.06 should have been 0.03) but since dozens of other values in these articles reproduced perfectly, these errors were not considered severe enough to deem the main results not computationally reproducible.
 
-After the data and code had been downloaded, and the reported results were identified by looking through the article, the average time to reproduce analyses reported in R was 27.08 minutes for the first coder (SD = 28.55) and 32.50 minutes (SD = 20.95) for the second coder.
+After the data and code had been downloaded, and the reported results were identified by looking through the article, the average time to reproduce analyses reported in R was 27.08 minutes (SD = 28.55) for the first coder and 32.50 minutes (SD = 20.95) for the second coder.
 Reproducing the SPSS analysis took on average 17.35 minutes (SD = 9.54) for the first coder and 25.50 minutes (SD = 9.72) for the second coder.
@@
 
-In addition to novel technologies, most progress can probably be made by developing standards within research communities, and educating researchers about best practices that guarantee reproducibility (for recent examples, see {[}O.
-Klein et al.
-(2018); liu\_successes\_2019{]}.
+In addition to novel technologies, most progress can probably be made by developing standards within research communities, and educating researchers about best practices that guarantee reproducibility (for recent examples, see (O.
+Klein et al., 2018; Liu \& Salganik, 2019).
 Most researchers are not trained in reproducible data analysis, and cannot be expected to invent best practices from scratch.
@@
 
+\leavevmode\hypertarget{ref-liu_successes_2019}{}%
+Liu, D., \& Salganik, M.
+(2019).
+Successes and struggles with computational reproducibility: Lessons from the Fragile Families Challenge.
+doi:\href{https://doi.org/10.31235/osf.io/g3pdb}{10.31235/osf.io/g3pdb}
+
 \leavevmode\hypertarget{ref-morey_peer_2016}{}%

### 2020-01-31 manuscript_version_2/reproducing_registered_reports.Rmd
resubmission

@@
 Of the main results from 62 articles that met our inclusion criteria, data were available for 41 articles, and analysis scripts for 37 articles.
-For the main results in 36 articles that shared both data and code we could run the scripts for 31 analyses, and reproduce the main results for 20 articles.
+For the main results in 36 articles that shared both data and code we could run the scripts for 31 analyses, and reproduce the main results for 21 articles.
 Although the articles that shared both data and code (36 out of 62, or 58%) and articles for which main results could be computationally reproduced (21 out of 36, or 58%) was relatively high compared to other studies, there is clear room for improvement.

### 2020-01-31 manuscript_version_2/reproducing_registered_reports.tex
resubmission

@@
 Of the main results from 62 articles that met our inclusion criteria, data were available for 41 articles, and analysis scripts for 37 articles.
-For the main results in 36 articles that shared both data and code we could run the scripts for 31 analyses, and reproduce the main results for 20 articles.
+For the main results in 36 articles that shared both data and code we could run the scripts for 31 analyses, and reproduce the main results for 21 articles.
 Although the articles that shared both data and code (36 out of 62, or 58\%) and articles for which main results could be computationally reproduced (21 out of 36, or 58\%) was relatively high compared to other studies, there is clear room for improvement.
